---
title: "Model Description"
author: "Adam Reimer"
date: "September 4, 2018"
output: 
  bookdown::word_document2:
    pandoc_args: ["--smart"]
---

```{r setup, echo=FALSE, include=FALSE}
library(bookdown)
knitr::opts_chunk$set(echo = TRUE)
library(SusitnaEG)
post <- readRDS("..\\..\\posts\\SuChinook_03ecf70.rds")
get_ids()
goals_list <- list(Deshka = c(9000, 18000),
                   Eastside = c(13000, 25000),
                   Talkeetna = c(9000, 17500),
                   Yentna = c(11000, 22000))
```

##State-Space Model
A state-space model (Appendix A1) was developed to generate annual abundance estimates for Susitna River Chinook salmon stocks that could be fit to a spawner-recruitment (S-R) relationship for use in deciding escapement goals based on maximum sustained yield. State-space models contain two components. Process equations describe population dynamics that are unobserved but of research interest. In this application we focus on spawning escapements, recruitment from those escapements and parameters that describe the S-R relationship. Observation equations describe how observed data are generated conditional on population parameters estimated by the process equations. We lack a robust time series of observed abundance and instead model the relationship between abundance and aerial survey data for the purpose of reconstructing historical abundance while incorporating the uncertainty in historical abundance estimates into S-R parameter estimates.   
  
Many parameters are estimated in this state-space model. Parameters with similar function or interpretation often use the same symbol, distinguished by a subscript capital letter. Subscript lower case letters denote parameter indices. For example, all harvest rates use the symbol $\mu$ where $\mu_{By}$ is the harvest rate below (downstream of) Susitna RM 34 and Yentna RM 6 in year $y$, and $\mu_{Ays}$ is the harvest rate of stock $s$ above Susitna RM 34 and Yentna RM 6 in year $y$. Year indices $y$ run from 1 to 39 representing 1979 to 2017 respectively. Stock indices $s$ run from 1 to 4 representing the Deshka River, East Susitna, Talkeetna River and Yentna River stock groups respectively. Age indices $a$ run from 3 to 6 representing total age of returning Chinook salmon where $a=6$ represents fish with a total age of 6 or larger.
  
###Process Component
Abundance of Susitna River Chinook salmon in each stock group is generated by a S-R relationship, which describes the number of fish expected to return (the “recruitment”) from a given “escapement” (number of spawning fish). The total recruitment $R_{cs}$ produced from fish spawning in brood year $c$ by stock $s$ follows the Ricker (1975) formulation:
\begin{equation}
R_{cs}~=~S_{cs}\alpha_s exp(\beta_s S_{cs})
  (\#eq:ricker)
\end{equation}
where $S_{cs}$ is the number of spawners, $\alpha_s$ (number of recruits per spawner in the absence of density dependence) is a measure of productivity for each stock group, and $\beta_s$ is a measure of density dependence for each stock group.

Productivity varies among brood years, fluctuating around a central tendency. Time-varying productivity often manifests as serially correlated model residuals, so a lognormal error term with a lag of one year was included in the linearized form of the S-R relationship (Noakes et al. 1987)
\begin{equation}
ln(R_{cs})~=~ln(S_{cs})+ln(\alpha_s)-\beta_s S_{cs} +\phi_s \nu_{(c-1)s}+\epsilon_{Ws}
  (\#eq:rickerar)
\end{equation}
where $\phi_s$ is the lag-1 moving average coefficient, $\nu_{cs}$ are model residuals
\begin{equation}
\nu_{cs}~=~ln(R_{cs})-ln(S_{cs})-ln(\alpha_s)+\beta_s S_{cs} 
  (\#eq:residuals)
\end{equation}
and the $\epsilon_{Ws}$ are independently and normally distributed process errors with “white noise” variance $\sigma^2_{Ws}$. The productivity parameters for each stock are drawn from a common distribution, $\textrm{ln}(\alpha_s)~\sim~\textrm{Normal}(\mu_\alpha, \sigma^2_\alpha)$.  
  
Age at maturity, which is needed to distribute recruitment across calendar years, is allowed to trend through time and fluctuate annually. Age-at-maturity vectors^[These proportions are maturity and survival schedules for a given brood year (cohort) across calendar years. In contrast, eq. $\@ref(eq:qstar)$ describes age proportions of returning fish in a given calendar year across brood years.] $\mathbf{p_c} = (\begin{array}{am} p_{c3} & p_{c4} & p_{c5} & p_{c6} \end{array})$ from brood year $c$ returning at ages 3--6 were drawn from a $\textrm{Dirichlet}(\gamma_{c3}, \gamma_{c4},  \gamma_{c5}, \gamma_{c6})$ distribution. The Dirichlet parameters are expressed in an alternate form where 
\begin{equation}
D~=~\sum_{a=3}^6 \gamma_{ca}
   (\#eq:Dage)
\end{equation}
is the (inverse) dispersion^[A low value of $D$ is reflective of a large amount of variability in age-at-maturity proportions $\mathbf{p_c}$ among brood years, whereas a high value of $D$ indicates more consistency in $\mathbf{p_c}$ over time.] of the annual age-at-maturity vectors, reflecting consistency of age at maturity among brood years.
The location parameters
\begin{equation}
\pi_{ca}~=~\frac{\gamma_{ca}}{D}~=~\frac{exp(ML1_a+ML2_ac)}{\sum_a exp(ML1_a+ML2_ac)}
   (\#eq:pi)
\end{equation}
are proportions that sum to one for each brood year and reflect the age-at-maturity central tendency in each year where $ML1_a$ and $ML2_a$ are multinomial logistic regression coefficients describing trending age at maturity.
  
The abundance $N_{yas}$ in stock group $s$ of age $a$ Chinook salmon in calendar year $y$ is the product of the age at maturity scalar $p_{ca}$ and the total return (recruitment) $R_{cs}$ in stock group $s$ from from brood year $c=y−a$:
\begin{equation}
N_{yas}~=~p_{(y-a)a}R_{(y-a)s}
   (\#eq:Ntas)
\end{equation}
Total run $N_{ys}$ for stock group $s$ during calendar year $y$ is the sum of abundance at age across all ages:
\begin{equation}
N_{ys}~=~\sum_{a=3}^6 N_{yas}
   (\#eq:Nts)
\end{equation}
Annual harvest of Susitna-origin Chinook salmon below (downstream of) Susitna RM 34 and Yentna RM 6, $H_{By}$, was modeled as the product of the annual harvest rate in the area $\mu_{By}$ and total run $N_y$:
\begin{equation}
H_{By}~=~\mu_{By}\sum_{s=1}^4 N_{ys}
   (\#eq:Hbelow)
\end{equation}
Inriver run $IR_{ys}$ of stock group $s$ during calendar year $y$ at Susitna RM 34 and Yentna RM 6 was modeled as the product of stock specific total run $N_{ys}$ and the annual survival rate in the area downstream: 
\begin{equation}
IR_{ys}~=~N_{ys}(1-\mu_{By})
   (\#eq:IR)
\end{equation}
Annual harvest of stock group $s$ above Susitna RM 34 and Yentna RM 6, $H_{Ays}$, was the product of the annual harvest rate for each stock in the area $\mu_{Ays}$ and the inriver run of stock group $s$:
\begin{equation}
H_{Ays}~=~\mu_{Ays}IR_{ys}
   (\#eq:Habove)
\end{equation}
Annual harvest of Deshka River Chinook salmon (s = 1) upstream of the Deshka River weir $H_{Dy}$ was a proportion $p_{Dy}$ of the total inriver harvest of Deshka River Chinook salmon $H_{Ay1}$:
\begin{equation}
H_{Dy}~=~p_{Dy}H_{Ay1}
   (\#eq:Hdeshka)
\end{equation}
The $p_{Dy}$ are drawn from a $\textrm{Beta}(b1_D, b2_D)$ distribution. The beta parameters are expressed in an alternate form where $B_D~=~b1_D+b2_D$ is the (inverse) dispersion of the annual proportion of the harvest from above the weir.
  
Spawning escapement $S_{ys}$ was inriver run abundance minus harvest above Susitna RM 34 and Yentna RM 6:
\begin{equation}
S_{ys}~=~IR_{ys}-H_{Ays}
   (\#eq:S)
\end{equation}
Finally, Chinook salmon passage at the Deshka River weir was the sum of the spawning escapemnt in the Deshka River $S_{y1}$ and harvest upstream of the weir: 
\begin{equation}
IR_{Dy}~=~S_{y1}+H_{Dy}
   (\#eq:dweir)
\end{equation}

Multiple tributaries ($t=1,2,\dots,T$) contribute to the spawning escapement in the East Susitna, Talkeetna, and Yentna stock groups. The relative composition of individual spawning tributaries within each stock is of interest because some observed data is germane to the tributary scale. Stock composition of the $T-1$ tributaries which are monitored by aerial survey is allowed to fluctuate annually around a trending central tendency. Four sets of equations analogous to eq. $\@ref(eq:Dage)$ and eq. $\@ref(eq:pi)$ were used to define stock composition vectors $\mathbf{\rho^*}_{sy} = (\begin{array} \rho^*_{sy1} & \rho^*_{sy2 }& \dots & \rho^*_{sy(T-1)}\end{array})$ for the surveyed tributaries in each stock group.
  
The annual proportion fish from stock $s$ that spawned in tributaries that were not monitored by aerial survey, $\rho\prime_{sy}$, are drawn from a $Beta(b1_s, b2_s)$ distribution. The Beta parameters are expressed in an alternate form where $B_s~=~b1_s+b2_s$ is the (inverse) dispersion of the annual proportion of each stock that was not surveyed.
  
Stock composition was calculated as follows:
\begin{equation}
\mathbf{\rho_{sy}}~=~\left(\begin{array}{} \rho^*_{sy1}(1-\rho\prime_{sy}) & \rho^*_{sy2}(1-\rho\prime_{sy}) & \dots & \rho\prime_{sy} \end{array}\right)
   (\#eq:pcomp)
\end{equation}
  
###Observation Component
Observed data (Appendices B1-B#) include estimates of annual harvest below and above Susitna RM 34 and Yentna RM 6, age composition data from throughout the Susitna River drainage, weir counts for `r dim(weir)[2]` tributaries, aerial survey data for `r sum(sapply(as, function(x){dim(x)[2]}))` tributaries, mark-recapture estimates of inriver run, radio telemetry data, and length composition data. Sampling distributions for the data follow.
  
Estimated annual inriver runs of Chinook salmon for stock $s$, $\widehat{IR}_{ys}$ from mark-recapture data were
\begin{equation}
\widehat{IR}_{ys}~=~IR_{500ys}exp(\epsilon_{IRys})
   (\#eq:IRhat)
\end{equation}
where $IR_{500ys}$ is the inriver run of fish 500 mm mid eye to tail fork (METF) length or larger, $\epsilon_{IRys}~\sim~\textrm{Normal}(0, \sigma^2_{IRys})$, and $\sigma^2_{IRys}$ is calculated from the coefficient of variation (CV) of $\widehat{IR}_{ys}$:
\begin{equation}
\sigma^2_{IR_{ys}}~=~\textrm{ln}(\textrm{CV}(\widehat{IR}_{ys})^2+1)
   (\#eq:cvIR)
\end{equation}

The number of age-3 and age-4 fish that were less than 500 mm METF, in year $y$, $x_{500ya}$ were
\begin{equation}
x_{500ya}~\sim~\textrm{Binomial}(p_{500ya}, n_{500ya})
   (\#eq:xsmall)
\end{equation}
where $n_{500ya}$ is the  total number of fish sampled for age and length in age class $a$ during year $y$ and $p_{500ya}$ is the proportion of fish less than 500 mm METF in age class $a$ (3 or 4) during year $y$.
  
Inriver runs of fish 500 mm METF or greater, $IR_{500ys}$, were
\begin{equation}
IR_{500ys}~=~IR_{ys}[1-(q_{y3}p_{500y3}+q_{y4}p_{500y4})]
   (\#eq:IRlarge)
\end{equation}
where $q_{ya}$ is the proportion of the run that is age $a$ in calendar year $y$.
  
Estimated annual harvest of Susitna River Chinook salmon below Susitna RM 34 and Yentna RM 6 $\widehat{H}_{By}$ was
\begin{equation}
\widehat{H}_{By}~=~H_{By}exp(\epsilon_{HBy})
   (\#eq:HBhat)
\end{equation}
where the $\epsilon_{HBy}~\sim~\textrm{Normal}(0, \sigma^2_{HBy})$ and the variances followed eq. $\@ref(eq:cvIR)$ with an assumed CV of 0.13 reflecting fair precision associated with reported commercial and subsistence harvest from mixed-stock fisheries.
  
Estimated annual harvest of Susitna River Chinook salmon above Susitna RM 34 and Yentna RM 6 $\widehat{H}_{Ays}$ for stock $s$ was
\begin{equation}
\widehat{H}_{Ays}~=~H_{Ays}exp(\epsilon_{HAys})
   (\#eq:HAhat)
\end{equation}
where the $\epsilon_{HAys}~\sim~\textrm{Normal}(0, \sigma^2_{HAys})$ and the variances followed eq. $\@ref(eq:cvIR)$ with an assumed CV of 0.15 for the East Susitna and Yentna stock groups, 0.2 from the Deshka stock group and 0.3 for the Talkeetna stock group. Assumed cv's are averages from 1996--2017 SWHS estimates.

Estimated annual harvest of Deshka River Chinook upstream of the Deshka weir $\widehat{H}_{Dy}$ was
\begin{equation}
\widehat{H}_{Dy}~=~H_{Dy}exp(\epsilon_{HDy})
   (\#eq:HAhat)
\end{equation}
where the $\epsilon_{HDy}~\sim~\textrm{Normal}(0, \sigma^2_{HDy})$ and the variances followed eq. $\@ref(eq:cvIR)$ with an assumed CV of 0.32 which is the average CV from 1996--2017 SWHS estimates.

Final destinations from radio telemetry data within each stock group $\mathbf{r}_{sy} = (\begin{array}{am} r_{sy1} & r_{sy2} & \dots & r_{syT} \end{array})$ were partitioned into $T$ categories with $T-1$ categories representing tributaries within the stock group that are counted during aerial surveys and one category ($T$) representing all tributaries that were not counted during aerial surveys. Radio tags located in tributaries that were not counted during aerial surveys were
\begin{equation}
r_{syT}~\sim~\textrm{Binomial}\left(\rho\prime_{sy}, \sum_t^T r_{syt}\right)
   (\#eq:nosurvey)
\end{equation}
  
Radio tags located within tributaries that were counted during aerial surveys $r_{sy[1:(T-1)]}$ were as follows:
\begin{equation}
r_{sy[1:(T-1)]}~\sim~\textrm{Multinomial}\left(\rho^*_{syt}, \sum_t^{T-1} r_{syt}\right)
   (\#eq:survey)
\end{equation}
where $\rho^*_{syt}$ estimates the annual proportion of radiotagged fish from surveyed tributaries within stock $s$ that spawned in tributary $t$.

The proportion of the spawning escapement in tributary $t$, $\theta_t$, counted during aerial surveys was
\begin{equation}
\textrm{logit}(\theta_t)~\sim~\textrm{Normal}(\mu_\theta, \sigma^2_\theta)
   (\#eq:theta)
\end{equation}

Annual aerial surveys, $as_{yt}$, were available for `r sum(sapply(as, function(x){dim(x)[2]}))` tributaries $t$. Each survey is related to abundance for the stock group within which it was located:
\begin{equation}
as_{yt}~=~\theta_t\rho_{syt}S_{ys}exp(\epsilon_{ASt})
   (\#eq:as)
\end{equation}
where the $\epsilon_{ASt}~\sim~\textrm{Normal}(0, \sigma^2_{ASt})$ and $\sigma_{ASt}~\sim~\textrm{half_Cauchy}(0, B_{AS})$ where $B_{AS}$ is the median of the distribution of $\sigma_{ASt}$. Modeled observability of spawning Chinook salmon, $\theta_t$ is constant across years and annual variability in observability is confounded with annual variability in stock composition, $\rho_{syt}$, and included in $\sigma_{ASt}$. Because stock composition was only observed late in the time series (2012--2017) stock composition trends reflect changes in the relative magnitude of aerial survey counts. Trends in relative magnitude of survey counts are assumed to reflect changes in stock composition, although trending stock-specific observability could result in similar data. This assumption is supported by consistent survey procedures utilized throughout the time series.   
  
Weirs counts were available for three tributaries. Each weir count is related to abundance for the stock group within which it was located:
\begin{equation}
w_{yt}~=~\rho_{syt}S_{ys}exp(\epsilon_{W})
   (\#eq:weir)
\end{equation}
where the $\epsilon_{W}~\sim~\textrm{Normal}(0, \sigma_{W}^2)$ and the variances followed eq. $\@ref(eq:cvIR)$ with an assumed CV of 0.05 reflecting good precision associated with weir counts.
  
Age composition data is modeled as if age samples were collected from the drainage wide return, although age samples were actually collected from stock specific locations either during or after harvest. Using age samples from the harvest and inriver run samples as a proxy for samples from the return was driven by the available data and represents an implicit assumption that fish are harvested in proportion to return-by-age. Age composition may differ between stock groups and multinomial logistic regression was used to include a correction for the stock group that was sampled when estimating annual drainage wide age composition. The stock specific scale-age counts $x_{yas}$ were modeled as multinomially distributed 
\begin{equation}
x_{yas}~=~\textrm{Multinomial}\left(q^*_{yas}, \sum_{(a=3)}^6 x_{yas}\right)
   (\#eq:xage)
\end{equation}
The location parameters are
\begin{equation}
q^*_{yas}~=~\frac{exp\left[\textrm{ln}\left(\frac{N_{ya}}{N_{y(a=3)}}\right)+b_{sa}I_s\right]}{\sum_a exp\left[\textrm{ln}\left(\frac{N_{ya}}{N_{y(a=3)}}\right)+b_{sa} I_s\right]}
   (\#eq:qstar)
\end{equation}
which represents a multinomial logistic regression where the intercept is a function of annual abundance in each age class and the categorical covariates account for age composition differences between the stock groups. The parameters $b_{sa}$ represent adjustments to the age composition estimate for stock $s$ in age $a$ whereas covariates $I_s$ represent indicator variables for each stock group. Because $\sum_s b_{sa}=0$ the quantity
\begin{equation}
q_{yt}~=~\frac{N_{ya}}{\sum_{a=3}^6 N_{y}}
   (\#eq:qstar)
\end{equation}
is an estimate of age compostion for the entire run of Susitna River Chinook salmon.

##Model Fitting
Model fitting involves finding the values of the population parameters that could have plausibly resulted in the data that were observed. To do so, Markov Chain Monte Carlo (MCMC) methods were employed using the package RJAGS (Plummer 2013) within R (R Core Team 2016). This methodology allows for inclusion of the effects of measurement error, serially-correlated productivity, and missing data into the analysis and provides a more realistic assessment of uncertainty than is possible with classical statistical methods. By properly specifying process variation, measurement error, and time-dependent linkage in the model, biases in the estimates can be reduced (Su and Peterman 2012).
  
Bayesian statistical methods employ the language of probability to quantify uncertainty about model parameters. Knowledge existing about the parameters outside the framework of this analysis is the “prior” probability distribution. The output of the Bayesian analysis is called the “posterior” probability distribution, which is a synthesis of the prior information and the information contained in the data. See Fleischman et al. (2013) and Staton et al. (2016) for similar applications of the methods used in this report. 
  
###Prior Distributions
Noninformative priors (chosen to have minimal effect on the posterior) were used for most parameters. Initial recruitments $R_{1973}-R_{1978}$ (those lacking linked spawner abundance) were modeled as drawn from a common lognormal distribution with median $\mu_{logR}$ and variance $\sigma^2_{logR}$. Truncated normal priors with mean zero, very large variances, and constrained to be positive were used for $\mu_{log(\alpha)}$, $\beta$, $\mu_{logR}$. Initial model residual $\nu_s$ were given a truncated normal prior with mean zero and variance $\sigma^2_{Ws}/(1-\phi^2_s)$ between -3 and +3. Annual harvest rates $\mu_{By},~\mu_{Asy}$ were given $\textrm{beta}(0.5,0.5)$ priors. Diffuse conjugate inverse gamma priors were used for $\sigma^2_{Ws}, \sigma^2_{logR}$. A informative conjugate inverse gamma prior [$\textrm{gamma}(2,1)$] was used for $\sigma^2_\alpha$. Dirichlet dispersion parameters $1/\sqrt{D}$ for age, stock, and harvest compositions have $\textrm{Uniform}(0.07,1)$ priors. $p_{500y3}$ and $p_{500y4}$ have $\textrm{Uniform}(0,1)$ priors. The prior on $B_{AS}$ is also $\textrm{Uniform}(0,1)$, and contains information on the range of $B_{AS}$ although the range is not limiting.
  
###Sampling from the Posterior Distribution
MCMC samples were drawn from the joint posterior probability distribution of all unknowns in the model. The model was initiated with `r post$mcmc.info$n.chains` chains and `r format(post$mcmc.info$n.iter, big.mark = ",", scientific = 100)` samples were generated per chain. The first `r format(post$mcmc.info$n.burnin, big.mark = ",", scientific = 100)` samples from each chain were discarded and the remaining samples were thinned by a factor of `r post$mcmc.info$n.thin`, resulting in `r format(post$mcmc.info$n.samples, big.mark = ",", scientific = 100)` samples that were used to estimate the marginal posterior means, standard deviations, and percentiles. The diagnostic tool ShinySTAN (Stan Development Team 2016) was used to assess mixing and convergence, and no major problems were encountered. Interval estimates were constructed from the percentiles of the posterior distribution.

##Reference Points and Optimal Yield Profiles
Reference points were calculated from S-R parameter estimates for each individual MCMC sample. Sustained yield is the number of fish in the expected recruitment over and above that needed to replace the spawners. Escapement goals in Alaska are developed to maximize sustained yield by choosing a range of escapements around $S_{MSY}$, the theoretical number of spawners that will result in the largest difference between recruitment and replacement. Spawning abundance providing maximum sustained yield (MSY) $S_{MSY}$ was approximated
\begin{equation}
S_{MSYs}~\cong~\frac{\textrm{ln}(\alpha\prime_s)}{\beta}[0.5-0.07\textrm{ln}(\alpha\prime_s)]
   (\#eq:SMSY)
\end{equation}
Sustained yield at a specified level of $S$ was obtained by subtracting spawning escapement from recruitment:
\begin{equation}
Y_{Ss}~=~R_s-S_s~=~S_{s}exp(\textrm{ln}(\alpha\prime_s)-\beta_s S_{s})-S_s
   (\#eq:Ys)
\end{equation}
The harvest rate leading to maximum sustained yield, is approximated by (Hilborn 1985):
\begin{equation}
U_{MSYs}~\cong~\textrm{ln}(\alpha\prime_s)[0.5-0.07\textrm{ln}(\alpha\prime_s)]
   (\#eq:UMSY)
\end{equation}
  
Fishery managers may want to evaluate existing and proposed goal ranges with respect to other indicators of fishery performance. In some sport fisheries, run sizes and high catch rates (associated with large recruitment) are important priorities. The escapement leading to maximum sustained recruitment (MSR) is:
\begin{equation}
S_{MSRs}~=~\frac{1}{\beta_s}
   (\#eq:SMSR)
\end{equation}
Equilibrium spawning abundance, where recruitment exactly replaces spawners is:
\begin{equation}
S_{EQs}~=~\frac{\textrm{ln}(\alpha\prime_s)}{\beta_s}
   (\#eq:SEQ)
\end{equation}
The quantity
\begin{equation}
\textrm{ln}(\alpha\prime_s)~=~\textrm{ln}(\alpha_s)+\frac{\sigma^2_{Ws}}{2(1-\phi_s^2)}
   (\#eq:alphaprime)
\end{equation}
in Equations $\@ref(eq:SMSY)$, $\@ref(eq:Ys)$, $\@ref(eq:UMSY)$, and $\@ref(eq:SEQ)$ adjusts for the difference between the median and the mean of a right-skewed lognormal error distribution with autocorrelation.

The probability that a given spawning escapement $S$ would produce average yields ($Y_S$) exceeding X% of MSY was obtained by calculating $Y_S$ at incremental values of $S$ for each MCMC sample, then comparing $Y_S$ with X% of the value of MSY for that sample. The proportion of samples in which $Y_S$ exceeded X% of MSY is an estimate of the desired probability, and the plot of proportion versus $S$ is termed an optimal yield profile (OYP; Fleischman et al. 2013).

The probability that yield would be reduced to less than X% of MSY by supplying too few spawners $S$ was obtained by calculating $Y_S$ at incremental values of $S$ and tallying the number of MCMC samples for which $Y_S$ was less than X% of MSY and $S$ was less than $S_{MSY}$. A plot of the fraction of samples in which this condition occurred versus $S$ is termed an overfishing profile (Bernard and Jones III 2010).

The probability that a given spawning escapement $S$ would produce average recruitment $R$ exceeding X% of MSR was obtained by calculating $R$ eq. $\@ref(eq:ricker)$ at incremental values of $S$ for each MCMC sample, then comparing $R$ with X% of the value of MSR for that sample. The proportion of samples in which $R$ exceeded X% of MSR is an estimate of the desired probability, and the plot of the proportion versus $S$ is termed an optimal recruitment profile (ORP; Fleischman et al. 2013).

OYPs, Overfishing profiles, and ORPs were used to quantify the yield (or recruitment) performance of prospective escapement goals, taking into consideration the uncertainty about the true abundance, productivity, and capacity of the stock.

##Escapement Goals Standardized To $S_{MSY}$
To compare escapement goals across stocks, we divided the lower and upper bounds of `r dim(chinBEGs)[1]` published goals for Alaska Chinook salmon (Munro and Volk 2016) by point estimates of $S_{MSY}$ for each stock, thereby expressing all goal ranges in terms of multiples of $S_{MSY}$. These values were multiplied by estimates of $S_{MSY}$ for each stock group to provide a graphical comparison of the recommended goals with those from other stocks.

##Escapement Goal Review Process
An interdivisional escapement goal review team was convened to review the available data, discuss analyses and results, and make escapement goal recommendations. The escapement goals recommended in this report are the product of several collaborative meetings of the review team and other ADF&G staff. The final recommendation was reached by consensus of fisheries scientists and regional research coordinators from both fisheries divisions.

#Results
##Deshka River
```{r echo=FALSE, include=FALSE}
digits <-
  function(p){
    ps <- ifelse(p < 0.01, format(p, TRUE, digits = 2, scientific = TRUE),
                 ifelse(p < 2, format(round(p, 2), TRUE, nsmall = 2),
                        ifelse(p < 100, format(round(p, 1), TRUE, nsmall = 1),
                               format(round(p, 0), TRUE, nsmall = 0, width = 5, scientific = FALSE, big.mark = ","))))
  return(ps)
}

S <- 
  post$summary[grepl("S\\[\\d+,\\d\\]", rownames(post$summary)),] %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column() %>%
  dplyr::rename(q50 = '50%') %>% 
  dplyr::mutate(stock = as.numeric(gsub("S\\[\\d+,(\\d)\\]", "\\1", rowname)),
                year = year_id[as.numeric(gsub("S\\[(\\d+),\\d\\]", "\\1", rowname))],
                cv = sd / mean) %>%
 dplyr::select(rowname, stock, year, q50, cv)
IR <- 
  post$summary[grepl("IR\\[\\d+,\\d\\]", rownames(post$summary)),] %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column() %>%
  dplyr::rename(q50 = '50%') %>%
  dplyr::mutate(stock = as.numeric(gsub("IR\\[\\d+,(\\d)\\]", "\\1", rowname)),
                year = year_id[as.numeric(gsub("IR\\[(\\d+),\\d\\]", "\\1", rowname))],
                cv = sd / mean) %>%
 dplyr::select(rowname, stock, year, q50, cv)
N <- 
  post$summary[grepl("N\\[\\d+,\\d\\]", rownames(post$summary)),] %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column() %>%
  dplyr::rename(q50 = '50%') %>%
  dplyr::mutate(stock = as.numeric(gsub("N\\[\\d+,(\\d)\\]", "\\1", rowname)),
                year = year_id[as.numeric(gsub("N\\[(\\d+),\\d\\]", "\\1", rowname))],
                cv = sd / mean) %>%
 dplyr::select(rowname, stock, year, q50, cv)
R <- 
  post$summary[grepl("R\\[\\d+,\\d\\]", rownames(post$summary)),] %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column() %>%
  dplyr::rename(q50 = '50%') %>%
  dplyr::mutate(stock = as.numeric(gsub("R\\[\\d+,(\\d)\\]", "\\1", rowname)),
                yr = as.numeric(gsub("R\\[(\\d+),\\d\\]", "\\1", rowname)),
                cv = sd / mean) %>%
  dplyr::filter(yr %in% 7:39) %>%
 dplyr::select(rowname, stock, yr, q50, cv)
minrow <- function(dat, n){
  dat %>% 
    dplyr::filter(stock == n) %>% 
    dplyr::slice(which.min(q50)) %>%
    dplyr::mutate(median = digits(q50))}
  
maxrow <- function(dat, n){
  dat %>% 
    dplyr::filter(stock == n) %>% 
    dplyr::slice(which.max(q50)) %>%
    dplyr::mutate(median = digits(q50))}
maxrow(N, 1)

NIR1cv94 <- digits(range(c(IR[IR$year %in% year_id[1:which(year_id == "1994")] & IR$stock == 1, ]$cv, 
                          N[N$year %in% year_id[1:which(year_id == "1994")] & N$stock == 1, ]$cv)))
NIRS1cv17 <- digits(range(c(IR[IR$year %in% year_id[which(year_id == "1995"):length(year_id)] & IR$stock == 1, ]$cv, 
                           N[IR$year %in% year_id[which(year_id == "1995"):length(year_id)] & IR$stock == 1, ]$cv, 
                           S[IR$year %in% year_id[which(year_id == "1995"):length(year_id)] & IR$stock == 1, ]$cv)))
S1cv94 <- digits(range(S[S$year %in% year_id[1:which(year_id == "1994")] & S$stock == 1, ]$cv))
R1cv94 <- digits(range(R[R$yr %in% 7:22 & R$stock == 1, ]$cv))
R1cv17 <- digits(range(R[R$yr %in% 23:39 & R$stock == 1, ]$cv))

t1 <- post$summary[grepl("theta\\[1,1\\]", rownames(post$summary)), ]
CI <- function(df) paste0(digits(df['50%']), " (95%CI ", digits(df['2.5%']), "-", digits(df['97.5%']), ")")

et1 <- as[[1]]/weir[,1] 
et1_n <- sum(!is.na(et1))
et1_r <-digits(range(et1, na.rm = TRUE))

sa1 <- post$summary[grepl("sigma.air\\[1\\]", rownames(post$summary)), ]

B <- post$summary[grepl("B$", rownames(post$summary)), ]

lna1 <- post$summary[grepl("lnalpha\\[1\\]", rownames(post$summary)), ]

sw1 <- post$summary[grepl("sigma.white\\[1\\]", rownames(post$summary)), ]

phi1 <- post$summary[grepl("phi\\[1\\]", rownames(post$summary)), ]

SMSY1 <- post$summary[grepl("S.msy\\[1\\]", rownames(post$summary)), ]

SMSR1 <- post$summary[grepl("S.max\\[1\\]", rownames(post$summary)), ]

rs <- function(sn){
  rs <- post$summary[grepl(paste0("R\\[\\d+,", sn, "\\]"), rownames(post$summary)), "50%"][7:42]/
    post$summary[grepl(paste0("S\\[\\d+,", sn, "\\]"), rownames(post$summary)), "50%"][1:36]
  list(min = digits(range(rs)[1]),
       max = digits(range(rs)[2]),
       n = sum(rs < 1)
  )
}

prob_e <- get_profileprobs(get_profile(post, "Deshka"), c(13000, 27000))
prob_p <- get_profileprobs(get_profile(post, "Deshka"), c(goals_list[[1]][1], goals_list[[1]][2]))
```
Measures of Deshka River Chinook salmon abundance are sparse, but display a common trend through time when more than one measure is available (Figure 2). Estimated abundance track weir counts, which are assumed to be very precise, closely starting in 1995. Prior to 1995, only aerial survey data is available to index abundance. Runs were large prior to 1991, underwent a decline during 1991--1994, rebounded during 1995--2004, declined again staring in 2005 and remained at a lower level during 2008--2017. Escapement estimates ranged between `r minrow(S, 1)$median` in `r minrow(S, 1)$year` and `r maxrow(S, 1)$median` in `r maxrow(S, 1)$year` and inriver run estimates ranged from `r minrow(IR, 1)$median` in `r minrow(IR, 1)$year` to `r maxrow(IR, 1)$median` in `r maxrow(IR, 1)$year`.
  
Total and inriver run estimates (Appendix C1) are more precise than escapement estimates prior to 1995 because harvest is well estimated compared to the abundance estimates based on one annual aerial survey. Coefficients of variation for total and inriver run ranged from `r NIR1cv94[1]` to `r NIR1cv94[2]` prior to 1995 whereas coefficients of variation for escapement ranged from `r S1cv94[1]` to `r S1cv94[2]`. After 1995, all estimates have coefficients of variation ranging from `r NIRS1cv17[1]` to `r NIRS1cv17[2]` because weir estimates are very precise. Coefficients of variation for recruitment from complete brood years were highly variable both before (`r R1cv94[1]`--`r R1cv94[2]`) and after (`r R1cv17[1]`--`r R1cv17[2]`) the weir was installed because of considerable variation in the S-R relationship [$\sigma_W$ = `r CI(sw1)`]. 
  
The model-estimated proportion of the escapement observed during aerial surveys of the Deshka River was `r CI(t1)`(Table 1). Empirical estimates of observability (survey count/weir count) exist for `r et1_n` years and range from `r et1_r[1]` to `r et1_r[2]`. There was average agreement between Deshka River aerial survey counts (expanded by inverse observability) and other indices of abundance on the Deshka River.  The lognormal standard deviation for the Deshka River aerial survey regression was `r CI(sa1)`, which is similar to the median value for the distribution of $\sigma_{AS}$ [`r CI(B)`].
  
Estimates of population parameters from the state-space model take uncertainty in estimated escapement S and recruitment R (Figure 3 error bars) into account. The individual data pairs are weighted depending upon the certainty with which the individual values of S and R are known. Because escapement and recruitment are poorly known for many brood years, and due to other sources of uncertainty, Ricker S-R relationships that could have plausibly generated the observed data are diverse (Figure 3: light lines), often deviating substantially from the mean Ricker relationship (Figure 3: heavy dashed line).
  
Median productivity (recruits per spawner, in the absence of density effects) of Deshka River Chinook salmon during 1979–2017 has been moderate [$\textrm{ln}(\alpha)$ = `r CI(lna1)`; Table 2]. There is a great deal of uncertainty about productivity, as evident in the extent to which the plausible S-R relationships differ with respect to their slope at the origin (Figure 3). Similarly, uncertainty about $\beta$ is reflected in variability in the escapements leading to maximum recruitment $S_{MSR}$, and uncertainty about equilibrium abundance $S_{EQ}$ is reflected by variability in the escapements where the curves intersect the replacement line. Variability in maximum sustained yield is harder to visualize. Graphically, maximum sustained yield is the escapement that maximizes the length of a vertical line drawn from the Ricker curve downward to the replacement line. Given the diversity of plausible S-R relationships (Figure 3), it is important to choose an escapement goal that is robust to this uncertainty rather than one tailored solely to the median S-R relationship. To address this uncertainty, we tallied the success or failure of a given number of spawners in achieving biological reference points across plausible S-R relationships in the optimal yield, optimal recruitment and overfishing profiles (Figure 4). 
  
Deshka River Chinook salmon escapement leading to maximum sustained yield $S_{MSY}$ (Table 2) was estimated to be `r CI(SMSY1)`. The optimal yield profiles in Figure 4 (top panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSY. These probabilities, which are highest near $S_{MSY}$ can be used to quantify the yield performance of prospective escapement goals (Figure 4 pink-shaded areas), taking into consideration all uncertainty about the true abundance and productivity of the stock. The overfishing profiles (Figure 4 middle panel) show the probability that sustained yield would be reduced to less than 70%, 80%, or 90% of MSY by fishing too hard and supplying too few spawners. For this stock, these probabilities are nearly the exact complements of the probabilities in the left-hand limbs of the optimal yield profiles.
  
Expected sustained yield (number of fish over and above that necessary to replace the number of spawners, averaged over brood years 1979–2015) is also maximized at $S_{MSY}$ (Figure 5). Actual yield in any single year has varied widely (Figure 3), in part because the S-R relationship is noisy and in part because many escapements have been near $S_{eq}$. Median return per spawner has varied between `r rs(1)$min` and `r rs(1)$max` for Deshka River Chinook salmon with `r rs(1)$n` of 36 complete brood years failing to replace themselves.
  
The escapement leading to maximum recruitment $S_{MSR}$ was estimated to be `r CI(SMSR1)`(Table 2). Analogous to the optimum yield profiles discussed above, optimum recruitment profiles tally the success or failure of a given number of spawners to maximize recruitment across plausible S-R relationships. The optimal recruitment profiles in Figure 4 (bottom panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSR. Optimum recruitment probabilities, which are highest near $S_{MSR}$, reach maximums at larger spawning abundances than optimum yield probabilities and decrease more slowly as spawning abundance increases.
  
##East Susitna
```{r echo=FALSE, include=FALSE}
NIR2cv <- digits(range(c(IR[IR$stock == 2, ]$cv, 
                        N[N$stock == 2, ]$cv)))
S2cv <- digits(range(S[S$stock == 2, ]$cv))
R2cv <- digits(range(R[R$stock == 2, ]$cv))

D2 <- post$summary[grepl("Dsum.S2", rownames(post$summary)), ]
B2 <- post$summary[grepl("Bsum.So\\[1", rownames(post$summary)), ]

p2out <-digits(post$summary[grepl("p.S2\\[\\d+,7\\]", rownames(post$summary)), "mean"] * 100)

t2 <- post$summary[grepl("theta\\[2,1\\]", rownames(post$summary)), ]
t3 <- post$summary[grepl("theta\\[3,1\\]", rownames(post$summary)), ]
t4 <- post$summary[grepl("theta\\[4,1\\]", rownames(post$summary)), ]
t5 <- post$summary[grepl("theta\\[5,1\\]", rownames(post$summary)), ]
t6 <- post$summary[grepl("theta\\[6,1\\]", rownames(post$summary)), ]
t7 <- post$summary[grepl("theta\\[7,1\\]", rownames(post$summary)), ]

et2 <- as[[2]][,4]/weir[,2] 
et2_n <- sum(!is.na(et2))
et2_r <- digits(et2[!is.na(et2)])

et3 <- as[[2]][,6]/weir[,3] 
et3_n <- sum(!is.na(et3))
et3_r <- digits(et3[!is.na(et3)])

sa2 <- post$summary[grepl("sigma.air\\[2\\]", rownames(post$summary)), ]
sa3 <- post$summary[grepl("sigma.air\\[3\\]", rownames(post$summary)), ]
sa4 <- post$summary[grepl("sigma.air\\[4\\]", rownames(post$summary)), ]
sa5 <- post$summary[grepl("sigma.air\\[5\\]", rownames(post$summary)), ]
sa6 <- post$summary[grepl("sigma.air\\[6\\]", rownames(post$summary)), ]
sa7 <- post$summary[grepl("sigma.air\\[7\\]", rownames(post$summary)), ]

lna2 <- post$summary[grepl("lnalpha\\[2\\]", rownames(post$summary)), ]

sw2 <- post$summary[grepl("sigma.white\\[2\\]", rownames(post$summary)), ]

phi2 <- post$summary[grepl("phi\\[2\\]", rownames(post$summary)), ]

SMSY2 <- post$summary[grepl("S.msy\\[2\\]", rownames(post$summary)), ]

SMSR2 <- post$summary[grepl("S.max\\[2\\]", rownames(post$summary)), ]

prob_p2 <- get_profileprobs(get_profile(post, "East Susitna"), c(goals_list[[2]][1], goals_list[[2]][2]))
```
Measures of East Susitna Chinook salmon abundance display a common trend through time (Figure 6). Runs were small prior to 1983 increased during 1983--1997, underwent a decline during 1998--2012, rebounded slightly after 2012, but were low again in 2017. Escapement estimates ranged between `r minrow(S, 2)$median` in `r minrow(S, 2)$year` and `r maxrow(S, 2)$median` in `r maxrow(S, 2)$year` and inriver run estimates ranged from `r minrow(IR, 2)$median` in `r minrow(IR, 2)$year` to `r maxrow(IR, 2)$median` in `r maxrow(IR, 2)$year`.
  
Total and inriver run estimates (Appendix C2) have similar precision as escapement estimates. Coefficients of variation for total and inriver run ranged from `r NIR2cv[1]` to `r NIR2cv[2]` and coefficients of variation for escapement ranged from `r S2cv[1]` to `r S2cv[2]`. Coefficients of variation for recruitment from complete brood years were moderate (`r R2cv[1]`-`r R2cv[2]`) reflective of moderate variation in the S-R relationship [$\sigma_W$ = `r CI(sw2)`].
  
Among the surveyed streams within the East Susitna stock group Little Willow and Willow Creeks increased in relative abundance between 1979 and 2017 whereas Goose, Kashwitna, Montana, and Sheep creeks decreased in relative abundance (Figure 7, Appendix D1). Most recently, Willow Creek is the largest component of the spawning abundance followed by Little Willow Creek, Montana Creek, Sheep Creek,  Kashwitna River and Goose Creek. The inverse dispersion for the East Susitna stock group is large [$D_{comp}$ = `r CI(D2)`, Table 3], indicating trends in the relative magnitude of survey counts and radio telemetry data are well explained by the multinomial logistic regression model with a calendar-year covariate. There are minor differences between estimated stock composition and empirical stock composition estimates in some years, which represent situations where weighted relative survey counts and telemetry data disagree.
  
Because unsurveyed streams in the East Susitna stock group lack relative composition information early in the time series, no trend can be estimated. Unsurvey streams compose `r min(p2out)`--`r max(p2out)`% (Figure 7, Appendix D1) of the East Susitna stock group. Inverse dispersion is small ($B_{survey}$ = `r CI(B2)`, Table 3) indicating high variability in the proportion of the East Susitna stock group which spawns within the 6 surveyed streams. High variability was documented with telemetry data.
  
The estimated proportion of the escapement observed during an aerial survey of Goose Creek was `r CI(t2)`(Table 1). There was good agreement between the Goose Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the East Susitna stock group.  The lognormal standard deviation for the Goose Creek aerial survey regression was `r CI(sa2)`, which is smaller than the median value for the distribution of $\sigma_{AS}$ [`r CI(B)`].
  
The estimated proportion of the escapement observed during an aerial survey of the Kashwitna River was `r CI(t3)`(Table 1). There was poor agreement between the Kashwitna River aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the East Susitna stock group.  The lognormal standard deviation for the Kashwitna River aerial survey regression was `r CI(sa3)`, which is larger than the median value for the distribution of $\sigma_{AS}$.
  
The estimated proportion of the escapement observed during an aerial survey of Little Willow Creek was `r CI(t4)`(Table 1). There was good agreement between the Little Willow Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the East Susitna stock group.  The lognormal standard deviation for the Little Willow Creek aerial survey regression was `r CI(sa4)`, which is smaller than the median value for the distribution of $\sigma_{AS}$.
  
The model-estimated proportion of the escapement observed during an aerial survey of Montana Creek was `r CI(t5)`(Table 1). Empirical estimates of observability (survey count/weir count) exist for `r et2_n` years and were `r et2_r[1]` and `r et2_r[2]`. There was good agreement between the Montana Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the East Susitna stock group.  The lognormal standard deviation for the Montana Creek aerial survey regression was `r CI(sa5)`, which is smaller than the median value for the distribution of $\sigma_{AS}$.
  
The estimated proportion of the escapement observed during an aerial survey of Sheep Creek was `r CI(t6)`(Table 1). There was poor agreement between the Sheep Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the East Susitna stock group.  The lognormal standard deviation for the Sheep Creek aerial survey regression was `r CI(sa6)`, which is larger than the median value for the distribution of $\sigma_{AS}$.
  
The model-estimated proportion of the escapement observed during an aerial surveys of Willow Creek was `r CI(t7)`(Table 1). Empirical estimates of observability (survey count/weir count) exist for `r et3_n` years and were `r et3_r[1]`, `r et3_r[2]`, and `r et3_r[3]`. There was good agreement between the Willow Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the East Susitna stock group.  The lognormal standard deviation for the Willow Creek aerial survey regression was `r CI(sa7)`, which is smaller than the median value for the distribution of $\sigma_{AS}$.
  
Estimates of population parameters from the state-space model take uncertainty in estimated escapement S and recruitment R (Figure 8 error bars) into account. The individual data pairs are weighted depending upon the certainty with which the individual values of S and R are known. Because escapement and recruitment are poorly known for many brood years, and due to other sources of uncertainty, Ricker S-R relationships that could have plausibly generated the observed data are diverse (Figure 8: light lines), often deviating substantially from the median Ricker relationship (Figure 8: heavy dashed line).
  
Median productivity (recruits per spawner, in the absence of density effects) of East Susitna Chinook salmon during 1979–2017 has been moderate ($\textrm{ln}(\alpha)$ = `r CI(lna2)`; Table 3). There is a great deal of uncertainty about productivity, as evident in the extent to which the plausible S-R relationships differ with respect to their slope at the origin (Figure 8). Similarly, uncertainty about $\beta$ is reflected in variability in the escapements leading to maximum recruitment $S_{MSR}$, and uncertainty about equilibrium abundance, $S_{EQ}$, is reflected by variability in the escapements where the curves intersect the replacement line. Variability in maximum sustained yield is harder to visualize. Graphically, this is the escapement which maximizes the length of a vertical line drawn from the Ricker curve downward to the replacement line. Given the diversity of plausible S-R relationships (Figure 8), it is important to choose an escapement goal that is robust to this uncertainty rather than one tailored solely to the median S-R relationship. To address this uncertainty, we tallied the success or failure of a given number of spawners in achieving biological reference points across plausible S-R relationships in the optimal yield, optimal recruitment and overfishing profiles (Figure 9).
  
East Susitna Chinook salmon escapement leading to maximum sustained yield $S_{MSY}$ was estimated to be `r CI(SMSY2)`. The optimal yield profiles in Figure 9 (top panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSY. These probabilities, which are highest near $S_{MSY}$ can be used to quantify the yield performance of prospective escapement goals (Figure 9 pink-shaded areas), taking into consideration all uncertainty about the true abundance and productivity of the stock. The overfishing profiles (Figure 9 middle panel) show the probability that sustained yield would be reduced to less than 70%, 80%, or 90% of MSY by fishing too hard and supplying too few spawners. For this stock, these probabilities are nearly the exact complements of the probabilities in the left-hand limbs of the optimal yield profiles.
  
Expected sustained yield (number of fish over and above that necessary to replace the number of spawners, averaged over brood years 1979–2015) is also maximized at $S_{MSY}$ (Figure 10). The East Susitna stock group has produced a yield for most broods (Figure 8), although not for a prolonged period in the early part of this century. Median return per spawner has varied between `r rs(2)$min` and `r rs(2)$max` for East Susitna Chinook salmon with `r rs(2)$n` of 36 complete brood years failing to replace themselves. 
  
Escapement leading to maximum recruitment $S_{MSR}$ was estimated to be `r CI(SMSR2)`(Table 3). Analogous to the optimum yield profiles discussed above, optimum recruitment profiles tally the success or failure of a given number of spawners to maximize recruitment across plausible S-R relationships. The optimal recruitment profiles in Figure 9 (bottom panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSR. Optimum recruitment probabilities, which are highest near $S_{MSR}$, reach maximums at larger spawning abundances than optimum yield probabilities and decrease more slowly as spawning abundance increases.
  
##Talkeetna
```{r echo=FALSE, include=FALSE}
NIR3cv <- digits(range(c(IR[IR$stock == 3, ]$cv, 
                        N[N$stock == 3, ]$cv)))
S3cv <- digits(range(S[S$stock == 3, ]$cv))
R3cv <- digits(range(R[R$stock == 3, ]$cv))

D3 <- post$summary[grepl("Dsum.S3", rownames(post$summary)), ]
B3 <- post$summary[grepl("Bsum.So\\[2", rownames(post$summary)), ]

p3out <-digits(post$summary[grepl("p.S3\\[\\d+,3\\]", rownames(post$summary)), "mean"] * 100)

t8 <- post$summary[grepl("theta\\[8,1\\]", rownames(post$summary)), ]
t9 <- post$summary[grepl("theta\\[9,1\\]", rownames(post$summary)), ]

sa8 <- post$summary[grepl("sigma.air\\[8\\]", rownames(post$summary)), ]
sa9 <- post$summary[grepl("sigma.air\\[9\\]", rownames(post$summary)), ]

lna3 <- post$summary[grepl("lnalpha\\[3\\]", rownames(post$summary)), ]

sw3 <- post$summary[grepl("sigma.white\\[3\\]", rownames(post$summary)), ]

phi3 <- post$summary[grepl("phi\\[3\\]", rownames(post$summary)), ]

SMSY3 <- post$summary[grepl("S.msy\\[3\\]", rownames(post$summary)), ]

SMSR3 <- post$summary[grepl("S.max\\[3\\]", rownames(post$summary)), ]

prob_p3 <- get_profileprobs(get_profile(post, "Talkeetna"), c(goals_list[[3]][1], goals_list[[3]][2]))
```
Measures of Talkeetna River Chinook salmon abundance are few, but display a common trend through time (Figure 11). Runs increased through 1998, underwent a decline during 1999--1994, and rebounded until 1997 and gradually declined thereafter. Escapement estimates ranged between `r minrow(S, 3)$median` in `r minrow(S, 3)$year` and `r maxrow(S, 3)$median` in `r maxrow(S, 3)$year` and inriver run estimates ranged from `r minrow(IR, 3)$median` in `r minrow(IR, 3)$year` and `r maxrow(IR, 3)$median` in `r maxrow(IR, 3)$year`.
  
Total and inriver run estimates (Appendix C3) have similar precision as escapement estimates. Coefficients of variation for total and inriver run ranged from `r NIR3cv[1]` to `r NIR3cv[2]` and coefficients of variation for escapement ranged from `r S3cv[1]` to `r S3cv[2]`. Coefficients of variation for recruitment from complete brood years were highly variable (`r R3cv[1]`--`r R3cv[2]`) because of considerable variation in the S-R relationship [$\sigma_W$ = `r CI(sw3)`].
  
Among the surveyed streams within the Talkeetna River stock group Clear Creek has increased in relative abundance between 1979 and 2017 whereas Prairie Creek has decreased in relative abundance (Figure 7, Appendix D2). Clear and Prairie Creeks are similar sized components of the spawning abundance in recent years. The inverse dispersion for the Talkeetna River stock group is small ($D_{comp}$ = `r CI(D3)`, Table 4) indicating trends in the relative magnitude of survey counts and radio telemetry data vary significantly from the multinomial logistic regression model with a calendar year covariate. There is considerable divergence between estimated stock composition and empirical stock composition estimates in some years, which represent situations where weighted relative survey counts and telemetry data disagree.
  
Because unsurveyed streams in the Talkeetna River stock group lack relative composition data early in the time series, no trend can be estimated. Unsurveyed streams compose `r min(p3out)`--`r max(p3out)`% (Figure 7, Appendix D2) of the Talkeetna River stock group. Inverse dispersion is small ($B_{survey}$ = `r CI(B3)`, Table 4) indicating high variability in the proportion of the Talkeetna River stock group spawning within the 2 surveyed streams. High variability was also documented with telemetry data.
  
The estimated proportion of the escapement observed during an aerial surveys of Clear Creek was `r CI(t8)`(Table 1). There was very good agreement between the Clear Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Talkeetna River stock group.  The lognormal standard deviation for the Clear Creek aerial survey regression was `r CI(sa8)`, which is smaller than the median value for the distribution of $\sigma_{AS}$ [`r CI(B)`].
  
The estimated proportion of the escapement observed during an aerial survey of Prairie Creek was `r CI(t9)`(Table 1). There was very good agreement between the Prairie Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Talkeetna River stock group.  The lognormal standard deviation for the Prairie Creek aerial survey regression was `r CI(sa9)`, which is smaller than the median value for the distribution of $\sigma_{AS}$.
  
Estimates of population parameters from the state-space model take uncertainty in estimated escapement S and recruitment R (Figure 12 error bars) into account. The individual data pairs are weighted depending upon the certainty with which the individual values of S and R are known. Because escapement and recruitment are poorly known for many brood years, and due to other sources of uncertainty, Ricker S-R relationships that could have plausibly generated the observed data are diverse (Figure 12: light lines), often deviating substantially from the median Ricker relationship (Figure 12: heavy dashed line).
  
Median productivity (recruits per spawner, in the absence of density effects) of Talkeetna River Chinook salmon during 1979–2017 has been low ($\textrm{ln}(\alpha)$ = `r CI(lna3)`; Table 4). There is a great deal of uncertainty about productivity, as evident in the extent to which the plausible S-R relationships differ with respect to their slope at the origin (Figure 12). Similarly, uncertainty about $\beta$ is reflected in variability in the escapements leading to maximum recruitment $S_{MSR}$, and uncertainty about equilibrium abundance $S_{EQ}$ is reflected by variability in the escapements where the curves intersect the replacement line. Variability in maximum sustained yield is harder to visualize. Graphically, this is the escapement which maximizes the length of a vertical line drawn from the Ricker curve downward to the replacement line. Given the diversity of plausible S-R relationships (Figure 12), it is important to choose an escapement goal that is robust to this uncertainty rather than one tailored solely to the median S-R relationship. To address this uncertainty, we tallied the success or failure of a given number of spawners in achieving biological reference points across plausible S-R relationships in the optimal yield, optimal recruitment and overfishing profiles (Figure 13).
  
Talkeetna River Chinook salmon escapement leading to maximum sustained yield $S_{MSY}$ was estimated to be `r CI(SMSY3)`. The optimal yield profiles in Figure 13 (top panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSY. These probabilities, which are highest near $S_{MSY}$ can be used to quantify the yield performance of prospective escapement goals (Figure 13 pink-shaded areas), taking into consideration the uncertainty about the true abundance and productivity of the stock. The overfishing profiles (Figure 13 middle panel) show the probability that sustained yield would be reduced to less than 70%, 80%, or 90% of MSY by fishing too hard and supplying too few spawners. For this stock, these probabilities are nearly the exact complements of the probabilities in the left-hand limbs of the optimal yield profiles.
  
Expected sustained yield (number of fish over and above that necessary to replace the number of spawners, averaged over brood years 1979–2015) is also maximized at $S_{MSY}$ (Figure 14). The Talkeetna River stock group has failed to produce a yield frequently (Figure 12), partially due to the escapements near $S_{eq}$ and partially due to the low productivity of the stock. Median return per spawner has varied between `r rs(3)$min` and `r rs(3)$max` for Talkeetna River Chinook salmon with `r rs(3)$n` of 36 complete brood years failing to replace themselves.

Escapement leading to maximum recruitment $S_{MSR}$ was estimated to be `r CI(SMSR3)`(Table 4). Analogous to the optimum yield profiles discussed above optimum recruitment profiles tally the success or failure of a given number of spawners to maximize recruitment across plausible S-R relationships. The optimal recruitment profiles in Figure 13 (bottom panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSR. Optimum recruitment probabilities, which are highest near $S_{MSR}$, reach maximums at larger spawning abundances than optimum yield probabilities and decrease more slowly as spawning abundance increases.

##Yentna
```{r echo=FALSE, include=FALSE}
NIR4cv <- digits(range(c(IR[IR$stock == 4, ]$cv, 
                        N[N$stock == 4, ]$cv)))
S4cv <- digits(range(S[S$stock == 4, ]$cv))
R4cv <- digits(range(R[R$stock == 4, ]$cv))

D4 <- post$summary[grepl("Dsum.S4", rownames(post$summary)), ]
B4 <- post$summary[grepl("Bsum.So\\[3", rownames(post$summary)), ]

p4out <-digits(post$summary[grepl("p.S4\\[\\d+,5\\]", rownames(post$summary)), "mean"] * 100)

t10 <- post$summary[grepl("theta\\[10,1\\]", rownames(post$summary)), ]
t11 <- post$summary[grepl("theta\\[11,1\\]", rownames(post$summary)), ]
t12 <- post$summary[grepl("theta\\[12,1\\]", rownames(post$summary)), ]
t13 <- post$summary[grepl("theta\\[13,1\\]", rownames(post$summary)), ]

sa10 <- post$summary[grepl("sigma.air\\[10\\]", rownames(post$summary)), ]
sa11 <- post$summary[grepl("sigma.air\\[11\\]", rownames(post$summary)), ]
sa12 <- post$summary[grepl("sigma.air\\[12\\]", rownames(post$summary)), ]
sa13 <- post$summary[grepl("sigma.air\\[13\\]", rownames(post$summary)), ]

lna4 <- post$summary[grepl("lnalpha\\[4\\]", rownames(post$summary)), ]

sw4 <- post$summary[grepl("sigma.white\\[4\\]", rownames(post$summary)), ]

phi4 <- post$summary[grepl("phi\\[4\\]", rownames(post$summary)), ]

SMSY4 <- post$summary[grepl("S.msy\\[4\\]", rownames(post$summary)), ]

SMSR4 <- post$summary[grepl("S.max\\[4\\]", rownames(post$summary)), ]

prob_p4 <- get_profileprobs(get_profile(post, "Yentna"), c(goals_list[[4]][1], goals_list[[4]][2]))
```
Some of the measures of Yentna River Chinook salmon abundance display a common trend through time (Figure 15). Runs increased through 1984, underwent a decline during 1985--1994, and rebounded until 2004, declined through 2009, increased through 2015, and declined to historically low levels in 2017. Escapement estimates ranged between `r minrow(S, 4)$median` in `r minrow(S, 4)$year` and `r maxrow(S, 4)$median` in `r maxrow(S, 4)$year` and inriver run estimates ranged from `r minrow(IR, 4)$median` in `r minrow(IR, 4)$year` to `r maxrow(IR, 4)$median` in `r maxrow(IR, 4)$year`.
  
Total and inriver run estimates (Appendix C4) have similar precision as escapement estimates. Coefficients of variation for total and inriver run ranged from `r NIR4cv[1]` to `r NIR4cv[2]` and coefficients of variation for escapement ranged from `r S4cv[1]` to `r S4cv[2]`. Coefficients of variation for recruitment from complete brood years were moderate (`r R4cv[1]`--`r R4cv[2]`) reflective of moderate variation in the S-R relationship [$\sigma_W$ = `r CI(sw4)`].
  
Among the surveyed streams within the Yentna River stock group, Peters Creek has increased in relative abundance between 1979 and 2017 whereas Cache Creek has decreased in relative abundance and Lake Creek and Talachulitna River have remained stable(Figure 7, Appendix D3). Lake Creek is the largest component of spawning abundance in recent years followed by Talachulitna River, Peters Creek and Cache Creek. The inverse dispersion for the Yentna River stock group is moderate ($D_{comp}$ = `r CI(D4)`, Table 5), indicating trends in the relative magnitude of survey counts and radio telemetry data are fairly well explained by the multinomial logistic regression model with a calendar year covariate. Estimated stock composition and empirical stock composition estimates are similar.
  
Because unsurveyed streams in the Yentna River stock group lack relative composition data early in the time series, no trend can be estimated. Unsurveyed streams compose `r min(p4out)`--`r max(p4out)`% (Figure 7, Appendix D3) of the Yentna River stock group. Inverse dispersion is moderate ($B_{survey}$ = `r CI(B4)`, Table 5) indicating moderate variability in the proportion of the Yentna River stock group spawning within the 4 surveyed streams. Moderate variability was documented with telemetry data.
  
The estimated proportion of the escapement observed during an aerial survey of Cache Creek was `r CI(t10)`(Table 1). There was very poor agreement between the Cache Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Yentna River stock group.  The lognormal standard deviation for the Cache Creek aerial survey regression was `r CI(sa10)`, which is larger than the median value for the distribution of $\sigma_{AS}$ [`r CI(B)`].
  
The estimated proportion of the escapement observed during an aerial survey of Lake Creek was `r CI(t11)`(Table 1). There was very good agreement between the Lake Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Yentna River stock group.  The lognormal standard deviation for the Lake Creek aerial survey regression was `r CI(sa11)`, which is smaller than the median value for the distribution of $\sigma_{AS}$.
  
The estimated proportion of the escapement observed during an aerial survey of Peters Creek was `r CI(t12)`(Table 1). There was very poor agreement between the Peters Creek single aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Yentna River stock group.  The lognormal standard deviation for the Peters Creek aerial survey regression was `r CI(sa12)`, which is larger than the median value for the distribution of $\sigma_{AS}$.
  
The estimated proportion of the escapement observed during an aerial survey of the Talachulitna River was `r CI(t13)`(Table 1). There was average agreement between Talachulitna River aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Yentna River stock group.  The lognormal standard deviation for the Talachulitna River aerial survey regression was `r CI(sa13)`, which is similar to the median value for the distribution of $\sigma_{AS}$.
  
Estimates of population parameters from the state-space model take uncertainty in estimated escapement S and recruitment R (Figure 16 error bars) into account. The individual data pairs are weighted depending upon the certainty with which the individual values of S and R are known. Because escapement and recruitment are poorly known for many brood years, and due to other sources of uncertainty, Ricker S-R relationships that could have plausibly generated the observed data are diverse (Figure 16: light lines), often deviating substantially from the median Ricker relationship (Figure 16: heavy dashed line).
  
Median productivity (recruits per spawner, in the absence of density effects) of Yentna River Chinook salmon during 1979–2017 has been moderate  ($\textrm{ln}(\alpha)$ = `r CI(lna4)` Table 5). There is a great deal of uncertainty about productivity, as evident in the extent to which the plausible S-R relationships differ with respect to their slope at the origin (Figure 16). Similarly, uncertainty about $\beta$ is reflected in variability in the escapements leading to maximum recruitment $S_{MSR}$, and uncertainty about equilibrium abundance $S_{EQ}$ is reflected by variability in the escapements where the curves intersect the replacement line. Variability in maximum sustained yield is harder to visualize. Graphically, this is the escapement which maximizes the length of a vertical line drawn from the Ricker curve downward to the replacement line. Given the diversity of plausible S-R relationships (Figure 16), it is important to choose an escapement goal that is robust to this uncertainty rather than one tailored solely to the median S-R relationship. To address this uncertainty, we tallied the success or failure of a given number of spawners in achieving biological reference points across plausible S-R relationships in the optimal yield, optimal recruitment and overfishing profiles (Figure 17).
  
Yentna River Chinook salmon escapement leading to maximum sustained yield $S_{MSY}$ was estimated to be `r CI(SMSY4)`. The optimal yield profiles in Figure 17 (top panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSY. These probabilities, which are highest near $S_{MSY}$ can be used to quantify the yield performance of prospective escapement goals (Figure 17 pink-shaded areas), taking into consideration all uncertainty about the true abundance and productivity of the stock. The overfishing profiles (Figure 17 middle panel) show the probability that sustained yield would be reduced to less than 70%, 80%, or 90% of MSY by fishing too hard and supplying too few spawners. For this stock, these probabilities are nearly the exact complements of the probabilities in the left-hand limbs of the optimal yield profiles.
  
Expected sustained yield (number of fish over and above that necessary to replace the number of spawners, averaged over brood years 1979–2015) is also maximized at $S_{MSY}$ (Figure 18). Many brood years from the Yentna River stock group have produced a yield (Figure 16), with most exceptions coming from escapement at or above $s_{EQ}$. Medain return per spawner varied between between `r rs(4)$min` and `r rs(4)$max` for Yentna River Chinook salmon with `r rs(4)$n` of 36 complete brood years failing to replace themselves.
  
Escapement leading to maximum recruitment $S_{MSR}$ was estimated to be `r CI(SMSR4)`(Table 5). Analogous to the optimum yield profiles discussed above optimum recruitment profiles tally the success or failure of a given number of spawners to maximize recruitment across plausible S-R relationships. The optimal recruitment profiles in Figure 17 (bottom panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSR. Optimum recruitment probabilities, which are highest near $S_{MSR}$, reach maximums at larger spawning abundances than optimum yield probabilities and decrease more slowly as spawning abundance increases.
  
##Age Composition
```{r echo=FALSE, include=FALSE}
ageD <- age[grepl("Deshka", age$stock), ]
ageES <- age[grepl("East Susitna", age$stock), ]
ageT <- age[grepl("Talkeetna", age$stock), ]
ageY <- age[grepl("Yentna", age$stock), ]

p1 <- digits(range(post$summary[grepl("p\\[\\d+,1\\]", rownames(post$summary)), "mean"])*100)
p2 <- digits(range(post$summary[grepl("p\\[\\d+,2\\]", rownames(post$summary)), "mean"])*100)
p3 <- digits(range(post$summary[grepl("p\\[\\d+,3\\]", rownames(post$summary)), "mean"])*100)
p4 <- digits(range(post$summary[grepl("p\\[\\d+,4\\]", rownames(post$summary)), "mean"])*100)
```
Between `r min(intersect(ageD$year, intersect(ageES$year, ageY$year)))` and `r max(intersect(ageD$year, intersect(ageES$year, ageY$year)))` annual age composition datasets exist from sport harvested Chinook salmon in the Deshka, East Susitna and Yentna stock groups. In general, East Susitna Chinook salmon contain larger proportions of older fish (Figure 19, middle panel). Between `r min(intersect(ageD$year, intersect(ageES$year, ageT$year)))` and `r max(intersect(ageD$year, intersect(ageES$year, ageT$year)))` annual age composition datasets exist for both the sport harvest and inriver run of Chinook salmon in the East Susitna, Deshka and Talkeetna stock groups. Deshka Chinook salmon contain smaller proportions of older fish in paired annual samples. 
  
Chinook salmon in the Susitna River Drainage are composed of age-3(1.1), age-4(1.2), age-5(1.3) and age-6 (1.4) fish (Figure 19 middle panel, Table 6). Throughout the time series age-5 fish have been the predominate age class whereas the relative abundance of age-6 fish has steadily decreased and the relative abundance of age-3 fish has increased (dramatically in recent years).
  
Susitna River Chinook salmon matured (Figure 19 top panel, Table 7) at age-3 (`r p1[1]`--`r p1[2]`%), age-4 (`r p2[1]`--`r p2[2]`%), age-5 (`r p3[1]`--`r p3[2]`%) and age-6 (`r p4[1]`--`r p4[2]`%). Age-at-maturity has trended strongly toward increasing contributions of age-3, age-4 and age-5 fish and decreasing contributions of age-6 fish.
  
# Discussion
## Some Susitna River Chinook salmon are ommited from this analysis
The four stock groups listed above do not cover the entire Susitna River drainage. Alexander Creek, upstream tributaries (notably Chulitna River but also Indian Creek and Portage Creek) and the mainstem of the Susitna River are not included. All of these areas are excluded because we lack quality data to inform the S-R model. Mark-recapture estimates of abundance were only germane to the Susitna River upstream of the confluence with Alexander Creek, so we lack an absolute abundance estimate for the entire drainage. Weir estimates of Alexander Creek Chinook salmon are available in recent years but the drainage was previously colonized by northern pike, and the stock recruit relationship probably changed as a result. Mark-recapture estimates do exist for upstream spawning areas and the mainstem Susitna River although we could not identify a relationship between mark-recapture estimates and aerial survey data in those areas.
  
## Why manage using stock groups instead of individual spawning tributaries?
Aerial surveys conducted only once per year are subject to many possible sources of error. The ability to see spawning Chinook salmon from the air varies daily based on water depth, water clarity, and ambient light conditions. Early or late spawning Chinook salmon may not even be present during the survey and the fraction of the escapement missed will vary annually based on run timing and survey timing. Herein we use the term "observability" to capture both of these effects. ADF&G has a standardized aerial survey program for the Susitna River drainage that attempts to minimize variability due to these factors and provide consistency throughout the time series. Remaining annual variability is confounded with variability in stock composition and quantified by the lognormal error term from the relationship between survey counts and estimated escapement eq. $\@ref(eq:as)$.
  
The currently existing goals within the Susitna River drainage (with the exception of the Deshka River) are based on once-per-year aerial surveys without accounting for the variability described above. This approach is fragile because escapement goal determinations are made based on a single data point which only indexes abundance. Our approach offers two fundamental improvements. First, multiple annual aerial surveys are used to make each run size determination. For example, in the East Susitna stock group instead of making 6 run size determinations using a single data point (one for each surveyed tributary in the East Susitna stock group) we make a single run size determination using 6 data points. Secondly, our approach considers variability in observability and stock composition to effectively weight each survey count by it's relative accuracy. 
  
Although current escapement goals are for individual spawning stocks, Susitna River Chinook salmon stocks are already managed using the stock groupings presented herein. These groups make sense as a management tool for several reasons. First, although annual abundance in each stock group (Figure 20) is somewhat correlated there are differences in temporal patterns for each group. For example, although all stocks have been near historical minimums in the last 10 years, the Deshka River stock was also near historical minimums in the middle 1990's at a time when the East Susitna stock was doing well. A second example can be seen in 2004 when Deshka and Yentna stocks were at historical maximums, East Susitna was very large and Talkeetna was middling. Stock groups also differ in data quantity and quality which can affect management. For example, Deshka River weir counts are by far the most precise estimates available allowing management actions pertaining to Deshka River Chinook salmon to be made inseason and with more confidence. In contrast, Yentna River estimates are imprecise and suggest a cautious approach.

This analysis suggests there are productivity differences between stock groups.  Although the confidence intervals all overlap, stock productivity $\textrm{ln}(\alpha_s)$ for the Talkeetna group may be lower than the other stocks. In general, more productive stocks can support larger yields. Stock groups also differ in productivity through the time series. Ricker recruitment residuals in Figure 21 are deviations in recruitment of Chinook salmon for each stock group from that predicted by the Ricker S-R relationship, reflecting time-varying changes in productivity after controlling for density-dependent effects. Recruitment residuals relate to trends in total run size. A general pattern of above-average productivity occurred through the 2001 brood year, although the Deshka River had an extended period of below-average productivity between the 1987 and 1991 brood years. In recent broods, all stocks have experienced below average productivity between the 2003 and 2014 brood years although the low productivity period in the East Susitna stock group  was the longest and most consistent. Examination of the Ricker residuals in conjunction with the horsetail plot (Figure 8) suggests two productivity regimes for the East Susitna stock group, with recent productivity considerably lower than average productivity, although a mechanism driving this pattern is unknown. Residual correlation is strong for the East Susitna stock group (Table 3), supporting the concept of time-varying productivity, which is non-existent for the Talkeetna stock group (Table 4) and intermediate for the Deshka (Table 2) and Yentna stock groups (Table 5).
  
Fishing power also differs for the 4 stock groups. In magnitude, the largest historical harvest rates (Figure 22) have been recorded on the East Susitna stock group, reflecting the greatest fishing power. Deshka River Chinook salmon have moderate historical harvest rates whereas Yentna and Talkeetna River stock groups have small historical harvest rates. None of these stocks have been fished historically at rates that would theoretically maximize yield. East Susitna and Talkeetna River Chinook salmon have historically been fished at rates that would maximize recruitment.
  
## Escapement Goal Recommendations
### Deshka River
Deshka River Chinook salmon have an existing goal range of 13,000--27,000 Chinook salmon. Escapements at the low end of the existing range have a `r prob_e[[1, "OYP80"]]`% probability of producing a yield greater than 80% of MSY whereas escapements at the upper end of the existing range have a `r prob_e[[2, "OYP80"]]`% probability of producing yields greater than 80% or MSY. With respect to recruitment, escapements at the low end of the existing range have a `r prob_e[[1, "ORP80"]]`% probability of producing a recruitment greater than 80% of MSR whereas escapements at the upper end of the existing range have a `r prob_e[[2, "ORP80"]]`% probability of producing a recruitment greater than 80% or MSR. 
  
*Describe procedure.*
  
The proposed escapement goal has a `r prob_p[[1, "OYP80"]]`% probability of achieving 80+% of MSY at the lower bound and a `r prob_p[[2, "OYP80"]]`% probability of achieving 80+% MSY at the upper bound. With respect to recruitment, the proposed escapement goal shown has a `r prob_p[[1, "ORP80"]]`% probability of achieving 80+% of MSR at the lower bound and a `r prob_p[[2, "ORP80"]]`% probability of achieving 80+% of MSR at the upper bound.

### East Susitna
Goose Creek, Little Willow Creek, Montana Creek, Sheep Creek and Willow Creek have existing goals based on single aerial survey data. Existing goals use 6 pieces of information (6 once-per-year aerial survey counts) to make 6 run size determinations without considering observability of each survey. This analysis leverages the same 6 pieces of information to make one run size determination while accounting for correlation in run sizes between the sub stocks and variability in survey observability.
  
*Describe procedure.*
  
The proposed escapement goal has a `r prob_p2[[1, "OYP80"]]`% probability of achieving 80+% of MSY at the lower bound and a `r prob_p2[[2, "OYP80"]]`% probability of achieving 80+% of MSY at the upper bound. With respect to recruitment, the proposed escapement goal has a `r prob_p2[[1, "ORP80"]]`% probability of achieving 80+% of MSR at the lower bound and a `r prob_p2[[2, "ORP80"]]`% probability of achieving 80+% of MSR at the upper bound.
  
### Talkeetna River
Clear Creek and Prairie Creek have existing goals based on once-per-year aerial survey data. Existing goals use 2 pieces of information (2 single aerial survey counts) to make 2 run size determinations without considering observability of each survey. This analysis leverages the same 2 pieces of information to make one run size determination while accounting for correlation in run sizes between the sub stocks and variability in survey observability. 
  
*Describe procedure.*
  
The proposed escapement goal has a `r prob_p3[[1, "OYP80"]]`% probability of achieving 80+% of MSY at the lower bound and a `r prob_p3[[2, "OYP80"]]`% probability of achieving 80+% of MSY at the upper bound. With respect to recruitment, the proposed escapement goal has a `r prob_p3[[1, "ORP80"]]`% probability of achieving 80+% of MSR at the lower bound and a `r prob_p3[[2, "ORP80"]]`% probability of achieving 80+% of MSR at the upper bound.
  
### Yentna River
Lake Creek, Peters Creek and Talachulitna River have existing goals based on single aerial survey data. Existing goals use 3 pieces of information (3 single aerial survey counts) to make 3 run size determinations without considering observability of each survey. This analysis leverages 4 pieces of information to make one run size determination while accounting for correlation in run sizes between the sub stocks and variability in survey observability.
  
*Describe procedure.*
  
The proposed escapement goal has a `r prob_p4[[1, "OYP80"]]`% probability of achieving 80+% of MSY at the lower bound and a `r prob_p4[[2, "OYP80"]]`% probability of achieving 80+% of MSY at the upper bound. With respect to recruitment, the proposed escapement goal has a `r prob_p4[[1, "ORP80"]]`% probability of achieving 80+% of MSR at the lower bound and a `r prob_p4[[2, "ORP80"]]`% probability of achieving 80+% of MSR at the upper bound.
  
## Timing of Run Size Assessment
Currently ... 

Run size assessments relative to the escapement goals proposed herein will rely on the run reconstruction model described herein. Becasue the model requires age composition and harvest data, run size assessments will be delayed relative to current practices.

## Summary and Conclusions
**Existing Susitna River Chinook stock assessment relies on 16 once-per-year aerial survey escapement goals but existing Susitna River Chinook salmon management is practiced on 5 stock groups.** Four of these stock groups are included in this assessment. The fifth stock group has never shown up in the ADF&G statewide harvest survey (SWHS).
  
**Run sizes, productivity and fishing power differ between existing management groups.** Proposed escapement goals consider each of these factors separately for each stock group.
  
**Escapement goals for the Susitna River drainage will be periodically reviewed.** All Pacific salmon escapement goals in the state of Alaska are subject to triennial review to allow for consideration of recent data, changes in stock productivity and revised assessment and analysis. The run reconstruction and stock recruit analysis described herein will be revised and improved between stock board cycles.