---
title: "SusitnaEG analysis"
author: "Adam Reimer"
date: "September 4, 2018"
output: 
  bookdown::word_document2:
#    pandoc_args: ["-Fpandoc-crossref"]
    reference_docx: ".\\doc_styles\\word_styles_FDS.docx"
---

```{r setup, echo=FALSE, include=FALSE}
library(bookdown)
knitr::opts_chunk$set(echo = TRUE)
library(SusitnaEG)
post <- readRDS("..\\..\\posts\\SuChinook_8e162f9.rds")
#post <- readRDS("C:\\postsC\\SuChinook_8e162f9.rds")
get_ids()
goals_list <- list(Deshka = c(9000, 18000),
                   Eastside = c(13000, 25000),
                   Talkeetna = c(9000, 17500),
                   Yentna = c(13000, 22000))
```
# Model Description
## State-Space Model
A state-space model (Appendix B1) was developed to generate annual abundance estimates for Susitna River Chinook salmon stocks that could be fit to a spawner-recruitment (S-R) relationship for use in deciding escapement goals based on maximum sustained yield. State-space models contain 2 components: process equations and observation equations. Process equations describe population dynamics that are unobserved but of research interest. In this application we focus on spawning escapements, recruitment from those escapements, and parameters that describe the S-R relationship. Observation equations describe how observed data are generated conditional on population parameters estimated by the process equations. We lack a robust time series of observed abundance and instead model the relationship between abundance and aerial survey data for the purpose of reconstructing historical abundances while incorporating the uncertainty in historical abundance estimates into the S-R parameter estimates.   
  
Many parameters are estimated in this state-space model. Parameters with similar function or interpretation often use the same symbol, distinguished by a subscript capital letter. Subscript lower case letters denote parameter indices. For example, all harvest rates use the symbol $\mu$ where $\mu_{By}$ is the harvest rate below (downstream of) both Susitna RM 34 and Yentna RM 6 in year $y$, and $\mu_{Ays}$ is the harvest rate of stock $s$ above either Susitna RM 34 or Yentna RM 6 in year $y$. Year indices $y$ run from 1 to 39 representing 1979 to 2017 respectively. Age indices $a$ run from 3 to 6 representing total age of returning Chinook salmon where $a=6$ represents fish with a total age of 6 or larger. Stock group indices $s$ run from 1 to 4 representing the Deshka River, East Susitna, Talkeetna River and Yentna River stock groups respectively (Figure 2). 
  
### Process Component
Abundance of Susitna River Chinook salmon in each stock group is generated by a S-R relationship, that describes the number of fish expected to return (the “recruitment”) from a given “escapement” (number of spawning fish). The total recruitment $R_{cs}$ produced from fish spawning in brood year $c$ by stock $s$ follows the Ricker (1975) formulation:
  
\begin{equation}
R_{cs}~=~S_{cs}\alpha_s exp(-\beta_s S_{cs}) (\#eq:ricker)
\end{equation}
  
where $S_{cs}$ is the number of spawners, $\alpha_s$ (number of recruits per spawner in the absence of density dependence) is a measure of productivity for each stock group, and $\beta_s$ is a measure of density dependence for each stock group.

Productivity varies among brood years, fluctuating around a central tendency. Time-varying productivity often manifests as serially correlated model residuals, so a lognormal error term with a lag of one year was included in the linearized form of the S-R relationship (Noakes et al. 1987).
  
\begin{equation}
ln(R_{cs})~=~ln(S_{cs})+ln(\alpha_s)-\beta_s S_{cs} +\phi_s \nu_{(c-1)s}+\epsilon_{Ws} (\#eq:rickerar)
\end{equation}
  
where $\phi_s$ is the lag-1 serial correlation coefficient, $\nu_{cs}$ are model residuals
  
\begin{equation}
\nu_{cs}~=~ln(R_{cs})-ln(S_{cs})-ln(\alpha_s)+\beta_s S_{cs} (\#eq:residuals)
\end{equation}
  
and the $\epsilon_{Ws}$ are independently and normally distributed process errors with “white noise” variance $\sigma^2_{Ws}$. The productivity parameters for each stock are drawn from a common distribution, $\textrm{ln}(\alpha_s)~\sim~\textrm{Normal}(\mu_\alpha, \sigma^2_\alpha)$.  
  
Age at maturity, which is needed to distribute recruitment across calendar years, is allowed to trend through time and fluctuate annually. Age-at-maturity vectors^[These proportions are maturity and survival schedules for a given brood year (cohort) across calendar years. In contrast, Equation \@ref(eq:qstar) describes age proportions of returning fish in a given calendar year across brood years.] $\mathbf{p_c} = (\begin{array}{am} p_{c3} & p_{c4} & p_{c5} & p_{c6} \end{array})$ from brood year $c$ returning at ages 3--6 were drawn from a $\textrm{Dirichlet}(\gamma_{c3}, \gamma_{c4},  \gamma_{c5}, \gamma_{c6})$ distribution. The Dirichlet parameters are expressed in an alternate form where
  
\begin{equation}
D_{age}~=~\sum_{a=3}^6 \gamma_{ca}~~\textrm{for all}~c (\#eq:Dage)
\end{equation}
  
is the (inverse) dispersion^[A low value of $D$ is reflective of a large amount of variability in age-at-maturity proportions $\mathbf{p_c}$ among brood years, whereas a high value of $D$ indicates more consistency in $\mathbf{p_c}$ over time.] of the annual age-at-maturity vectors, reflecting consistency of age at maturity among brood years.
The location parameters
  
\begin{equation}
\pi_{ca}~=~\frac{\gamma_{ca}}{D_{age}}~=~\frac{exp(ML1_a+ML2_ac)}{\sum_{a=3}^6 exp(ML1_a+ML2_ac)} (\#eq:pi)
\end{equation}
  
are proportions that sum to 1 for each brood year and reflect the age-at-maturity central tendency in each year where $ML1_a$ and $ML2_a$ are multinomial logistic regression coefficients describing trending age at maturity.
  
The abundance $N_{yas}$ in stock group $s$ of age $a$ Chinook salmon in calendar year $y$ is the product of the age at maturity scalar $p_{ca}$ and the total return (recruitment) $R_{cs}$ for stock group $s$ from brood year $c=y−a$:
  
\begin{equation}
N_{yas}~=~p_{(y-a)a}R_{(y-a)s} (\#eq:Ntas)
\end{equation}
  
Total run $N_{ys}$ for stock group $s$ during calendar year $y$ is the sum of abundance at age across all ages:
  
\begin{equation}
N_{ys}~=~\sum_{a=3}^6 N_{yas} (\#eq:Nts)
\end{equation}
  
Annual harvest of Susitna-origin Chinook salmon below (downstream of) both Susitna RM 34 and Yentna RM 6, $H_{By}$, was modeled as the product of the annual harvest rate in the downstream area $\mu_{By}$, and total run $N_y$:
  
\begin{equation}
H_{By}~=~\mu_{By}\sum_{s=1}^4 N_{ys} (\#eq:Hbelow)
\end{equation}
  
Inriver run $IR_{ys}$ of stock group $s$ during calendar year $y$ at either Susitna RM 34 or Yentna RM 6 was modeled as the product of stock specific total run $N_{ys}$ and the annual survival rate in the area downstream:
  
\begin{equation}
IR_{ys}~=~N_{ys}(1-\mu_{By}) (\#eq:IR)
\end{equation}
  
Annual harvest of stock group $s$ above either Susitna RM 34 or Yentna RM 6, $H_{Ays}$, was the product of the annual harvest rate for each stock in the upstream area $\mu_{Ays}$ and the inriver run of stock group $s$:
  
\begin{equation}
H_{Ays}~=~\mu_{Ays}IR_{ys} (\#eq:Habove)
\end{equation}
  
Annual harvest of Deshka River Chinook salmon ($s$ = 1) upstream of the Deshka River weir, $H_{DESHKAy}$, was a proportion $p_{DESHKAy}$ of the total inriver harvest of Deshka River Chinook salmon $H_{Ay1}$:
  
\begin{equation}
H_{DESHKAy}~=~p_{DESHKAy}H_{Ay1} (\#eq:Hdeshka)
\end{equation}
  
The $p_{DESHKAy}$ are drawn from a $\textrm{Beta}(b1_D, b2_D)$ distribution. The beta parameters are expressed in an alternate form where $B_D~=~b1_D+b2_D$ is the (inverse) dispersion and the location is drawn from a non-informative beta prior.
  
Spawning escapement $S_{ys}$ was inriver run abundance minus harvest above Susitna RM 34 or Yentna RM 6:
  
\begin{equation}
S_{ys}~=~IR_{ys}-H_{Ays} (\#eq:S)
\end{equation}
  
Finally, Chinook salmon passage at the Deshka River weir was the sum of the spawning escapement in the Deshka River, $S_{y1}$, and harvest upstream of the weir:   
\begin{equation}
IR_{DESHKAy}~=~S_{y1}+H_{DESHKAy} (\#eq:dweir)
\end{equation}
  
Multiple tributaries ($t=1,2,\dots,T_s$) contribute to the spawning escapement in the East Susitna, Talkeetna, and Yentna stock groups. The relative composition of individual spawning tributaries within each stock is of interest because some observed data is germane to the tributary scale. Stock compositions of the $T_s-1$ tributaries that are monitored by aerial survey are allowed to fluctuate annually around a trending central tendency. Four sets of equations analogous to Equations \@ref(eq:Dage) and \@ref(eq:pi) were used to define stock composition vectors $\mathbf{\rho^*}_{sy} = (\begin{array}{} \rho^*_{sy1} & \rho^*_{sy2 } & \dots & \rho^*_{sy(T_s-1)}\end{array})$ for the surveyed tributaries in each stock group.
  
The annual proportion of fish from stock $s$ that spawned in tributaries that were not monitored by aerial survey, $\rho\prime_{sy}$, are drawn from a $\textrm{Beta}(b1_s, b2_s)$ distribution. The beta parameters are expressed in an alternate form where $B_s~=~b1_s+b2_s$ is the (inverse) dispersion and the location is drawn from a non-informative beta prior.
  
Stock composition was calculated as follows:
    
\begin{equation}
\mathbf{\rho_{sy}}~=~\left(\begin{array}{} \rho^*_{sy1}(1-\rho\prime_{sy}) & \rho^*_{sy2}(1-\rho\prime_{sy}) & \dots & \rho^*_{syT_s}(1-\rho\prime_{sy}) &  \rho\prime_{sy} \end{array}\right) (\#eq:pcomp)
\end{equation}
   
### Observation Component
Observed data (Appendices A1--A10) include mark-recapture estimates of inriver run; estimates of annual marine commercial and subsistence harvests below both Susitna RM 34 and Yentna RM 6, freshwater sport harvests above Susitna RM 34 or Yentna RM 6, and freshwater sport harvest above the Deshka weir; radiotelemetry data; aerial survey data for `r sum(sapply(as, function(x){dim(x)[2]}))` tributaries; weir counts for `r dim(weir)[2]` tributaries; age composition data from throughout the Susitna River drainage; and length composition data from the Deshka weir. . Sampling distributions for the observed data are given below.
  
#### Inriver Run and Length Composition
Estimated annual inriver runs of Chinook salmon for stock $s$, $\widehat{IR}_{ys}$, from mark-recapture data were
  
\begin{equation}
\widehat{IR}_{ys}~=~IR_{500ys}exp(\epsilon_{IRys}) (\#eq:IRhat)
\end{equation}
  
where $IR_{500ys}$ is the inriver run of fish 500 mm mid eye to tail fork (METF) length or larger, $\epsilon_{IRys}~\sim~\textrm{Normal}(0, \sigma^2_{IRys})$, and $\sigma^2_{IRys}$ is calculated from the coefficient of variation (CV) of $\widehat{IR}_{ys}$:
  
\begin{equation}
\sigma^2_{IR_{ys}}~=~\textrm{ln}(\textrm{CV}(\widehat{IR}_{ys})^2+1) (\#eq:cvIR)
\end{equation}
  
The numbers of age-3 or age-4 fish that were less than 500 mm METF, in year $y$, $x_{500ya}$, were
  
\begin{equation}
x_{500ya}~\sim~\textrm{Binomial}(p_{500ya}, n_{500ya}) (\#eq:xsmall)
\end{equation}
  
where $n_{500ya}$ is the  total number of fish sampled for age and length in age class $a$ during year $y$ and $p_{500ya}$ is the proportion of fish less than 500 mm METF in age class $a$ (3 or 4) during year $y$.
  
Inriver runs of fish 500 mm METF or greater, $IR_{500ys}$, were
  
\begin{equation}
IR_{500ys}~=~IR_{ys}[1-(q_{y3}p_{500y3}+q_{y4}p_{500y4})] (\#eq:IRlarge)
\end{equation}
  
where $q_{ya}$ is the proportion of the run that is age $a$ in calendar year $y$.
  
#### Harvest
Estimated annual harvest of Susitna River Chinook salmon below both Susitna RM 34 and Yentna RM 6 ,$\widehat{H}_{By}$, was
  
\begin{equation}
\widehat{H}_{By}~=~H_{By}exp(\epsilon_{HBy}) (\#eq:HBhat)
\end{equation}
  
where the $\epsilon_{HBy}~\sim~\textrm{Normal}(0, \sigma^2_{HBy})$ and the variances followed Equation \@ref(eq:cvIR). Estimated annual harvest of Susitna River Chinook salmon above either Susitna RM 34 or Yentna RM 6, $\widehat{H}_{Ays}$ for stock $s$ was generated according to Equation \@ref(eq:HBhat) after substituting ${H}_{Ays}$ and $\epsilon_{HAys}$ for ${H}_{By}$ and $\epsilon_{HBy}$, respectively, where the $\epsilon_{HAys}~\sim~\textrm{Normal}(0, \sigma^2_{HAys})$ and the variances followed Equation \@ref(eq:cvIR). Similarly, estimated annual harvest of Deshka River Chinook salmon upstream of the Deshka weir, $\widehat{H}_{Dy}$, was generated according to Equation \@ref(eq:HBhat) after substituting ${H}_{Dy}$ and $\epsilon_{HDy}$ for ${H}_{By}$ and $\epsilon_{HBy}$, respectively, where the $\epsilon_{HDy}~\sim~\textrm{Normal}(0, \sigma^2_{HDy})$ and the variances followed Equation \@ref(eq:cvIR).
  
#### Radiotelemetry
Radio telemetry data (counts of radio tagged fish) within each stock group $\mathbf{r}_{sy} = (\begin{array}{} r_{sy1} & r_{sy2} & \dots & r_{syT_s} \end{array})$ were partitioned into $T_s$ categories with $T_s-1$ categories representing numbers of Chinook salmon located within tributaries that are counted during aerial surveys and 1 category ($T_s$) representing the number of Chinook salmon located within the stock group but outside of tributaries counted during aerial surveys. The number of radio tags located in tributaries that were not counted during aerial surveys were
  
\begin{equation}
r_{syT_s}~\sim~\textrm{Binomial}\left(\rho\prime_{sy}, \sum_{t=1}^{T_s} r_{syt}\right) (\#eq:nosurvey)
\end{equation}
  
The number of radio tags located within tributaries that were counted during aerial surveys, $r_{sy[1:(T_s-1)]}$, were as follows:
  
\begin{equation}
r_{sy[t=1:(T_s-1)]}~\sim~\textrm{Multinomial}\left(\rho^*_{sy[t=1:(T_s-1)]}, \sum_t^{T_s-1} r_{syt}\right) (\#eq:survey)
\end{equation}
  
where $\rho^*_{syt}$ estimates the annual proportion of radiotagged fish from surveyed tributaries within stock $s$ that spawned in tributary $t$.
  
#### Abundance Indices
Abundance information for tributaries within stock groups were available for `r sum(sapply(as, function(x){dim(x)[2]}))` index streams $i$. Annual aerial survey counts, $as_{yi}$, are related to abundance for the stock group within which it was located after accounting for survey observability $\theta_i$ and stock composition $\rho_{s_{(i)}yt_{(i)}}$:
  
\begin{equation}
as_{yi}~=~\theta_i\rho_{s_{(i)}yt_{(i)}}S_{ys_{(i)}}exp(\epsilon_{ASi}) (\#eq:as)
\end{equation}
  
where $\epsilon_{ASi}~\sim~\textrm{Normal}(0, \sigma^2_{ASi})$. In \@ref(eq:as) $s_{(i)}$ and $t_{(i)}$ are functions that map the index stream identifier $i$ to the stock group $s$ and tributary $t$ identifiers respectively. The proportion of the spawning escapement in stock group $s(i)$ counted during aerial surveys $\theta_i$ was modeled hierarchically $\textrm{logit}(\theta_i)~\sim~\textrm{Normal}(\mu_\theta, \sigma^2_\theta)$.

Survey specific residual standard deviations were modeled hierarchically $\sigma_{ASi}~\sim~\textrm{half_Cauchy}(0, C_{AS})$ where $C_{AS}$ is the median of the distribution of $\sigma_{ASi}$ (Lunn et al, 2013). Because modeled observability of spawning Chinook salmon, $\theta_i$, is treated as constant, annual variability in observability is confounded with annual variability in stock composition, $\rho_{s_{(i)}yt_{(i)}}$, and included in $\sigma_{ASi}$. Also note that stock composition was only observed late in the time series (2012--2017) and modeled trends in stock composition in the remainder result from changes in the relative magnitude of aerial survey counts. Thus the relative magnitude of survey counts are assumed to reflect stock composition^[While trending stock-specific observability could result in similar data we believe consistent survey procedures utilized throughout the time series make this possibility less likely.].  

Weirs counts were available for `r dim(weir)[2]` of the index streams. Each weir count is related to abundance for the stock group within which it was located after accounting for stock composition:
  
\begin{equation}
  w_{yi} = \begin{cases} \rho_{s_{(i)}yt_{(i)}}IR_{DESHKAy}exp(\epsilon_{W}), & \mbox{if } s\mbox{ = 1} \\ 
  \rho_{s_{(i)}yt_{(i)}}S_{ys_{(i)}}exp(\epsilon_{W}), & \mbox{if } s\ne\mbox{1} 
  \end{cases} (\#eq:weir) 
\end{equation}
  
where the $\epsilon_{W}~\sim~\textrm{Normal}(0, \sigma_{W}^2)$ and the variances followed Equation \@ref(eq:cvIR) with an assumed CV of 0.05 reflecting good precision associated with weir counts.
  
#### Age Composition
A total of `r dim(post$data$x.a)[1]` age composition dataset were collected from stock-specific locations between `r min(year_id)` and `r max(year_id)`. The Deshka stock group is represented throughout the time series, but most other stock groups are represented only early in the time series. We deemed this resolution insufficient to model age composition independently for each stock group, and focused on modeling the age composition of the the run to the entire Susitna River drainage. The model assumes fish were harvested in proportion to return-by-age. Age composition may differ between stock groups, and multinomial logistic regression was used to include a correction for the stock group that was sampled when estimating annual age composition for the entire drainage. Thus, age counts $x_{ja}$ were modeled as multinomially distributed
  
\begin{equation}
x_{j[a=3:6]}~=~\textrm{Multinomial}\left(q^*_{j[a=3:6]}, \sum_{a=3}^6 x_{ja}\right) (\#eq:xage)
\end{equation}
  
where $j$=1:`r dim(post$data$x.a)[1]`. The location parameters were
    
\begin{equation}
q^*_{ja}~=~\frac{exp\left[\textrm{ln}\left(\frac{N_{y(j)a}}{N_{y(j)(a=3)}}\right)+b_{s(j)a}\right]}{\sum_{a=3}^6 exp\left[\textrm{ln}\left(\frac{N_{y(j)a}}{N_{y(j)(a=3)}}\right)+b_{s(j)a}\right]} (\#eq:qstar)
\end{equation}
    
where $y(j)$ is a function that maps the row index $j$ to the year $y$ in which the data were collected and $s(j)$ is a function that maps the row index $j$ to the stock $s$ from which the data were collected. Equation \@ref(eq:qstar) represents a multinomial logistic regression where the intercept is a function of annual abundance of all four stocks in each age class and the categorical covariates $b_{sa}$ account for age composition differences between the stock groups. The categorical covariates were parameterized with a sum to zero constraint. Because $\sum_s b_{sa}=0$, the quantity
  
\begin{equation}
q_{ya}~=~\frac{N_{ya}}{\sum_{a=3}^6 N_{y}} (\#eq:q)
\end{equation}
  
estimates age composition for the entire Susitna River Chinook salmon run.

## Model Fitting
Bayesian statistical methods employ the language of probability to quantify uncertainty about model parameters. Knowledge existing about the parameters outside the framework of this analysis is reflected in the “prior” probability distribution. The output of the Bayesian analysis is called the “posterior” probability distribution, which is a synthesis of the prior information and the information contained in the data. This methodology allows for inclusion of the effects of measurement error, serially-correlated productivity, and missing data into the analysis and provides a more realistic assessment of uncertainty than is possible with classical statistical methods. By properly specifying process variation, measurement error, and time-dependent linkage in the model, biases in the estimates can be reduced (Su and Peterman 2012). Model fitting involves finding the values of the population parameters of the model that could have plausibly resulted in the observed data. To do so, Markov Chain Monte Carlo (MCMC) methods were employed using the package RJAGS (Plummer 2013) within R (R Core Team 2016). See Fleischman et al. (2013) and Staton et al. (2016) for similar applications of the methods used in this report.
  
### Prior Distributions
Noninformative priors (chosen to have minimal effect on the posterior) were used for most parameters. Initial recruitments $R_{1973}-R_{1978}$ (those lacking linked spawner abundance) were modeled as drawn from a common lognormal distribution with median $\mu_{logR}$ and variance $\sigma^2_{logR}$. Truncated normal priors with mean zero, very large variances, and constrained to be positive were used for $\mu_{log(\alpha)}$, $\beta$, and $\mu_{logR}$. Initial model residuals $\nu_s$ were given a truncated normal prior with mean zero and variance $\sigma^2_{Ws}/(1-\phi^2_s)$ between --3 and +3. Annual harvest rates $\mu_{By},~\mu_{Asy}$ were given $\textrm{beta}(0.5,0.5)$ priors. Diffuse conjugate inverse gamma priors were used for $\sigma^2_{Ws}, \sigma^2_{logR}$. An informative conjugate inverse gamma prior [$\textrm{gamma}(2,1)$] was used for $\sigma^2_\alpha$. Dirichlet dispersion parameters $1/\sqrt{D}$ for age, stock, and harvest compositions have $\textrm{Uniform}(0.07,1)$ priors. $p_{500y3}$ and $p_{500y4}$ have $\textrm{Uniform}(0,1)$ priors. The prior on $B_{AS}$ was also $\textrm{Uniform}(0,1)$, and contained information on the range of $B_{AS}$, although the range was not limiting.
  
### Sampling from the Posterior Distribution
MCMC samples were drawn from the joint posterior probability distribution of all unknowns in the model. The model was initiated with `r post$mcmc.info$n.chains` chains and `r format(post$mcmc.info$n.iter, big.mark = ",", scientific = 100)` samples were generated per chain. The first `r format(post$mcmc.info$n.burnin, big.mark = ",", scientific = 100)` samples from each chain were discarded and the remaining samples were thinned by a factor of `r post$mcmc.info$n.thin`, resulting in `r format(post$mcmc.info$n.samples, big.mark = ",", scientific = 100)` samples that were used to estimate the marginal posterior means, standard deviations, and percentiles. The diagnostic tool ShinySTAN (Stan Development Team 2016) was used to assess mixing and convergence, and no major problems were encountered. Interval estimates were constructed from the percentiles of the posterior distribution.

## Reference Points and Optimal Yield Profiles
Reference points were calculated from S-R parameter estimates for each individual MCMC sample. Sustained yield is the number of fish in the expected recruitment over and above that needed to replace the spawners. Escapement goals in Alaska are developed to maximize sustained yield (MSY) by choosing a range of escapements around $S_{MSY}$, the theoretical number of spawners that will result in the largest difference between recruitment and replacement. Spawning abundance providing MSY $S_{MSY}$, was approximated
  
\begin{equation}
S_{MSYs}~\cong~\frac{\textrm{ln}(\alpha\prime_s)}{\beta}[0.5-0.07\textrm{ln}(\alpha\prime_s)] (\#eq:SMSY)
\end{equation}
  
The quantity
  
\begin{equation}
\textrm{ln}(\alpha\prime_s)~=~\textrm{ln}(\alpha_s)+\frac{\sigma^2_{Ws}}{2(1-\phi_s^2)} (\#eq:alphaprime)
\end{equation}
  
in Equation \@ref(eq:SMSY) adjusts for the difference between the median and the mean of a right-skewed lognormal error distribution with autocorrelation.
  
Sustained yield at a specified level of $S$ was obtained by subtracting spawning escapement from recruitment:
  
\begin{equation}
Y_{Ss}~=~R_s-S_s~=~S_{s}exp(\textrm{ln}(\alpha\prime_s)-\beta_s S_{s})-S_s (\#eq:Ys)
\end{equation}
  
The harvest rate leading to maximum sustained yield, is approximated by (Hilborn 1985):
  
\begin{equation}
U_{MSYs}~\cong~\textrm{ln}(\alpha\prime_s)[0.5-0.07\textrm{ln}(\alpha\prime_s)] (\#eq:UMSY)
\end{equation}
  
Fishery managers may want to evaluate existing and proposed goal ranges with respect to other indicators of fishery performance. In some sport fisheries, run sizes and high catch rates (associated with large recruitment) are important priorities. The escapement leading to maximum sustained recruitment (MSR) is as follows:
  
\begin{equation}
S_{MSRs}~=~\frac{1}{\beta_s} (\#eq:SMSR)
\end{equation}
  
Equilibrium spawning abundance, where recruitment exactly replaces spawners is
  
\begin{equation}
S_{EQs}~=~\frac{\textrm{ln}(\alpha\prime_s)}{\beta_s} (\#eq:SEQ)
\end{equation}
  
The probability that a given spawning escapement $S$ would produce an average yield ($Y_S$) exceeding X% of MSY was obtained by calculating $Y_S$ at incremental values of $S$ for each MCMC sample, then comparing $Y_S$ with X% of the value of MSY for that sample. The proportion of samples in which $Y_S$ exceeds X% of MSY is an estimate of the desired probability, and the plot of this proportion versus $S$ is termed an optimal yield profile (OYP; Fleischman et al. 2013).

The probability that yield would be reduced to less than X% of MSY by supplying too few spawners $S$ was obtained by calculating $Y_S$ at incremental values of $S$ and tallying the number of MCMC samples for which $Y_S$ was less than X% of MSY and $S$ was less than $S_{MSY}$. A plot of the fraction of samples in which this condition occurred versus $S$ is termed an overfishing profile (Bernard and Jones III 2010).

The probability that a given spawning escapement $S$ would produce average recruitment $R$ exceeding X% of MSR was obtained by calculating $R$ from Equation \@ref(eq:ricker) at incremental values of $S$ for each MCMC sample, then comparing $R$ with X% of the value of MSR for that sample. The proportion of samples in which $R$ exceeded X% of MSR is an estimate of the desired probability, and the plot of this proportion versus $S$ is termed an optimal recruitment profile (ORP; Fleischman et al. 2013).

OYPs, Overfishing profiles, and ORPs were used to quantify the yield (or recruitment) performance of prospective escapement goals, taking into consideration the uncertainty about the true abundance, productivity, and capacity of the stock.

## Escapement Goals Standardized to $S_{MSY}$
To compare escapement goals from this study to goals for other Alaska stocks, we divided the lower and upper bounds of `r dim(chinBEGs)[1]` published goals for Alaska Chinook salmon (Munro and Volk 2016) by point estimates of $S_{MSY}$ associated with each goal range, thereby expressing all goal ranges in terms of multiples of $S_{MSY}$. These values were multiplied by estimates of $S_{MSY}$ presented in this report to provide a graphical comparison of the recommended goals with exisitng goals for Alaskan Chinook salmon.

## Escapement Goal Review Process
An interdivisional escapement goal review team was convened to review the available data, discuss analyses and results, and make escapement goal recommendations. The escapement goals recommended in this report are the product of several collaborative meetings of the review team and other ADF&G staff. The final recommendation was reached by consensus.

# Results
## Deshka River Stock Group
```{r echo=FALSE, include=FALSE}
digits <-
  function(p){
    ps <- ifelse(p < 0.01, format(p, TRUE, digits = 2, scientific = TRUE),
                 ifelse(p < 2, format(round(p, 2), TRUE, nsmall = 2),
                        ifelse(p < 100, format(round(p, 1), TRUE, nsmall = 1),
                               format(round(p, 0), TRUE, nsmall = 0, width = 5, scientific = FALSE, big.mark = ","))))
  return(ps)
}

S <- 
  post$summary[grepl("S\\[\\d+,\\d\\]", rownames(post$summary)),] %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column() %>%
  dplyr::rename(q50 = '50%') %>% 
  dplyr::mutate(stock = as.numeric(gsub("S\\[\\d+,(\\d)\\]", "\\1", rowname)),
                year = year_id[as.numeric(gsub("S\\[(\\d+),\\d\\]", "\\1", rowname))],
                cv = sd / mean) %>%
 dplyr::select(rowname, stock, year, q50, cv)
IR <- 
  post$summary[grepl("IR\\[\\d+,\\d\\]", rownames(post$summary)),] %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column() %>%
  dplyr::rename(q50 = '50%') %>%
  dplyr::mutate(stock = as.numeric(gsub("IR\\[\\d+,(\\d)\\]", "\\1", rowname)),
                year = year_id[as.numeric(gsub("IR\\[(\\d+),\\d\\]", "\\1", rowname))],
                cv = sd / mean) %>%
 dplyr::select(rowname, stock, year, q50, cv)
N <- 
  post$summary[grepl("N\\[\\d+,\\d\\]", rownames(post$summary)),] %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column() %>%
  dplyr::rename(q50 = '50%') %>%
  dplyr::mutate(stock = as.numeric(gsub("N\\[\\d+,(\\d)\\]", "\\1", rowname)),
                year = year_id[as.numeric(gsub("N\\[(\\d+),\\d\\]", "\\1", rowname))],
                cv = sd / mean) %>%
 dplyr::select(rowname, stock, year, q50, cv)
R <- 
  post$summary[grepl("R\\[\\d+,\\d\\]", rownames(post$summary)),] %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column() %>%
  dplyr::rename(q50 = '50%') %>%
  dplyr::mutate(stock = as.numeric(gsub("R\\[\\d+,(\\d)\\]", "\\1", rowname)),
                yr = as.numeric(gsub("R\\[(\\d+),\\d\\]", "\\1", rowname)),
                cv = sd / mean) %>%
  dplyr::filter(yr %in% 7:39) %>%
 dplyr::select(rowname, stock, yr, q50, cv)
minrow <- function(dat, n){
  dat %>% 
    dplyr::filter(stock == n) %>% 
    dplyr::slice(which.min(q50)) %>%
    dplyr::mutate(median = digits(q50))}
  
maxrow <- function(dat, n){
  dat %>% 
    dplyr::filter(stock == n) %>% 
    dplyr::slice(which.max(q50)) %>%
    dplyr::mutate(median = digits(q50))}
maxrow(N, 1)

NIR1cv94 <- digits(range(c(IR[IR$year %in% year_id[1:which(year_id == "1994")] & IR$stock == 1, ]$cv, 
                          N[N$year %in% year_id[1:which(year_id == "1994")] & N$stock == 1, ]$cv)))
NIRS1cv17 <- digits(range(c(IR[IR$year %in% year_id[which(year_id == "1995"):length(year_id)] & IR$stock == 1, ]$cv, 
                           N[IR$year %in% year_id[which(year_id == "1995"):length(year_id)] & IR$stock == 1, ]$cv, 
                           S[IR$year %in% year_id[which(year_id == "1995"):length(year_id)] & IR$stock == 1, ]$cv)))
S1cv94 <- digits(range(S[S$year %in% year_id[1:which(year_id == "1994")] & S$stock == 1, ]$cv))
R1cv94 <- digits(range(R[R$yr %in% 7:22 & R$stock == 1, ]$cv))
R1cv17 <- digits(range(R[R$yr %in% 23:39 & R$stock == 1, ]$cv))

t1 <- post$summary[grepl("theta\\[1,1\\]", rownames(post$summary)), ]
CI <- function(df) paste0(digits(df['50%']), "; 95% CI ", digits(df['2.5%']), "--", digits(df['97.5%']))
CIt <- function(df) paste0(digits(df['50%']), " (95% CI ", digits(df['2.5%']), "--", digits(df['97.5%'])) #Note missing closing parens

et1 <- as[[1]]/weir[,1] 
et1_n <- sum(!is.na(et1))
et1_r <-digits(range(et1, na.rm = TRUE))

sa1 <- post$summary[grepl("sigma.air\\[1\\]", rownames(post$summary)), ]

B <- post$summary[grepl("B$", rownames(post$summary)), ]

lna1 <- post$summary[grepl("lnalpha\\[1\\]", rownames(post$summary)), ]

sw1 <- post$summary[grepl("sigma.white\\[1\\]", rownames(post$summary)), ]

phi1 <- post$summary[grepl("phi\\[1\\]", rownames(post$summary)), ]

SMSY1 <- post$summary[grepl("S.msy\\[1\\]", rownames(post$summary)), ]

SMSR1 <- post$summary[grepl("S.max\\[1\\]", rownames(post$summary)), ]

rs <- function(sn){
  rs <- post$summary[grepl(paste0("R\\[\\d+,", sn, "\\]"), rownames(post$summary)), "50%"][7:42]/
    post$summary[grepl(paste0("S\\[\\d+,", sn, "\\]"), rownames(post$summary)), "50%"][1:36]
  list(min = digits(range(rs)[1]),
       max = digits(range(rs)[2]),
       n = sum(rs < 1)
  )
}

prob_e <- get_profileprobs(get_profile(post, "Deshka"), c(13000, 27000))
prob_p <- get_profileprobs(get_profile(post, "Deshka"), c(goals_list[[1]][1], goals_list[[1]][2]))
```
Measures of Chinook salmon abundance for the Deshka River stock group are sparse but display a common trend through time when more than 1 measure is available (Figure 3). Estimated abundance tracks weir counts, which are assumed to be very precise, closely starting in 1995. Prior to 1995, only aerial survey data are available to index abundance. Runs were large prior to 1991, underwent a decline during 1991--1994, rebounded during 1995--2004, declined again starting in 2005 and remained at a lower level during 2008--2017. Escapement estimates ranged between `r minrow(S, 1)$median` in `r minrow(S, 1)$year` and `r maxrow(S, 1)$median` in `r maxrow(S, 1)$year`, and inriver run estimates ranged from `r minrow(IR, 1)$median` in `r minrow(IR, 1)$year` to `r maxrow(IR, 1)$median` in `r maxrow(IR, 1)$year`.
  
Total and inriver run estimates (Appendix C1) are more precise than escapement estimates prior to 1995 because harvest is well estimated compared to the abundance estimates based on single annual aerial surveys. Coefficients of variation for total and inriver run ranged from `r NIR1cv94[1]` to `r NIR1cv94[2]` prior to 1995 whereas coefficients of variation for escapement ranged from `r S1cv94[1]` to `r S1cv94[2]`. After 1995, all estimates have coefficients of variation ranging from `r NIRS1cv17[1]` to `r NIRS1cv17[2]` because weir estimates are very precise. Coefficients of variation for recruitment from complete brood years were highly variable both before (`r R1cv94[1]`--`r R1cv94[2]`) and after (`r R1cv17[1]`--`r R1cv17[2]`) the weir was installed and associated with considerable variation in the S-R relationship ($\sigma_W$ = `r CI(sw1)`; Table 2). 
  
The model-estimated proportion of the escapement observed during single aerial surveys of the Deshka River was `r CIt(t1)`; Table 1). Empirical estimates of observability (survey count/weir count) exist for `r et1_n` years and range from `r et1_r[1]` to `r et1_r[2]`. There was average agreement between Deshka River aerial survey counts (expanded by inverse observability) and other indices of abundance on the Deshka River.  The lognormal standard deviation for the Deshka River aerial survey regression was `r CIt(sa1)`; Table 1), which is similar to the median value for the distribution of $\sigma_{AS}$ (`r CI(B)`).
  
Estimates of population parameters from the state-space model take uncertainty in estimated escapement S and recruitment R (Figure 4 error bars) into account. The individual data pairs are weighted depending upon the certainty with which the individual values of S and R are known. Because escapement and recruitment are poorly known for many brood years, and due to other sources of uncertainty, Ricker S-R relationships that could have plausibly generated the observed data are diverse (Figure 4: light lines), often deviating substantially from the mean Ricker relationship (Figure 4: heavy dashed line).
  
Median productivity (recruits per spawner in the absence of density effects) of the Deshka River Chinook salmon stock group during 1979–2017 was moderate ($\textrm{ln}[\alpha]$ = `r CI(lna1)`) (Table 2). There is a great deal of uncertainty about productivity, as evident in the extent to which the plausible S-R relationships differ with respect to their slope at the origin (Figure 4). Similarly, uncertainty about $\beta$ is reflected in variability in the escapements leading to maximum recruitment $S_{MSR}$, and uncertainty about equilibrium abundance $S_{EQ}$ is reflected by variability in the escapements where the curves intersect the replacement line. Variability in spawning escapements associated with maximum sustained yield $S_{MSY}$ is harder to visualize. Graphically, sustained yield is greatest at the escapement that maximizes the length of a vertical line drawn from the Ricker curve downward to the replacement line. Given the diversity of plausible S-R relationships (Figure 4), it is important to choose an escapement goal that is robust to this uncertainty rather than one tailored solely to the median S-R relationship. To address this uncertainty, we tallied the success or failure of a given number of spawners in achieving biological reference points across plausible S-R relationships in the optimal yield, optimal recruitment, and overfishing profiles (Figure 5). 
  
The model-estimated escapement leading to maximum sustained yield $S_{MSY}$ for the Deshka River Chinook salmon stock group was `r CIt(SMSY1)`; Table 2). The optimal yield profiles in Figure 5 (top panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSY. These probabilities, which are greatest near $S_{MSY}$, can be used to quantify the yield performance of prospective escapement goals (Figure 5 pink-shaded areas), taking into consideration all uncertainty about the true abundance and productivity of the stock. The overfishing profiles (Figure 5 middle panel) show the probability that sustained yield would be reduced to less than 70%, 80%, or 90% of MSY by fishing too hard and supplying too few spawners. For this stock, these probabilities are nearly the exact complements of the probabilities in the left-hand limbs of the optimal yield profiles.
  
Expected sustained yield (number of fish over and above that necessary to replace the number of spawners, averaged over brood years 1979–2015) is also maximized at $S_{MSY}$ (Figure 6). Actual yield in any single year has varied widely (Figure 4), in part because the S-R relationship is noisy and in part because many escapements have been near $S_{eq}$. Median return per spawner has varied between `r rs(1)$min` and `r rs(1)$max` for Deshka River Chinook salmon with `r rs(1)$n` of 36 complete brood years failing to replace themselves.
  
The model-estimated escapement leading to maximum recruitment $S_{MSR}$ was `r CIt(SMSR1)`; Table 2). Analogous to the optimum yield profiles discussed above, optimum recruitment profiles tally the success or failure of a given number of spawners to maximize recruitment across plausible S-R relationships. The optimal recruitment profiles in Figure 5 (bottom panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSR. Optimum recruitment probabilities, which are highest near $S_{MSR}$, reach maximums at larger spawning abundances than optimum yield probabilities and decrease more slowly as spawning abundance increases.
  
## Eastside Susitna Stock Group
```{r echo=FALSE, include=FALSE}
NIR2cv <- digits(range(c(IR[IR$stock == 2, ]$cv, 
                        N[N$stock == 2, ]$cv)))
S2cv <- digits(range(S[S$stock == 2, ]$cv))
R2cv <- digits(range(R[R$stock == 2, ]$cv))

D2 <- post$summary[grepl("Dsum.S2", rownames(post$summary)), ]
B2 <- post$summary[grepl("Bsum.So\\[1", rownames(post$summary)), ]

p2out <-digits(post$summary[grepl("p.S2\\[\\d+,7\\]", rownames(post$summary)), "mean"] * 100)

t2 <- post$summary[grepl("theta\\[2,1\\]", rownames(post$summary)), ]
t3 <- post$summary[grepl("theta\\[3,1\\]", rownames(post$summary)), ]
t4 <- post$summary[grepl("theta\\[4,1\\]", rownames(post$summary)), ]
t5 <- post$summary[grepl("theta\\[5,1\\]", rownames(post$summary)), ]
t6 <- post$summary[grepl("theta\\[6,1\\]", rownames(post$summary)), ]
t7 <- post$summary[grepl("theta\\[7,1\\]", rownames(post$summary)), ]

et2 <- as[[2]][,4]/weir[,2] 
et2_n <- sum(!is.na(et2))
et2_r <- digits(et2[!is.na(et2)])

et3 <- as[[2]][,6]/weir[,3] 
et3_n <- sum(!is.na(et3))
et3_r <- digits(et3[!is.na(et3)])

sa2 <- post$summary[grepl("sigma.air\\[2\\]", rownames(post$summary)), ]
sa3 <- post$summary[grepl("sigma.air\\[3\\]", rownames(post$summary)), ]
sa4 <- post$summary[grepl("sigma.air\\[4\\]", rownames(post$summary)), ]
sa5 <- post$summary[grepl("sigma.air\\[5\\]", rownames(post$summary)), ]
sa6 <- post$summary[grepl("sigma.air\\[6\\]", rownames(post$summary)), ]
sa7 <- post$summary[grepl("sigma.air\\[7\\]", rownames(post$summary)), ]

lna2 <- post$summary[grepl("lnalpha\\[2\\]", rownames(post$summary)), ]

sw2 <- post$summary[grepl("sigma.white\\[2\\]", rownames(post$summary)), ]

phi2 <- post$summary[grepl("phi\\[2\\]", rownames(post$summary)), ]

SMSY2 <- post$summary[grepl("S.msy\\[2\\]", rownames(post$summary)), ]

SMSR2 <- post$summary[grepl("S.max\\[2\\]", rownames(post$summary)), ]

prob_p2 <- get_profileprobs(get_profile(post, "East Susitna"), c(goals_list[[2]][1], goals_list[[2]][2]))
```
Measures of Chinook salmon abundance for the Eastside Susitna stock group display a common trend through time (Figure 7). Runs were small prior to 1983, increased during 1983--1997, underwent a decline during 1998--2012, rebounded slightly after 2012, but were low again in 2017. Escapement estimates ranged between `r minrow(S, 2)$median` in `r minrow(S, 2)$year` and `r maxrow(S, 2)$median` in `r maxrow(S, 2)$year`, and inriver run estimates ranged from `r minrow(IR, 2)$median` in `r minrow(IR, 2)$year` to `r maxrow(IR, 2)$median` in `r maxrow(IR, 2)$year`.
  
Total and inriver run estimates (Appendix C2) have similar precision as escapement estimates. Coefficients of variation for total and inriver run ranged from `r NIR2cv[1]` to `r NIR2cv[2]`, and coefficients of variation for escapement ranged from `r S2cv[1]` to `r S2cv[2]`. Coefficients of variation for recruitment from complete brood years were moderate (`r R2cv[1]`--`r R2cv[2]`) and reflect moderate variation in the S-R relationship ($\sigma_W$ = `r CI(sw2)`).
  
Among the surveyed streams within the Eastside Susitna stock group, stocks in Little Willow and Willow creeks increased in relative abundance between 1979 and 2017 whereas stocks in Goose, Kashwitna, Montana, and Sheep creeks decreased in relative abundance (Figure 8, Appendix D1). Most recently, Willow Creek was the largest component of the Eastside Susitna stock group spawning abundance followed by stocks in Little Willow Creek, Montana Creek, Sheep Creek,  Kashwitna River, and Goose Creek. The inverse dispersion for the Eastside Susitna stock group is large ($D_{comp}$ = `r CI(D2)`; Table 3), indicating trends in the relative magnitude of survey counts and radiotelemetry data are well explained by the multinomial logistic regression model with a calendar-year covariate. There are minor differences between estimated stock composition and empirical stock composition estimates in some years, which represent situations where weighted relative survey counts and telemetry data disagree.
  
Because stocks in unsurveyed streams in the Eastside Susitna stock group lack relative composition information early in the time series, no trend can be estimated. "Other" stocks from unsurveyed streams composed `r min(p2out)`--`r max(p2out)`% (Figure 8, Appendix D1) of the Eastside Susitna stock group. Inverse dispersion is small ($B_{survey}$ = `r CI(B2)`; Table 3) indicating high variability in the proportion of the Eastside Susitna stock group that spawns within the 6 surveyed streams. High variability was documented with telemetry data.
  
The model-estimated proportion of the escapement observed during an aerial survey of Goose Creek was `r CIt(t2)`; Table 1). There was good agreement between the Goose Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Eassidet Susitna stock group.  The lognormal standard deviation for the Goose Creek aerial survey regression was `r CIt(sa2)`), which is smaller than the median value for the distribution of $\sigma_{AS}$ (`r CI(B)`).
  
The model-estimated proportion of the escapement observed during an aerial survey of the Kashwitna River was `r CIt(t3)`; Table 1). There was poor agreement between the Kashwitna River aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Eastside Susitna stock group.  The lognormal standard deviation for the Kashwitna River aerial survey regression was `r CIt(sa3)`), which is larger than the median value for the distribution of $\sigma_{AS}$.
  
The model-estimated proportion of the escapement observed during an aerial survey of Little Willow Creek was `r CIt(t4)`; Table 1). There was good agreement between the Little Willow Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Eastside Susitna stock group.  The lognormal standard deviation for the Little Willow Creek aerial survey regression was `r CIt(sa4)`), which is smaller than the median value for the distribution of $\sigma_{AS}$.
  
The model-estimated proportion of the escapement observed during an aerial survey of Montana Creek was `r CIt(t5)`; Table 1). Empirical estimates of observability (survey count/weir count) exist for `r et2_n` years and were `r et2_r[1]` and `r et2_r[2]`. There was good agreement between the Montana Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Eastside Susitna stock group.  The lognormal standard deviation for the Montana Creek aerial survey regression was `r CIt(sa5)`), which is smaller than the median value for the distribution of $\sigma_{AS}$.
  
The model-estimated proportion of the escapement observed during an aerial survey of Sheep Creek was `r CIt(t6)`; Table 1). There was poor agreement between the Sheep Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Eastside Susitna stock group.  The lognormal standard deviation for the Sheep Creek aerial survey regression was `r CIt(sa6)`), which is larger than the median value for the distribution of $\sigma_{AS}$.
  
The model-estimated proportion of the escapement observed during an aerial surveys of Willow Creek was `r CIt(t7)`; Table 1). Empirical estimates of observability (survey count/weir count) exist for `r et3_n` years and were `r et3_r[1]`, `r et3_r[2]`, and `r et3_r[3]`. There was good agreement between the Willow Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Eastside Susitna stock group.  The lognormal standard deviation for the Willow Creek aerial survey regression was `r CIt(sa7)`), which is smaller than the median value for the distribution of $\sigma_{AS}$.
  
Estimates of population parameters from the state-space model take uncertainty in estimated escapement S and recruitment R (Figure 9 error bars) into account. The individual data pairs are weighted depending upon the certainty with which the individual values of S and R are known. Because escapement and recruitment are poorly known for many brood years, and due to other sources of uncertainty, Ricker S-R relationships that could have plausibly generated the observed data are diverse (Figure 9: light lines), often deviating substantially from the median Ricker relationship (Figure 9: heavy dashed line).
  
Median productivity (recruits per spawner in the absence of density effects) of the Eastside Susitna Chinook salmon stock group during 1979–2017 was moderate ($\textrm{ln}[\alpha]$ = `r CI(lna2)`; Table 3). There is a great deal of uncertainty about productivity, as evident in the extent to which the plausible S-R relationships differ with respect to their slope at the origin (Figure 9). Similarly, uncertainty about $\beta$ is reflected in variability in the escapements leading to maximum recruitment $S_{MSR}$, and uncertainty about equilibrium abundance, $S_{EQ}$, is reflected by variability in the escapements where the curves intersect the replacement line. Variability in spawning escapements associated with maximum sustained yield, $S_{MSY}$, is harder to visualize. Graphically, sustained yield is greatest at the escapement that maximizes the length of a vertical line drawn from the Ricker curve downward to the replacement line. Given the diversity of plausible S-R relationships (Figure 9), it is important to choose an escapement goal that is robust to this uncertainty rather than one tailored solely to the median S-R relationship. To address this uncertainty, we tallied the success or failure of a given number of spawners in achieving biological reference points across plausible S-R relationships in the optimal yield, optimal recruitment, and overfishing profiles (Figure 10).
  
The model-estimated escapement leading to maximum sustained yield $S_{MSY}$ for the Eastside Susitna Chinook salmon stock group was `r CIt(SMSY2)`; Table 3). The optimal yield profiles in Figure 10 (top panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSY. These probabilities, which are highest near $S_{MSY}$, can be used to quantify the yield performance of prospective escapement goals (Figure 10 pink-shaded areas), taking into consideration all uncertainty about the true abundance and productivity of the stock. The overfishing profiles (Figure 10 middle panel) show the probability that sustained yield would be reduced to less than 70%, 80%, or 90% of MSY by fishing too hard and supplying too few spawners. For this stock, these probabilities are nearly the exact complements of the probabilities in the left-hand limbs of the optimal yield profiles.
  
Expected sustained yield (number of fish over and above that necessary to replace the number of spawners, averaged over brood years 1979–2015) is also maximized at $S_{MSY}$ (Figure 11). The Eastside Susitna stock group has produced a yield for most broods (Figure 9), although not for a prolonged period in the early part of this century. Median return per spawner has varied between `r rs(2)$min` and `r rs(2)$max` for the Eastside Susitna Chinook salmon stock group with `r rs(2)$n` of 36 complete brood years failing to replace themselves. 
  
Model-estimated escapement leading to maximum recruitment $S_{MSR}$ was `r CIt(SMSR2)`; Table 3). Analogous to the optimum yield profiles discussed above, optimum recruitment profiles tally the success or failure of a given number of spawners to maximize recruitment across plausible S-R relationships. The optimal recruitment profiles in Figure 10 (bottom panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSR. Optimum recruitment probabilities, which are highest near $S_{MSR}$, reach maximums at larger spawning abundances than optimum yield probabilities and decrease more slowly as spawning abundance increases.
  
## Talkeetna River Stock Group
```{r echo=FALSE, include=FALSE}
NIR3cv <- digits(range(c(IR[IR$stock == 3, ]$cv, 
                        N[N$stock == 3, ]$cv)))
S3cv <- digits(range(S[S$stock == 3, ]$cv))
R3cv <- digits(range(R[R$stock == 3, ]$cv))

D3 <- post$summary[grepl("Dsum.S3", rownames(post$summary)), ]
B3 <- post$summary[grepl("Bsum.So\\[2", rownames(post$summary)), ]

p3out <-digits(post$summary[grepl("p.S3\\[\\d+,3\\]", rownames(post$summary)), "mean"] * 100)

t8 <- post$summary[grepl("theta\\[8,1\\]", rownames(post$summary)), ]
t9 <- post$summary[grepl("theta\\[9,1\\]", rownames(post$summary)), ]

sa8 <- post$summary[grepl("sigma.air\\[8\\]", rownames(post$summary)), ]
sa9 <- post$summary[grepl("sigma.air\\[9\\]", rownames(post$summary)), ]

lna3 <- post$summary[grepl("lnalpha\\[3\\]", rownames(post$summary)), ]

sw3 <- post$summary[grepl("sigma.white\\[3\\]", rownames(post$summary)), ]

phi3 <- post$summary[grepl("phi\\[3\\]", rownames(post$summary)), ]

SMSY3 <- post$summary[grepl("S.msy\\[3\\]", rownames(post$summary)), ]

SMSR3 <- post$summary[grepl("S.max\\[3\\]", rownames(post$summary)), ]

prob_p3 <- get_profileprobs(get_profile(post, "Talkeetna"), c(goals_list[[3]][1], goals_list[[3]][2]))
```
Measures of Chinook salmon abundance for the Talkeetna River stock group are few but display a common trend through time (Figure 12). Runs increased through 1998, underwent a decline during 1999--1994, rebounded until 1997 and gradually declined thereafter. Escapement estimates ranged between `r minrow(S, 3)$median` in `r minrow(S, 3)$year` and `r maxrow(S, 3)$median` in `r maxrow(S, 3)$year`, and inriver run estimates ranged from `r minrow(IR, 3)$median` in `r minrow(IR, 3)$year` and `r maxrow(IR, 3)$median` in `r maxrow(IR, 3)$year`.
  
Total and inriver run estimates (Appendix C3) have similar precision as escapement estimates. Coefficients of variation for total and inriver run ranged from `r NIR3cv[1]` to `r NIR3cv[2]`, and coefficients of variation for escapement ranged from `r S3cv[1]` to `r S3cv[2]`. Coefficients of variation for recruitment from complete brood years were highly variable (`r R3cv[1]`--`r R3cv[2]`) and associated with considerable variation in the S-R relationship ($\sigma_W$ = `r CI(sw3)`).
  
Among the surveyed streams within the Talkeetna River stock group, the Clear Creek stock increased in relative abundance between 1979 and 2017 whereas the Prairie Creek stock decreased in relative abundance (Figure 8, Appendix D2). Clear and Prairie Creeks are similar-sized components of the spawning abundance for the Talkeetna River stock group in recent years. The inverse dispersion for the Talkeetna River stock group is small ($D_{comp}$ = `r CI(D3)`; Table 4) indicating trends in the relative magnitude of survey counts and radiotelemetry data vary significantly from the multinomial logistic regression model with a calendar-year covariate. There is considerable divergence between estimated stock composition and empirical stock composition estimates in some years, which represent situations where weighted relative survey counts and telemetry data disagree.
  
Because stocks in unsurveyed streams in the Talkeetna River stock group lack relative composition data early in the time series, no trend can be estimated. "Other" stocks from unsurveyed streams composed `r min(p3out)`--`r max(p3out)`% (Figure 8, Appendix D2) of the Talkeetna River stock group. Inverse dispersion is small ($B_{survey}$ = `r CI(B3)`; Table 4) indicating high variability in the proportion of the Talkeetna River stock group spawning within the 2 surveyed streams. High variability was also documented with telemetry data.
  
The model-estimated proportion of the escapement observed during aerial surveys of Clear Creek was `r CIt(t8)`; Table 1). There was very good agreement between the Clear Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Talkeetna River stock group.  The lognormal standard deviation for the Clear Creek aerial survey regression was `r CIt(sa8)`), which is smaller than the median value for the distribution of $\sigma_{AS}$ (`r CI(B)`).
  
The model-estimated proportion of the escapement observed during aerial surveys of Prairie Creek was `r CIt(t9)`; Table 1). There was very good agreement between the Prairie Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Talkeetna River stock group.  The lognormal standard deviation for the Prairie Creek aerial survey regression was `r CIt(sa9)`), which is smaller than the median value for the distribution of $\sigma_{AS}$.
  
Estimates of population parameters from the state-space model take uncertainty in estimated escapement S and recruitment R (Figure 13 error bars) into account. The individual data pairs are weighted depending upon the certainty with which the individual values of S and R are known. Because escapement and recruitment are poorly known for many brood years, and due to other sources of uncertainty, Ricker S-R relationships that could have plausibly generated the observed data are diverse (Figure 13: light lines), often deviating substantially from the median Ricker relationship (Figure 13: heavy dashed line).
  
Median productivity (recruits per spawner in the absence of density effects) of the Talkeetna River Chinook salmon stock group during 1979–2017 was low ($\textrm{ln}[\alpha]$ = `r CI(lna3)`; Table 4). There is a great deal of uncertainty about productivity, as evident in the extent to which the plausible S-R relationships differ with respect to their slope at the origin (Figure 13). Similarly, uncertainty about $\beta$ is reflected in variability in the escapements leading to maximum recruitment $S_{MSR}$, and uncertainty about equilibrium abundance $S_{EQ}$ is reflected by variability in the escapements where the curves intersect the replacement line. Variability in spawning escapements associated with maximum sustained yield $S_{MSY}$ is harder to visualize. Graphically, sustained yield is greatest at the escapement that maximizes the length of a vertical line drawn from the Ricker curve downward to the replacement line. Given the diversity of plausible S-R relationships (Figure 13), it is important to choose an escapement goal that is robust to this uncertainty rather than one tailored solely to the median S-R relationship. To address this uncertainty, we tallied the success or failure of a given number of spawners in achieving biological reference points across plausible S-R relationships in the optimal yield, optimal recruitment, and overfishing profiles (Figure 14).
  
Model-estimated escapement leading to maximum sustained yield $S_{MSY}$ for the Talkeetna River Chinook salmon stock group was `r CIt(SMSY3)`; Table 4). The optimal yield profiles in Figure 14 (top panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSY. These probabilities, which are highest near $S_{MSY}$, can be used to quantify the yield performance of prospective escapement goals (Figure 14 pink-shaded areas), taking into consideration the uncertainty about the true abundance and productivity of the stock. The overfishing profiles (Figure 14 middle panel) show the probability that sustained yield would be reduced to less than 70%, 80%, or 90% of MSY by fishing too hard and supplying too few spawners. For this stock, these probabilities are nearly the exact complements of the probabilities in the left-hand limbs of the optimal yield profiles.
  
Expected sustained yield (number of fish over and above that necessary to replace the number of spawners, averaged over brood years 1979–2015) is also maximized at $S_{MSY}$ (Figure 15). The Talkeetna River stock group has frequently failed to produce a yield (Figure 13); this may be partially due to the escapements near $S_{eq}$ and partially due to the low productivity of the stock. Median return per spawner has varied between `r rs(3)$min` and `r rs(3)$max` for Talkeetna River Chinook salmon, with `r rs(3)$n` of 36 complete brood years failing to replace themselves.

Model-estimated escapement leading to maximum recruitment $S_{MSR}$ was `r CIt(SMSR3)`; Table 4). Analogous to the optimum yield profiles discussed above, optimum recruitment profiles tally the success or failure of a given number of spawners to maximize recruitment across plausible S-R relationships. The optimal recruitment profiles in Figure 14 (bottom panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSR. Optimum recruitment probabilities, which are highest near $S_{MSR}$, reach maximums at larger spawning abundances than optimum yield probabilities and decrease more slowly as spawning abundance increases.

## Yentna River Stock Group
```{r echo=FALSE, include=FALSE}
NIR4cv <- digits(range(c(IR[IR$stock == 4, ]$cv, 
                        N[N$stock == 4, ]$cv)))
S4cv <- digits(range(S[S$stock == 4, ]$cv))
R4cv <- digits(range(R[R$stock == 4, ]$cv))

D4 <- post$summary[grepl("Dsum.S4", rownames(post$summary)), ]
B4 <- post$summary[grepl("Bsum.So\\[3", rownames(post$summary)), ]

p4out <-digits(post$summary[grepl("p.S4\\[\\d+,5\\]", rownames(post$summary)), "mean"] * 100)

t10 <- post$summary[grepl("theta\\[10,1\\]", rownames(post$summary)), ]
t11 <- post$summary[grepl("theta\\[11,1\\]", rownames(post$summary)), ]
t12 <- post$summary[grepl("theta\\[12,1\\]", rownames(post$summary)), ]
t13 <- post$summary[grepl("theta\\[13,1\\]", rownames(post$summary)), ]

sa10 <- post$summary[grepl("sigma.air\\[10\\]", rownames(post$summary)), ]
sa11 <- post$summary[grepl("sigma.air\\[11\\]", rownames(post$summary)), ]
sa12 <- post$summary[grepl("sigma.air\\[12\\]", rownames(post$summary)), ]
sa13 <- post$summary[grepl("sigma.air\\[13\\]", rownames(post$summary)), ]

lna4 <- post$summary[grepl("lnalpha\\[4\\]", rownames(post$summary)), ]

sw4 <- post$summary[grepl("sigma.white\\[4\\]", rownames(post$summary)), ]

phi4 <- post$summary[grepl("phi\\[4\\]", rownames(post$summary)), ]

SMSY4 <- post$summary[grepl("S.msy\\[4\\]", rownames(post$summary)), ]

SMSR4 <- post$summary[grepl("S.max\\[4\\]", rownames(post$summary)), ]

prob_p4 <- get_profileprobs(get_profile(post, "Yentna"), c(goals_list[[4]][1], goals_list[[4]][2]))
```
Some of the measures of abundance for the Yentna River Chinook salmon stock group display a common trend through time (Figure 16). Runs increased through 1984, underwent a decline during 1985--1994, and rebounded until 2004, declined through 2009, increased through 2015, and declined to historically low levels in 2017. Escapement estimates ranged between `r minrow(S, 4)$median` in `r minrow(S, 4)$year` and `r maxrow(S, 4)$median` in `r maxrow(S, 4)$year`, and inriver run estimates ranged from `r minrow(IR, 4)$median` in `r minrow(IR, 4)$year` to `r maxrow(IR, 4)$median` in `r maxrow(IR, 4)$year`.
  
Total and inriver run estimates (Appendix C4) have similar precision as escapement estimates. Coefficients of variation for total and inriver run ranged from `r NIR4cv[1]` to `r NIR4cv[2]`, and coefficients of variation for escapement ranged from `r S4cv[1]` to `r S4cv[2]`. Coefficients of variation for recruitment from complete brood years were moderate (`r R4cv[1]`--`r R4cv[2]`), reflective of moderate variation in the S-R relationship ($\sigma_W$ = `r CI(sw4)`).
  
Among the surveyed streams within the Yentna River stock group, the Peters Creek stock increased in relative abundance between 1979 and 2017 whereas the Cache Creek stock decreased in relative abundance, and the reletive abundances of the Lake Creek and Talachulitna River stocks have remained similar across years (Figure 8, Appendix D3). The Lake Creek stock is the largest component of the Yentna stock group spawning abundance in recent years followed by stocks in Talachulitna River, Peters Creek, and Cache Creek. The inverse dispersion for the Yentna River stock group is moderate ($D_{comp}$ = `r CI(D4)`; Table 5), indicating trends in the relative magnitude of survey counts and radio-telemetry data are fairly well explained by the multinomial logistic regression model with a calendar year covariate. Estimated stock composition and empirical stock composition estimates are similar.
  
Because stocks in unsurveyed streams in the Yentna River stock group lack relative composition data early in the time series, no trend can be estimated. "Other" stocks in unsurveyed streams compose `r min(p4out)`--`r max(p4out)`% (Figure 8, Appendix D3) of the Yentna River stock group. Inverse dispersion is moderate ($B_{survey}$ = `r CI(B4)`; Table 5), indicating moderate variability in the proportion of the Yentna River stock group spawning within the 4 surveyed streams. Moderate variability was documented with telemetry data.
  
The model-estimated proportion of the escapement observed during aerial surveys of Cache Creek was `r CIt(t10)`; Table 1). There was very poor agreement between the Cache Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Yentna River stock group.  The lognormal standard deviation for the Cache Creek aerial survey regression was `r CIt(sa10)`), which is larger than the median value for the distribution of $\sigma_{AS}$ (`r CI(B)`).
  
The model-estimated proportion of the escapement observed during aerial surveys of Lake Creek was `r CIt(t11)`; Table 1). There was very good agreement between the Lake Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Yentna River stock group.  The lognormal standard deviation for the Lake Creek aerial survey regression was `r CIt(sa11)`), which is smaller than the median value for the distribution of $\sigma_{AS}$.
  
The model-estimated proportion of the escapement observed during aerial surveys of Peters Creek was `r CIt(t12)`; Table 1). There was very poor agreement between the Peters Creek single aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Yentna River stock group.  The lognormal standard deviation for the Peters Creek aerial survey regression was `r CIt(sa12)`), which is larger than the median value for the distribution of $\sigma_{AS}$.
  
The model-estimated proportion of the escapement observed during an aerial survey of the Talachulitna River was `r CIt(t13)`; Table 1). There was average agreement between Talachulitna River aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Yentna River stock group.  The lognormal standard deviation for the Talachulitna River aerial survey regression was `r CIt(sa13)`), which is similar to the median value for the distribution of $\sigma_{AS}$.
  
Estimates of population parameters from the state-space model take uncertainty in estimated escapement S and recruitment R (Figure 17 error bars) into account. The individual data pairs are weighted depending upon the certainty with which the individual values of S and R are known. Because escapement and recruitment are poorly known for many brood years, and due to other sources of uncertainty, Ricker S-R relationships that could have plausibly generated the observed data are diverse (Figure 17: light lines), often deviating substantially from the median Ricker relationship (Figure 17: heavy dashed line).
  
Median productivity (recruits per spawner in the absence of density effects) of the Yentna River Chinook salmon stock group during 1979–2017 was moderate  ($\textrm{ln}[\alpha]$ = `r CI(lna4)`; Table 5). There is a great deal of uncertainty about productivity, as evident in the extent to which the plausible S-R relationships differ with respect to their slope at the origin (Figure 17). Similarly, uncertainty about $\beta$ is reflected in variability in the escapements leading to maximum recruitment $S_{MSR}$, and uncertainty about equilibrium abundance $S_{EQ}$ is reflected by variability in the escapements where the curves intersect the replacement line. Variability in spawning escapements associated with maximum sustained yield $S_{MSY}$ is harder to visualize. Graphically, sustained yield is greatest at the escapement that maximizes the length of a vertical line drawn from the Ricker curve downward to the replacement line. Given the diversity of plausible S-R relationships (Figure 17), it is important to choose an escapement goal that is robust to this uncertainty rather than one tailored solely to the median S-R relationship. To address this uncertainty, we tallied the success or failure of a given number of spawners in achieving biological reference points across plausible S-R relationships in the optimal yield, optimal recruitment, and overfishing profiles (Figure 18).
  
Model-estimated escapement leading to maximum sustained yield $S_{MSY}$ for the Yentna RIver Chinook salmon stock group was estimated to be `r CIt(SMSY4)`; Table 5). The optimal yield profiles in Figure 18 (top panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSY. These probabilities, which are highest near $S_{MSY}$, can be used to quantify the yield performance of prospective escapement goals (Figure 18 pink-shaded areas), taking into consideration all uncertainty about the true abundance and productivity of the stock. The overfishing profiles (Figure 18 middle panel) show the probability that sustained yield would be reduced to less than 70%, 80%, or 90% of MSY by fishing too hard and supplying too few spawners. For this stock, these probabilities are nearly the exact complements of the probabilities in the left-hand limbs of the optimal yield profiles.
  
Expected sustained yield (number of fish over and above that necessary to replace the number of spawners, averaged over brood years 1979–2015) is also maximized at $S_{MSY}$ (Figure 19). Many brood years from the Yentna River stock group have produced a yield (Figure 17), with most exceptions coming from escapement at or above $s_{EQ}$. Median return per spawner varied between `r rs(4)$min` and `r rs(4)$max` for the Yentna River Chinook salmon stock group with `r rs(4)$n` of 36 complete brood years failing to replace themselves.
  
Model-estimated escapement leading to maximum recruitment $S_{MSR}$ was `r CIt(SMSR4)`; Table 5). Analogous to the optimum yield profiles discussed above, optimum recruitment profiles tally the success or failure of a given number of spawners to maximize recruitment across plausible S-R relationships. The optimal recruitment profiles in Figure 18 (bottom panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSR. Optimum recruitment probabilities, which are highest near $S_{MSR}$, reach maximums at larger spawning abundances than optimum yield probabilities and decrease more slowly as spawning abundance increases.
  
## Age Composition
```{r echo=FALSE, include=FALSE}
ageD <- age[grepl("Deshka", age$stock), ]
ageES <- age[grepl("East Susitna", age$stock), ]
ageT <- age[grepl("Talkeetna", age$stock), ]
ageY <- age[grepl("Yentna", age$stock), ]

p1 <- digits(range(post$summary[grepl("p\\[\\d+,1\\]", rownames(post$summary)), "mean"])*100)
p2 <- digits(range(post$summary[grepl("p\\[\\d+,2\\]", rownames(post$summary)), "mean"])*100)
p3 <- digits(range(post$summary[grepl("p\\[\\d+,3\\]", rownames(post$summary)), "mean"])*100)
p4 <- digits(range(post$summary[grepl("p\\[\\d+,4\\]", rownames(post$summary)), "mean"])*100)
```
Between `r min(intersect(ageD$year, intersect(ageES$year, ageY$year)))` and `r max(intersect(ageD$year, intersect(ageES$year, ageY$year)))`, annual age composition datasets exist from sport harvested Chinook salmon in the Deshka, Eastside Susitna and Yentna stock groups. In general, the Eastside Susitna Chinook salmon stock group contained larger proportions of older fish (Figure 20, middle panel). Between `r min(intersect(ageD$year, intersect(ageES$year, ageT$year)))` and `r max(intersect(ageD$year, intersect(ageES$year, ageT$year)))`, annual age composition datasets exist for the sport harvest of Chinook salmon in the Eastside Susitna, Deshka and Talkeetna stock groups. The Deshka River Chinook salmon stock group contained smaller proportions of older fish in paired annual samples. 
  
Chinook salmon in the Susitna River drainage are composed of age-3(1.1), age-4(1.2), age-5(1.3), and age-6 (1.4) fish (Figure 20 middle panel, Table 6). Throughout the time series age-5 fish have been the dominante age class whereas the relative abundance of age-6 fish has steadily decreased and the relative abundance of age-3 fish has increased (dramatically in recent years).
  
Susitna River drainage Chinook salmon matured (Figure 20 top panel, Table 7) at age-3 (`r p1[1]`--`r p1[2]`%), age-4 (`r p2[1]`--`r p2[2]`%), age-5 (`r p3[1]`--`r p3[2]`%), and age-6 (`r p4[1]`--`r p4[2]`%). Age-at-maturity has trended strongly toward increasing contributions of age-3, age-4 and age-5 fish and decreasing contributions of age-6 fish.
  
# Discussion
The only discussion presented in this document pertains to performance at the current and recommended goal ranges.
  
### Deshka River
Deshka River Chinook salmon have an existing goal range of 13,000--27,000 Chinook salmon. Escapements at the low end of the existing range have `r prob_e[[1, "OYP80"]]`% probability of producing a yield greater than 80% of MSY whereas escapements at the upper end of the existing range have `r prob_e[[2, "OYP80"]]`% probability of producing yields greater than 80% of MSY. With respect to recruitment, escapements at the low end of the existing range have `r prob_e[[1, "ORP80"]]`% probability of producing a recruitment greater than 80% of MSR whereas escapements at the upper end of the existing range have `r prob_e[[2, "ORP80"]]`% probability of producing a recruitment greater than 80% or MSR. 
  
The proposed escapement goal of 9,000--18,000 fish has `r prob_p[[1, "OYP80"]]`% probability of achieving 80+% of MSY at the lower bound and `r prob_p[[2, "OYP80"]]`% probability of achieving 80+% MSY at the upper bound. With respect to recruitment, the proposed escapement goal shown has `r prob_p[[1, "ORP80"]]`% probability of achieving 80+% of MSR at the lower bound and `r prob_p[[2, "ORP80"]]`% probability of achieving 80+% of MSR at the upper bound.

### East Susitna
The proposed escapement goal of 13,000–25,000 fish has `r prob_p2[[1, "OYP80"]]`% probability of achieving 80+% of MSY at the lower bound and `r prob_p2[[2, "OYP80"]]`% probability of achieving 80+% of MSY at the upper bound. With respect to recruitment, the proposed escapement goal has `r prob_p2[[1, "ORP80"]]`% probability of achieving 80+% of MSR at the lower bound and `r prob_p2[[2, "ORP80"]]`% probability of achieving 80+% of MSR at the upper bound.
  
### Talkeetna River
The proposed escapement goal 9,000–17,500 fish has `r prob_p3[[1, "OYP80"]]`% probability of achieving 80+% of MSY at the lower bound and `r prob_p3[[2, "OYP80"]]`% probability of achieving 80+% of MSY at the upper bound. With respect to recruitment, the proposed escapement goal has `r prob_p3[[1, "ORP80"]]`% probability of achieving 80+% of MSR at the lower bound and `r prob_p3[[2, "ORP80"]]`% probability of achieving 80+% of MSR at the upper bound.
  
### Yentna River
The proposed escapement goal of 13,000–22,000 fish has `r prob_p4[[1, "OYP80"]]`% probability of achieving 80+% of MSY at the lower bound and `r prob_p4[[2, "OYP80"]]`% probability of achieving 80+% of MSY at the upper bound. With respect to recruitment, the proposed escapement goal has `r prob_p4[[1, "ORP80"]]`% probability of achieving 80+% of MSR at the lower bound and `r prob_p4[[2, "ORP80"]]`% probability of achieving 80+% of MSR at the upper bound.