---
output: 
  word_document:
    reference_docx: ".\\doc_styles\\word_styles_FDS.docx"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.cap = TRUE, fig.align = 'center')
library(SusitnaEG)
get_ids()
#post <- readRDS("..\\..\\posts\\SuChinook_8e162f9.rds")
post <- readRDS("C:\\postsC\\SuChinook_8e162f9.rds")
```


Table: Table 1.- Aerial survey observability and lognormal standard deviation with 95% confidence interval for each surveyed spawning area tributary in the Susitna River drainage.
```{r}
table_airerror(post)
``` 

Table: Table 2.- State-space model parameter estimates for Deshka River Chinook salmon stock group, calendar years 1979--2017. Posterior medians are point estimates and 95% credibility intervals are shown in parentheses. Parameter definitions are in the Methods section. 
```{r}
table_params(post, 1)
```

Table: Table 3.- State-space model parameter estimates for Eastside Susitna Chinook salmon stock group, calendar years 1979--2017. Posterior medians are point estimates and 95% credibility intervals are shown in parentheses. Parameter definitions are in the Methods section. 
```{r}
table_params(post, 2)
```

Table: Table 4.- State-space model parameter estimates for Talkeetna River Chinook salmon stock group, calendar years 1979--2017. Posterior medians are point estimates and 95% credibility intervals are shown in parentheses. Parameter definitions are in the Methods section. 
```{r}
table_params(post, 3)
```

Table: Table 5.- State-space model parameter estimates for Yentna River Chinook salmon stock group, calendar years 1979--2017. Posterior medians are point estimates and 95% credibility intervals are shown in parentheses. Parameter definitions are in the Methods section. 
```{r}
table_params(post, 4)
```

Table: Table 6.- Age composition estimates obtained by fitting a state-space model to data from Susitna River drainage Chinook salmon, calendar years 1979--2017.
```{r}
table_age(post, "q")
```

Table: Table 7.- Age-at-maturity estimates obtained by fitting a state-space model to data from Susitna River drainage Chinook salmon, brood years 1973--2014.
```{r}
table_age(post, "p")
```
