---
title: "Model Description"
author: "Adam Reimer"
date: "September 4, 2018"
output: 
  bookdown::word_document2
---

```{r setup, echo=FALSE, include=FALSE}
library(bookdown)
knitr::opts_chunk$set(echo = TRUE)
library(SusitnaEG)
post <- readRDS("..\\..\\posts\\SuChinook_DsumS_ababd3a.rds")
get_ids()
```

##State-Space Model
The state-space model (Appendix A1) specifies how population parameters lead to the data that are observed. The process model component describes how natural population processes generate true annual abundance by age, and the observation model component describes how the observed data are generated.
  
###Notation conventions
Many parameters are estimated in this model. Parameters with similar function or interpretation often use the same symbol, distinguished by a subscript capital letter. Subscript lower case letters denote parameter indices. For example, all harvest rates use the symbol $\mu$ where $\mu_{By}$ is the harvest rate below (downstream of) Susitna RM 34 and Yentna RM 6 in year $y$, $\mu_{Ays}$ is the harvest rate of stock $s$ above Susitna RM 34 and Yentna RM 6 in year $y$, and $\mu_{Dy}$ is the harvest rate upstream of the Deshka River weir in year $y$. Year indices run from 1 to 39 representing 1979 to 2017 respectively. Stock indices run from 1 to 5 representing Deshka River, East Susitna Drainage, Talkeetna River, Yentna River, and all Other areas respectively.
  
###Process Component
Abundance of Susitna River Chinook salmon in each stock group is generated by a spawner-recruit (SR) relationship, which describes the number of fish expected to return (the “recruitment”) from a given “escapement” (number of spawning fish). The total recruitment $R_{ys}$ produced from fish spawning in year $y$ by stock $s$ follows the Ricker (1975) formulation:
\begin{equation}
R_{ys}~=~S_{ys}\alpha_s exp(\beta_s S_{ys})
  (\#eq:ricker)
\end{equation}
where $S_{ys}$ is the number of spawners, $\alpha_s$ (number of recruits per spawner in the absence of density dependence) is a measure of productivity for each stock group, and $\beta_s$ is a measure of density dependence for each stock group.

Productivity varies among brood years, fluctuating around a central tendency. Time-varying productivity often manifests as serially correlated model residuals, so a log-normal error term with a lag of one year (MA1) was included in the linearized form of the spawner-recruit relationship (Noakes et al. 1987)
\begin{equation}
ln(R_{ys})~=~ln(S_{ys})+ln(\alpha_s)-\beta_s S_{ys} +\phi_s \nu_{(y-1)s}+\epsilon_{Ws}
  (\#eq:rickerar)
\end{equation}
where $\phi_s$ is the lag-1 moving average coefficient, $\nu_{ys}$ are model residuals
\begin{equation}
\nu_{ys}~=~ln(R_{ys})-ln(S_{ys})-ln(\alpha_s)+\beta_s S_{ys} 
  (\#eq:residuals)
\end{equation}
and the $\epsilon_{Ws}$ are independently and normally distributed process errors with “white noise” variance $\sigma^2_{Ws}$. The productivity parameters for each stock $\alpha_s$ are drawn from a common distribution, $\textrm{ln}(\alpha_s)~\sim~\textrm{Normal}(\mu_\alpha, \sigma^2_\alpha)$.  
  
Expected age at maturity is allowed to trend through time and fluctuate annually. Age-at-maturity vectors $\mathbf{p_y} = (\begin{array}{am} p_{y3} & p_{y4} & p_{y5} & p_{y6} \end{array})$ from year $y$ returning at ages 3-6 were drawn from a $Dirichlet(\gamma_{y3}, \gamma_{y4},  \gamma_{y5}, \gamma_{y6})$ distribution. The Dirichlet parameters are expressed in an alternate form where 
\begin{equation}
D~=~\sum_{a=3}^6 \gamma_{ya}
   (\#eq:Dage)
\end{equation}
is the (inverse) dispersion of the annual age-at-maturity vectors, reflecting consistency of age at maturity among brood years.
The location parameters
\begin{equation}
\pi_{ya}~=~\frac{\gamma_{ya}}{D}~=~\frac{exp(ML1_a+ML2_ay)}{\sum_a exp(ML1_a+ML2_ay)}
   (\#eq:pi)
\end{equation}
are proportions that sum to one and reflect age-at-maturity central tendency in each year where $ML1_a$ and $ML2_a$ are multinomial logistic regression coefficients describing trending age at maturity.
  
The abundance $N_{yas}$ in stock group $s$ of age $a$ Chinook salmon in calendar year $y$ is the product of the age at maturity scalar $p_{ya}$ and the total return (recruitment) $R_{ys}$ in stock group $s$ from year $y−a$:
\begin{equation}
N_{yas}~=~p_{(y-a)a}R_{(y-a)s}
   (\#eq:Ntas)
\end{equation}
Total run $N_{ys}$ for stock group $s$ during calendar year $y$ is the sum of abundance at age across ages:
\begin{equation}
N_{ys}~=~\sum_{a=3}^6 N_{yas}
   (\#eq:Nts)
\end{equation}
Annual harvest of Susitna-origin Chinook salmon below (downstream of) Susitna RM 34 and Yentna RM 6, $H_{By}$, was modeled as the product of the annual harvest rate below in the area $\mu_{By}$ and total run $N_y$:
\begin{equation}
H_{By}~=~\mu_{By}\sum_{s=1}^5 N_{ys}
   (\#eq:Hbelow)
\end{equation}
Inriver run $IR_{ys}$ of stock group $s$ during calendar year $y$ at Susitna RM 34 and Yentna RM 6 was modeled as the product of stock specific total run $N_{ys}$ and the annual survival rate in the area downstream: 
\begin{equation}
IR_{ys}~=~N_{ys}(1-\mu_{By})
   (\#eq:IR)
\end{equation}
Annual harvest of stock group $s$ above Susitna RM 34 and Yentna RM 6 $H_{Ays}$ was the product of the annual harvest rate for each stock in the area $\mu_{Ays}$ and inriver run:
\begin{equation}
H_{Ays}~=~\mu_{Ays}IR_{ys}
   (\#eq:Habove)
\end{equation}
Annual harvest of Deshka River Chinook salmon (stock = 1) upstream of the Deshka River weir $H_{Dy}$ was the product of the annual harvest rate the above the weir $\mu_{Dy}$ and abundance of Chinook salmon at the weir $IR_{Dy}$:
\begin{equation}
H_{Dy}~=~\mu_{Dy}IR_{Dy}~=~\mu_{Dy}(IR_{y1} - H_{Ay1})
   (\#eq:Hdeshka)
\end{equation}
Finally, spawning escapement $S_{ys}$ was inriver run abundance minus harvest above Susitna RM 34 and Yentna RM 6:
\begin{equation}
S_{y1}~=~IR_{Dy}-H_{Dy}~=~IR_{y1} - H_{Ay1} - H_{Dy}
   (\#eq:S1)
\end{equation}
for the Deshka River stock group and
\begin{equation}
S_{y(2:5)}~=~IR_{y(2:5)}-H_{Ay(2:5)}
   (\#eq:S2)
\end{equation}
for the other stock groups.
  
Multiple tributaries ($t=1,2,\dots,T$) contribute to the spawning escapement in the East Susitna, Talkeetna, Yentna and Other stock groups. Expected stock composition of the $T-1$ tributaries which are monitored by aerial survey is allowed to trend through time and fluctuate annually. Four sets of equations analogous to eq. $\@ref(eq:Dage)$ and eq. $\@ref(eq:pi)$ were used to define stock composition vectors $\mathbf{\rho^*}_{sy} = (\begin{array} \rho^*_{sy1} & \rho^*_{sy2 }& \dots & \rho^*_{sy(T-1)}\end{array})$ for the surveyed tributaries in each stock group.
  
###Observation Component
Observed data (Appendices A1-A#) include estimates of annual harvest below and above Susitna RM 34 and Yentna RM 6, age composition data from carcass surveys, creel surveys, fishwheel catches and weir projects throughout the Susitna drainage, weir counts for 3 tributaries, single aerial survey data for 16 tributaries, mark-recapture estimates of inriver run, radio telemetry data, and length composition data. Sampling distributions for the data follow.
  
Estimated annual inriver runs of Chinook salmon from mark-recapture $\widehat{IR}_{ys}$ for stock $s$ were
\begin{equation}
\widehat{IR}_{ys}~=~IR_{500ys}exp(\epsilon_{IRys})
   (\#eq:IRhat)
\end{equation}
where $IR_{500ys}$ is the inriver run of fish 500mm MEFT or larger and $\epsilon_{IRys}~\sim~\textrm{Normal}(0, \sigma^2_{IRys})$ with
\begin{equation}
\sigma^2_{IR_{ys}}~=~\textrm{ln}(\textrm{CV}(\widehat{IR}_{ys})^2+1)
   (\#eq:cvIR)
\end{equation}

The number of age-3 and age-4 fish that were less than 500mm MEFT $x_{500ya}$ in year $y$ were
\begin{equation}
x_{500ya}~\sim~\textrm{Binomial}(p_{500ya}, n_{500ya})
   (\#eq:xsmall)
\end{equation}
where $n_{500ya}$ is the  total number of fish sampled for age and length in age class $a$ during year $y$ and $p_{500ya}$ is the proportion of fish less than 500mm MEFT in age class $a$ during year $y$. Inriver runs of fish 500mm MEFT or greater $IR_{500ys}$ were
\begin{equation}
IR_{500ys}~=~IR_{ys}[1-(q_{y3}p_{500y3}+q_{y4}p_{500y4})]
   (\#eq:IRlarge)
\end{equation}
where $q_{ya}$ is the proportion of the run that is age $a$ in calendar year $y$.
  
Estimated annual harvest of Susitna River Chinook salmon below Susitna RM 34 and Yentna RM 6 $\widehat{H}_{By}$ was
\begin{equation}
\widehat{H}_{By}~=~H_{By}exp(\epsilon_{HBy})
   (\#eq:HBhat)
\end{equation}
where the $\epsilon_{HBy}~\sim~\textrm{Normal}(0, \sigma^2_{HBy})$ and the variances followed eq. $\@ref(eq:cvIR)$ with an assumed CV of 0.05 reflecting good precision associated with reported commercial and subsistence harvest.
  
Estimated annual harvest of Susitna River Chinook salmon above Susitna RM 34 and Yentna RM 6 $\widehat{H}_{Ays}$ for stock $s$ was
\begin{equation}
\widehat{H}_{Ays}~=~H_{Ays}exp(\epsilon_{HAy})
   (\#eq:HAhat)
\end{equation}
where the $\epsilon_{HAy}~\sim~\textrm{Normal}(0, \sigma^2_{HAy})$ and the variances followed eq. $\@ref(eq:cvIR)$ with an assumed CV of 0.2 reflecting moderate precision associated with estimated harvest.

Estimated annual harvest of Deshka River Chinook upstream of the Deshka weir $\widehat{H}_{Dy}$ was
\begin{equation}
\widehat{H}_{Dy}~=~H_{Dy}exp(\epsilon_{HAy})
   (\#eq:HAhat)
\end{equation}

Radio telemetry final destinations within each stock group $\mathbf{r}_{sy} = (\begin{array}{am} r_{sy1} & r_{sy2} & \dots & r_{syT} \end{array})$ were partitioned into $T$ categories with $T-1$ categories representing tributaries within the stock group that are counted during aerial surveys and one category ($T$) representing all tributaries that were not counted during aerial surveys. Radio tags located in tributaries that were not counted during aerial surveys were
\begin{equation}
r_{syT}~\sim~\textrm{Binomial}\left(\rho\prime_{sy}, \sum_t^T r_{syt}\right)
   (\#eq:nosurvey)
\end{equation}
where $\rho\prime_{sy}$ estimates the annual proportion of radio tagged fish from stock $s$ that spawned in tributaries that were not monitored by aerial survey. Equations analogous to eq. $\@ref(eq:Dage)$ and eq. $\@ref(eq:pi)$ (without the regression component) were used to define the prior structure on $\rho\prime_{sy}$.
  
Radio tags located within within tributaries that were counted during aerial surveys $r_{sy[1:(T-1)]}$ were:
\begin{equation}
r_{sy[1:(T-1)]}~\sim~\textrm{Multinomial}\left(\rho^*_{syt}, \sum_t^{T-1} r_{syt}\right)
   (\#eq:survey)
\end{equation}
where $\rho^*_{syt}$ estimates the annual proportion of radio tagged fish from stock $s$ that spawned in tributary $t$.
  
Stock composition was calculated as:
\begin{equation}
\rho_{syt}~=~\left(\begin{array}{} \rho^*_{sy1}(1-\rho\prime_{sy}) & \rho^*_{sy2}(1-\rho\prime_{sy}) & \dots & \rho\prime_{sy} \end{array}\right)
   (\#eq:pcomp)
\end{equation}

The proportion of the spawning escapement counted during single aerial surveys $\theta_t$ was
\begin{equation}
\textrm{logit}(\theta_t)~\sim~\textrm{Normal}(\mu_\theta, \sigma^2_\theta)
   (\#eq:theta)
\end{equation}

Annual single aerial surveys $as_{yt}$ were available for sixteen tributaries $t$. Each survey is related to abundance for the stock group within which it was located:
\begin{equation}
as_{yt}~=~\theta_t\rho_{syt}S_{ys}exp(\epsilon_{ASt})
   (\#eq:as)
\end{equation}
where the $\epsilon_{ASt}~\sim~\textrm{Normal}(0, \sigma^2_{ASt})$ and $\sigma_{ASt}~\sim~\textrm{half_Cauchy}(0, B_{AS})$ where $B_{AS}$ is the median of the distribution of $\sigma_{ASt}$.
  
Weirs counts were available for three tributaries. Each weir count is related to abundance for the stock group within which it was located:
\begin{equation}
wc_{yt}~=~\rho_{syt}S_{ys}exp(\epsilon_{WC})
   (\#eq:weir)
\end{equation}
where the $\epsilon_{WC}~\sim~\textrm{Normal}(0, \sigma_{WC}^2)$ and the variances followed eq. $\@ref(eq:cvIR)$ with an assumed CV of 0.05 reflecting good precision associated with weir counts.
  
The scale-age counts $x_{yac}$ were modeled as multinomially distributed 
\begin{equation}
x_{yac}~=~\textrm{Multinomial}\left(q^*_{yac}, \sum_{(a=3)}^6 x_{yac}\right)
   (\#eq:xage)
\end{equation}
The location parameters are
\begin{equation}
q^*_{yac}~=~\frac{exp\left[\textrm{ln}\left(\frac{N_{ya}}{N_{y(a=3)}}\right)+b_{ca}I_c\right]}{\sum_a exp\left[\textrm{ln}\left(\frac{N_{ya}}{N_{y(a=3)}}\right)+b_{ca} I_c\right]}
   (\#eq:qstar)
\end{equation}
which represents a multinomial logistic regression where the intercept is a function of annual abundance in each age class and the categorical covariates account for age-related sampling bias. The parameters $b_{ca}$ represent bias adjustments for sample type $c$ (weir, creel and carcass survey/fishwheel samples respectively) in age $a$ for  while covariates $I_c$ represent indicator variables for each sample type. Because $b_{1a}=0$ weir samples are considered unbiased and estimated annual age composition is:
\begin{equation}
q_{yt}~=~\frac{N_{ya}}{\sum_{a=3}^6 N_{y}}
   (\#eq:qstar)
\end{equation}

##Model Fitting
Model fitting involves finding the values of the population parameters that could have plausibly resulted in the data that were observed. To do so, Markov Chain Monte Carlo (MCMC) methods were employed using the package RJAGS (Plummer 2013) within R (R Core Team 2016). This methodology allows for inclusion of the effects of measurement error, serially-correlated productivity, and missing data into the analysis and provides a more realistic assessment of uncertainty than is possible with classical statistical methods. By properly specifying process variation, measurement error, and time-dependent linkage in the model, biases in the estimates can be reduced (Su and Peterman 2012).
  
Bayesian statistical methods employ the language of probability to quantify uncertainty about model parameters. Knowledge existing about the parameters outside the framework of this analysis is the “prior” probability distribution. The output of the Bayesian analysis is called the “posterior” probability distribution, which is a synthesis of the prior information and the information contained in the data. See Fleischman et al. (2013) and Staton et al. (2016) for similar applications of the methods used in this report. 
  
###Prior Distributions
Non-informative priors (chosen to have minimal effect on the posterior) were used for most parameters. Initial recruitments $R_{1973}-R_{1978}$ (those lacking linked spawner abundance) were modeled as drawn from a common log-normal distribution with median $\mu_{logR}$ and variance $\sigma^2_{logR}$. Truncated normal priors with mean zero, very large variances, and constrained to be positive were used for $\mu_{log(\alpha)}$, $\beta$, $\mu_{logR}$, . Initial model residual $\nu_s$ were given a truncated normal prior with mean zero and variance $\sigma^2_{Ws}/(1-\phi^2_s)$ between -3 and 3. Annual harvest rates ($\mu_{By}, \mu_{Asy}, \mu_{Dy}$) were given $\textrm{beta}(0.5,0.5)$ priors. Diffuse conjugate inverse gamma priors were used for $\sigma^2_{Ws}, \sigma^2_{logR}$. Dirichlet dispersion parameters $1/\sqrt{D}$ for age and stock composition have $\textrm{Uniform}(0.1,1)$ priors. $B_{AS}$, $p_{500y3}$ and $p_{500y4}$ have $\textrm{Uniform}(0,1)$ priors.
  
###Sampling from the Posterior Distribution
MCMC samples were drawn from the joint posterior probability distribution of all unknowns in the model. The model was initiated with `r post$mcmc.info$n.chains` chains and `r format(post$mcmc.info$n.iter, big.mark = ",", scientific = 100)` samples were generated per chain. The first `r format(post$mcmc.info$n.burnin, big.mark = ",", scientific = 100)` samples from each chain were discarded and the remaining samples were thinning by a factor of `r post$mcmc.info$n.thin`, resulting in `r format(post$mcmc.info$n.samples, big.mark = ",", scientific = 100)` samples that were used to estimate the marginal posterior means, standard deviations, and percentiles. The diagnostic tool ShinySTAN (Stan Development Team 2016) was used to assess mixing and convergence, and no major problems were encountered. Interval estimates were constructed from the percentiles of the posterior distribution.

##Reference Points and Optimal Yield Profiles
Reference points were calculated for each individual MCMC sample. Spawning abundance providing maximum sustained yield (MSY) $S_{MSY}$ was approximated
\begin{equation}
S_{MSYs}~\cong~\frac{\textrm{ln}(\alpha\prime_s)}{\beta}[0.5-0.07\textrm{ln}(\alpha\prime_s)]
   (\#eq:SMSY)
\end{equation}
Sustained yield at a specified level of $S$ was obtained by subtracting spawning escapement from recruitment:
\begin{equation}
Y_{Ss}~=~R_s-S_s~=~S_{s}exp(\textrm{ln}(\alpha\prime_s)-\beta_s S_{s})-S_s
   (\#eq:Ys)
\end{equation}
Other relevant quantities include harvest rate leading to maximum sustained yield, approximated by (Hilborn 1985)
\begin{equation}
U_{MSYs}~\cong~\textrm{ln}(\alpha\prime_s)[0.5-0.07\textrm{ln}(\alpha\prime_s)]
   (\#eq:UMSY)
\end{equation}
escapement leading to maximum sustained recruitment (MSR)
\begin{equation}
S_{MSRs}~=~\frac{1}{\beta_s}
   (\#eq:SMSR)
\end{equation}
and equilibrium spawning abundance, where recruitment exactly replaces spawners:
\begin{equation}
S_{EQs}~=~\frac{\textrm{ln}(\alpha\prime_s)}{\beta_s}
   (\#eq:SEQ)
\end{equation}
The quantity
\begin{equation}
\textrm{ln}(\alpha\prime_s)~=~\textrm{ln}(\alpha_s)+\frac{\sigma^2_{Ws}}{2(1-\phi_s^2)}
   (\#eq:alphaprime)
\end{equation}
in Equations $\@ref(eq:SMSY)$, $\@ref(eq:Ys)$, $\@ref(eq:UMSY)$, and $\@ref(eq:SEQ)$ adjusts for the difference between the median and the mean of a right-skewed log-normal error distribution autocorrelation.

The probability that a given spawning escapement $S$ would produce average yields ($Y_S$) exceeding X% of MSY was obtained by calculating $Y_S$ at incremental values of $S$ for each MCMC sample, then comparing $Y_S$ with X% of the value of MSY for that sample. The proportion of samples in which $Y_S$ exceeded X% of MSY is an estimate of the desired probability, and the plot of proportion versus $S$ is termed an optimal yield profile (OYP; Fleischman et al. 2013).

The probability that yield would be reduced to less than X% of MSY by supplying too few spawners $S$ was obtained by calculating $Y_S$ at incremental values of $S$ and tallying the number of MCMC samples for which $Y_S$ was less than X% of MSY and $S$ was less than $S_{MSY}$. A plot of the fraction of samples in which this condition occurred versus $S$ is termed an overfishing profile (Bernard and Jones III 2010).

The probability that a given spawning escapement $S$ would produce average recruitment $R$ exceeding X% of MSR was obtained by calculating $R$ (Equation 1) at incremental values of $S$ for each MCMC sample, then comparing $R$ with X% of the value of MSR for that sample. The proportion of samples in which $R$ exceeded X% of MSR is an estimate of the desired probability, and the plot of the proportion versus $S$ is termed an optimal recruitment profile (ORP; Fleischman et al. 2013).

OYPs Overfishing profiles and ORPs were used to quantify the yield (or recruitment) performance of prospective escapement goals, taking into consideration the uncertainty about the true abundance, productivity, and capacity of the stock.

##Escapement Goals Standardized To $S_{MSY}$
For purposes of comparing escapement goals across stocks, we divided the lower and upper bounds of 21 published goals for Alaska Chinook salmon (Munro and Volk 2016) by point estimates of $S_{MSY}$ for each stock, thereby expressing all goal ranges in terms of multiples of $S_{MSY}$. These values were multiplied by estimates of $S_{MSY}$ for each stock group to provide a graphical comparison of the recommended goals with those from other stocks.

##Escapement Goal Review Process
An inter-divisional escapement goal review team was convened to review the available data, discuss analyses and results, and make escapement goal recommendations. The escapement goals recommended in this report are the product of several collaborative meetings of the review team and other ADF&G staff. The final recommendation was reached by consensus of fisheries scientists and regional research coordinators from both fisheries divisions.

#Results
##Deshka River
```{r echo=FALSE, include=FALSE}
digits <-
  function(p){
    ps <- ifelse(p < 0.01, format(p, TRUE, digits = 2, scientific = TRUE),
                 ifelse(p < 2, format(round(p, 2), TRUE, nsmall = 2),
                        ifelse(p < 100, format(round(p, 1), TRUE, nsmall = 1),
                               format(round(p, 0), TRUE, nsmall = 0, width = 5, scientific = FALSE, big.mark = ","))))
  return(ps)
}

S <- 
  post$summary[grepl("S\\[\\d+,\\d\\]", rownames(post$summary)),] %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column() %>%
  dplyr::rename(q50 = '50%') %>% 
  dplyr::mutate(stock = as.numeric(gsub("S\\[\\d+,(\\d)\\]", "\\1", rowname)),
                year = year_id[as.numeric(gsub("S\\[(\\d+),\\d\\]", "\\1", rowname))]) %>%
                  dplyr::select(rowname, stock, year, q50)
IR <- 
  post$summary[grepl("IR\\[\\d+,\\d\\]", rownames(post$summary)),] %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column() %>%
  dplyr::rename(q50 = '50%') %>%
  dplyr::mutate(stock = as.numeric(gsub("IR\\[\\d+,(\\d)\\]", "\\1", rowname)),
                year = year_id[as.numeric(gsub("IR\\[(\\d+),\\d\\]", "\\1", rowname))]) %>%
  dplyr::select(rowname, stock, year, q50)
minrow <- function(dat, n){
  dat %>% 
    dplyr::filter(stock == n) %>% 
    dplyr::slice(which.min(q50)) %>%
    dplyr::mutate(median = digits(q50))}
  
maxrow <- function(dat, n){
  dat %>% 
    dplyr::filter(stock == n) %>% 
    dplyr::slice(which.max(q50)) %>%
    dplyr::mutate(median = digits(q50))}

t1 <- post$summary[grepl("theta\\[1,1\\]", rownames(post$summary)), ]
CI <- function(df) paste0(digits(df['50%']), " (95%CI ", digits(df['2.5%']), "-", digits(df['97.5%']), ")")

et1 <- as[[1]]/weir[,1] 
et1_n <- sum(!is.na(et1))
et1_r <-digits(range(et1, na.rm = TRUE))

sa1 <- post$summary[grepl("sigma.air\\[1\\]", rownames(post$summary)), ]

B <- post$summary[grepl("B$", rownames(post$summary)), ]

lna1 <- post$summary[grepl("lnalpha\\[1\\]", rownames(post$summary)), ]

sw1 <- post$summary[grepl("sigma.white\\[1\\]", rownames(post$summary)), ]

phi1 <- post$summary[grepl("phi\\[1\\]", rownames(post$summary)), ]

SMSY1 <- post$summary[grepl("S.msy\\[1\\]", rownames(post$summary)), ]

SMSR1 <- post$summary[grepl("S.max\\[1\\]", rownames(post$summary)), ]

rs <- function(sn){
  rs <- post$summary[grepl(paste0("R\\[\\d+,", sn, "\\]"), rownames(post$summary)), "50%"][7:42]/
    post$summary[grepl(paste0("S\\[\\d+,", sn, "\\]"), rownames(post$summary)), "50%"][1:36]
  list(min = digits(range(rs)[1]),
       max = digits(range(rs)[2]),
       n = sum(rs < 1)
  )
}

prob_e <- get_profileprobs(get_profile(post, "Deshka"), c(13000, 27000))
prob_p <- get_profileprobs(get_profile(post, "Deshka"), c(10000, 11000))
```
Deshka River Chinook salmon escapement estimates are proportional to annual single aerial surveys through 1994 and to annual weir counts and sporadic single aerial surveys after 1994 (Figure 2, Appendix B1). Five years (2013-2017) of mark-recapture based inriver run estimates are also available. All measures of abundance display a common trend through time and modeled estimates of inriver run were all within the 95% CI of the Deshka River mark-recapture estimates. Runs were large prior to 1991, underwent a decline during 1991-1994, rebounded during 1995-2004, declined again staring in 2005 and remained at a lower level during 2008-2017. Escapement estimates ranged between `r minrow(S, 1)$median` in `r minrow(S, 1)$year` and `r maxrow(S, 1)$median` in `r maxrow(S, 1)$year` while inriver run estimates ranged from `r minrow(IR, 1)$median` in `r minrow(IR, 1)$year` and `r maxrow(IR, 1)$median` in `r maxrow(IR, 1)$year`. Estimates of abundance are very imprecise prior to 1995, when weir counts became available.
  
The model estimated proportion of the escapement observed during single aerial surveys of the Deshka River `r CI(t1)`(Table 1) does not include annual variation which is sure to exist. Empirical estimates of observability (survey count/weir count) exist for `r et1_n` years and range from `r paste0(et1_r[1], "-", et1_r[2])`. In this model annual variability is included in the log-normal error term from the relationship between survey counts and estimated escapement $\@ref(eq:as)$. There was moderate agreement between Deshka River single aerial survey counts (expanded by inverse observability) and other indices of abundance on the Deshka River.  The log-normal standard deviation for the Deshka River aerial survey regression was `r CI(sa1)`, which is close to the median value for the distribution of $\sigma_{AS}$ (`r CI(B)`).
  
Total run estimates (Figure 3 second panel, Appendix B1) are marginally more precisely than escapement estimates because harvest is relatively well estimated. Coefficients of variation for total run are generally greater than 0.2 prior to 1995 and less than 0.1 after 1995. Coefficients of variation for recruitment (Figure 3 third panel) were larger (0.1 – 0.4) particularly at the beginning and end of the data series, when one or more age classes were missing. Harvest rates for Deshka River Chinook salmon have been below levels that would maximize yield but have approached levels that would maximize recruitment during 1991-1993 (Figure 3 fourth panel).
  
Estimates of population parameters from the state-space model take the measurement errors in escapement S and recruitment R (Figure 4 error bars) into account. The individual data pairs are weighted depending upon the certainty with which the individual values of S and R are known. Because measurement error is substantial for many brood years, and due to other sources of uncertainty, Ricker SR relationships that could have plausibly generated the observed data are diverse (Figure 4: light lines), often deviating substantially from the median Ricker relationship (Figure 4: heavy dashed line).
  
Median productivity (recruits per spawner, in the absence of density effects) of Deshka River Chinook salmon during 1979–2014 has been moderate ($\textrm{ln}(\alpha)$ = `r CI(lna1)`; Table 2). There is a great deal of uncertainty about productivity, as evident in the extent to which the plausible SR relationships differ with respect to their slope at the origin (Figure 4). Similarly, uncertainty about $\beta$ is reflected in variability in the escapements leading to maximum recruitment $S_{MSR}$, and uncertainty about equilibrium abundance $S_{EQ}$ is reflected by variability in the in the escapements where the curves intersect the replacement line. There is considerable variation around the Ricker estimated mean ($\sigma_W$ = `r CI(sw1)`).
  
The Ricker recruitment residuals in Figure 2 (bottom panel) are deviations in recruitment of Deshka River Chinook salmon from that predicted by the Ricker SR relationship, reflecting time-varying changes in productivity after controlling for density-dependent effects. Deshka Chinook had high productivity through the 1986 brood year, experienced a sharp decline declined during 1987-1991, remained slightly above average through 2001 and has remained at or below average since. Model residuals are positively correlated supporting the concept of time-varying productivity ($\phi$ = `r CI(phi1)`).
  
Sustained yield is the number of fish in the expected recruitment over and above that needed to replace the spawners. Escapement goals in Alaska are developed to maximize sustained yield by choosing a range of escapements around $S_{MSY}$, the theoretical number of spawners that will result in the largest difference between recruitment and replacement. Graphically, this is the escapement which maximizes the length of a vertical line drawn from the Ricker curve downward to the replacement line. Given the diversity of plausible SR relationships (Figure 4), it is important to choose an escapement goal that is robust to this uncertainty rather than one tailored solely to the median SR relationship. To address this uncertainty we tallied the success or failure of a given number of spawners to achieve biological reference points across plausible SR relationships.
  
Deshka River Chinook salmon escapement leading to maximum sustained yield $S_{MSY}$ (Table 2) was estimated to be `r CI(SMSY1)`. The optimal yield profiles in Figure 5 (top panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSY. These probabilities, which are highest near $S_{MSY}$ can be used to quantify the yield performance of prospective escapement goals (Figure 5 shaded areas), taking into consideration all of the uncertainty about the true abundance and productivity of the stock. The overfishing profiles (Figure 5 middle panel) show the probability that sustained yield would be reduced to less than 70%, 80%, or 90% of MSY by fishing too hard and supplying too few spawners. For this stock, these probabilities are nearly the exact complements of the probabilities in the left-hand limbs of the optimal yield profiles.
  
Expected sustained yield (number of fish over and above that necessary to replace the number of spawners, averaged over brood years 1979–2015) is also maximized at $S_{MSY}$ (Figure 6). Realized yield in any single year varies widely, return per spawner varied between `r rs(1)$min` and `r rs(1)$max` for Deshka River Chinook salmon with `r rs(1)$n` of 36 complete brood years failing to replace themselves.
  
Fishery managers may want to evaluate existing and proposed goal ranges with respect the other indicators of fishery performance. In some sport fisheries run sizes and high catch rates are an important priority. Run size is associated with large recruitment. The escapement leading to maximum recruitment $S_{MSR}$ was estimated to be `r CI(SMSR1)`(Table 2). Analogous to the optimum yield profiles discussed above optimum recruitment profiles tally the success or failure of a given number of spawners to maximize recruitment across plausible SR relationships. The optimal recruitment profiles in Figure 5 (bottom panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSR. Optimum Recruitment probabilities, which are highest near $S_{MSR}$, reach maximums at larger spawning abundances than optimum yield probabilities and decrease more slowly as spawning abundance increases.
  
Deshka River Chinook salmon have an existing goal range of 13,000-27,000 Chinook salmon. Escapements at the low end of the existing range have a `r prob_e[[1, "OYP80"]]`% probability of producing a yield within 80% of MSY while escapements at the upper end of the existing range have a `r prob_e[[2, "OYP80"]]`% probability of producing yields within 80% or MSY. With respect to recruitment, escapements at the low end of the existing range have a `r prob_e[[1, "ORP80"]]`% probability of producing a yield within 80% of MSR while escapements at the upper end of the existing range have a `r prob_e[[2, "ORP80"]]`% probability of producing yields within 80% or MSR. 
  
Proposed escapement goals were determined by ?. The proposed escapement goal has a `r prob_p[[1, "OYP80"]]`% probability of achieving 80% of MSY at the lower bound and a `r prob_p[[2, "OYP80"]]`% probability of achieving MSY at the upper bound. With respect to recruitment, the proposed escapement goal shown has a `r prob_p[[1, "ORP80"]]`% probability of achieving 80% of MSR at the lower bound and a `r prob_p[[2, "ORP80"]]`% probability of achieving 80% of MSR at the upper bound.
  
##East Susitna
```{r echo=FALSE, include=FALSE}
D2 <- post$summary[grepl("Dsum.S2", rownames(post$summary)), ]
B2 <- post$summary[grepl("Bsum.So\\[1", rownames(post$summary)), ]

p2out <-digits(post$summary[grepl("p.S2\\[\\d+,7\\]", rownames(post$summary)), "mean"] * 100)

t2 <- post$summary[grepl("theta\\[2,1\\]", rownames(post$summary)), ]
t3 <- post$summary[grepl("theta\\[3,1\\]", rownames(post$summary)), ]
t4 <- post$summary[grepl("theta\\[4,1\\]", rownames(post$summary)), ]
t5 <- post$summary[grepl("theta\\[5,1\\]", rownames(post$summary)), ]
t6 <- post$summary[grepl("theta\\[6,1\\]", rownames(post$summary)), ]
t7 <- post$summary[grepl("theta\\[7,1\\]", rownames(post$summary)), ]

et2 <- as[[2]][,4]/weir[,2] 
et2_n <- sum(!is.na(et2))
et2_r <- digits(et2[!is.na(et2)])

et3 <- as[[2]][,6]/weir[,3] 
et3_n <- sum(!is.na(et3))
et3_r <- digits(et3[!is.na(et3)])

sa2 <- post$summary[grepl("sigma.air\\[2\\]", rownames(post$summary)), ]
sa3 <- post$summary[grepl("sigma.air\\[3\\]", rownames(post$summary)), ]
sa4 <- post$summary[grepl("sigma.air\\[4\\]", rownames(post$summary)), ]
sa5 <- post$summary[grepl("sigma.air\\[5\\]", rownames(post$summary)), ]
sa6 <- post$summary[grepl("sigma.air\\[6\\]", rownames(post$summary)), ]
sa7 <- post$summary[grepl("sigma.air\\[7\\]", rownames(post$summary)), ]

lna2 <- post$summary[grepl("lnalpha\\[2\\]", rownames(post$summary)), ]

sw2 <- post$summary[grepl("sigma.white\\[2\\]", rownames(post$summary)), ]

phi2 <- post$summary[grepl("phi\\[2\\]", rownames(post$summary)), ]

SMSY2 <- post$summary[grepl("S.msy\\[2\\]", rownames(post$summary)), ]

SMSR2 <- post$summary[grepl("S.max\\[2\\]", rownames(post$summary)), ]

prob_p2 <- get_profileprobs(get_profile(post, "East Susitna"), c(10000, 11000))
```
East Susitna Chinook salmon escapement estimates are proportional to 6 annual single aerial surveys and infrequent weir counts on 2 substocks (Figure 7). Five years (2013-2017) of mark recapture based inriver run estimates are available. Measures of abundance display a common trend through time although in 2015 the mark recapture estimate was much higher that would be expected based on aerial survey data alone. Runs were small prior to 1983 increased during 1983-1997, underwent a decline during 1998-2012, and rebounded slightly after 2012. Escapement estimates ranged between `r minrow(S, 2)$median` in `r minrow(S, 2)$year` and `r maxrow(S, 2)$median` in `r maxrow(S, 2)$year` while inriver run estimates ranged from `r minrow(IR, 2)$median` in `r minrow(IR, 2)$year` and `r maxrow(IR, 2)$median` in `r maxrow(IR, 2)$year`. Estimates of abundance are precise throughout the time series.
  
Stock composition (Figure 8, Appendix C1) estimates are handled differently for surveyed and unsurveyed spawning areas within the model. For surveyed areas multinomial logistic regression is used to allow stock composition estimates to trend through time. Because empirical stock composition data only exists for late in the time series (2012-2017) estimated changes in stock composition early in the time series represent changes in the relative magnitude of the single aerial survey counts. In this model changes in survey relative abundance are assumed to reflect changes in stock composition, although trends in relative observability could result in similar data. This assumption is supported by consistent survey procedures utilized throughout the time series. Among the surveyed streams within the East Susitna stock group Little Willow and Willow Creeks increased in relative abundance between 1979 and 2017 while Goose, Kashwitna, Montana and Sheep Creeks decreased in relative abundance. Most recently, Willow Creek is the largest component of spawning abundance followed by Little Willow Creek, Montana Creek, Sheep Creek,  Kashwitna River and Goose Creek. The inverse dispersion for the East Susitna stock group is large (D = `r CI(D2)`, Table 3) indicating trends in the relative magnitude of survey counts and radio telemetry data are well explained by the multinomial logistic regression model with a calendar year covariate. Interestingly, there is considerable divergence between estimated stock composition and our empirical stock composition estimates in some years, which represent situations where weighted relative survey counts and telemetry data disagree.
  
Because unsurveyed streams in the East Susitna stock group lack relative composition information early in the time series, no trend can be estimated. Unsurvey streams comprise `r min(p2out)`-`r max(p2out)`% (Figure 8, Appendix C1) of the East Susitna stock group. Inverse dispersion is small (B = `r CI(B2)`, Table 3) indicating high variability in the proportion of the East Susitna stock group which spawns within the 6 surveyed streams. High variability was documented with empirical telemetry data.
  
The model estimated proportion of the escapement observed during single aerial surveys of Goose Creek `r CI(t2)`(Table 1) does not include annual variation which is sure to exist. In this model annual variability is included in the log-normal error term from the relationship between survey counts and estimated escapement eq. $\@ref(eq:as)$. There was good agreement between Goose Creek single aerial survey counts (expanded by inverse observability and stock composition) and other indices of smaller than the median value for the distribution of $\sigma_{AS}$ (`r CI(B)`).
  
The model estimated proportion of the escapement observed during single aerial surveys of the Kashwitna River `r CI(t3)`(Table 1) does not include annual variation which is sure to exist. There was poor agreement between the Kashwitna River single aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the East Susitna stock group.  The log-normal standard deviation for the Kashwitna River aerial survey regression was `r CI(sa3)`, which is larger than the median value for the distribution of $\sigma_{AS}$.
  
The model estimated proportion of the escapement observed during single aerial surveys of Little Willow Creek `r CI(t4)`(Table 1) does not include annual variation which is sure to exist. There was good agreement between Little Willow Creek single aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the East Susitna stock group.  The log-normal standard deviation for the Little Willow Creek aerial survey regression was `r CI(sa4)`, which is smaller than the median value for the distribution of $\sigma_{AS}$.
  
The model estimated proportion of the escapement observed during single aerial surveys of Montana Creek `r CI(t5)`(Table 1) does not include annual variation which is sure to exist. Empirical estimates of observability (survey count/weir count) exist for `r et2_n` years and were `r et2_r[1]` and `r et2_r[2]`. There was good agreement between Montana Creek single aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the East Susitna stock group.  The log-normal standard deviation for the Montana Creek aerial survey regression was `r CI(sa5)`, which is smaller than the median value for the distribution of $\sigma_{AS}$.
  
The model estimated proportion of the escapement observed during single aerial surveys of Sheep Creek `r CI(t6)`(Table 1) does not include annual variation which is sure to exist. There was poor agreement between Sheep Creek single aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the East Susitna stock group.  The log-normal standard deviation for the Sheep Creek aerial survey regression was `r CI(sa6)`, which is larger than the median value for the distribution of $\sigma_{AS}$.
  
The model estimated proportion of the escapement observed during single aerial surveys of Willow Creek `r CI(t7)`(Table 1) does not include annual variation which is sure to exist. Empirical estimates of observability (survey count/weir count) exist for `r et3_n` years and were `r et3_r[1]`, `r et3_r[2]` and `r et3_r[3]`. There was good agreement between Willow Creek single aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the East Susitna stock group.  The log-normal standard deviation for the Willow Creek aerial survey regression was `r CI(sa7)`, which is smaller than the median value for the distribution of $\sigma_{AS}$.

Total run estimates (Figure 9 second panel, Appendix B2) are more precise than escapement estimates because harvest is relatively well estimated. Coefficients of variation for total run are generally less than 0.15. Coefficients of variation for recruitment (Figure 9 middle panel) were generally less than 20% except at the beginning and end of the data series, when one or more age classes were missing.  Harvest rates for East Susitna Chinook salmon approached levels that would maximize yield during 1992-1994 and have been close to levels that would maximize recruitment during 1986-1991 and again during 1995-2008 (Figure 9 fourth panel).
  
Estimates of population parameters from the state-space model take the measurement errors in escapement S and recruitment R (Figure 10 error bars) into account. The individual data pairs are weighted depending upon the certainty with which the individual values of S and R are known. Because measurement error is substantial for many brood years, and due to other sources of uncertainty, Ricker SR relationships that could have plausibly generated the observed data are diverse (Figure 10: light lines), often deviating substantially from the median Ricker relationship (Figure 10: heavy dashed line).
  
Median productivity (recruits per spawner, in the absence of density effects) of East Susitna Chinook salmon during 1979–2014 has been low ($\textrm{ln}(\alpha)$ = `r CI(lna2)`; Table 3). There is a great deal of uncertainty about productivity, as evident in the extent to which the plausible SR relationships differ with respect to their slope at the origin (Figure 10). Similarly, uncertainty about $\beta$ is reflected in variability in the escapements leading to maximum recruitment SMSR, and uncertainty about equilibrium abundance$S_{EQ}$ is reflected by variability in the in the escapements where the curves intersect the replacement line. There is moderate variation around the Ricker estimated mean ($\sigma_W$ = `r CI(sw2)`).
  
The Ricker recruitment residuals in Figure 9 (bottom panel) are deviations in recruitment of East Susitna Chinook salmon from that predicted by the Ricker SR relationship, reflecting time-varying changes in productivity after controlling for density-dependent effects. East Susitna Chinook had mostly above average productivity through the 2001 brood year, experienced an extended period of below average productivity during 2002-2011, and returned to average productivity in the 2012 brood year. Examination of the Ricker residuals in conjunction with the horsetail plot (Figure 10) suggest two productivity regimes for the East Susitna stock group, while average productivity does not fit either regime particularly well, although a mechanism driving patterned productivity is unknown. Model residuals are strongly positively correlated supporting the concept of time-varying productivity ($\phi$ = `r CI(phi2)`).

Sustained yield is the number of fish in the expected recruitment over and above that needed to replace the spawners. Escapement goals in Alaska are developed to maximize sustained yield by choosing a range of escapements around $S_{MSY}$, the theoretical number of spawners that will result in the largest difference between recruitment and replacement. Graphically, this is the escapement which maximizes the length of a vertical line drawn from the Ricker curve downward to the replacement line. Given the diversity of plausible SR relationships (Figure 10), it is important to choose an escapement goal that is robust to this uncertainty rather than one tailored solely to the median SR relationship. To address this uncertainty we tallied the success or failure of a given number of spawners to achieve biological reference points across plausible SR relationships.
  
East Susitna Chinook salmon escapement leading to maximum sustained yield $S_{MSY}$ was estimated to be `r CI(SMSY2)`. The optimal yield profiles in Figure 11 (top panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSY. These probabilities, which are highest near $S_{MSY}$ can be used to quantify the yield performance of prospective escapement goals (Figure 11 shaded areas), taking into consideration all of the uncertainty about the true abundance and productivity of the stock. The overfishing profiles (Figure 11 middle panel) show the probability that sustained yield would be reduced to less than 70%, 80%, or 90% of MSY by fishing too hard and supplying too few spawners. For this stock, these probabilities are nearly the exact complements of the probabilities in the left-hand limbs of the optimal yield profiles.
  
Expected sustained yield (number of fish over and above that necessary to replace the number of spawners, averaged over brood years 1979–2015) is also maximized at $S_{MSY}$ (Figure 12). Realized yield in any single year varies widely, return per spawner varied between between `r rs(2)$min` and `r rs(2)$max` for East Susitna Chinook salmon with `r rs(2)$n` of 36 complete brood years failing to replace themselves.
  
Fishery managers may want to evaluate existing and proposed goal ranges with respect to other indicators of fishery performance. In some sport fisheries run sizes and high catch rates are an important priority. Run size is associated with large recruitment. Escapement leading to maximum recruitment $S_{MSR}$ was estimated to be `r CI(SMSR2)`. Analogous to the optimum yield profiles discussed above optimum recruitment profiles tally the success or failure of a given number of spawners to maximize recruitment across plausible SR relationships. The optimal recruitment profiles in Figure 11 (bottom panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSR. Optimum Recruitment probabilities, which are highest near $S_{MSR}$, reach maximums at larger spawning abundances than optimum yield probabilities and decrease more slowly as spawning abundance increases.
  
Goose Creek, Little Willow Creek, Montana Creek, Sheep Creek and Willow Creek have existing goals based on single aerial survey data. Existing goals use 6 pieces of information (6 single aerial survey counts) to make 6 run size determinations without considering observability of each survey. This analysis leverages the same 6 pieces of information to make one run size determination while accounting for correlation in run sizes between the sub stocks and variability in survey observability. 
  
Proposed escapement goals were determined by . The proposed escapement goal has a `r prob_p2[[1, "OYP80"]]`% probability of achieving 80% of MSY at the lower bound and a `r prob_p2[[2, "OYP80"]]`% probability of achieving MSY at the upper bound. With respect to recruitment, the proposed escapement goal has a `r prob_p2[[1, "ORP80"]]`% probability of achieving 80% of MSR at the lower bound and a `r prob_p2[[2, "ORP80"]]`% probability of achieving 80% of MSR at the upper bound.
  
##Talkeetna
```{r echo=FALSE, include=FALSE}
D3 <- post$summary[grepl("Dsum.S3", rownames(post$summary)), ]
B3 <- post$summary[grepl("Bsum.So\\[2", rownames(post$summary)), ]

p3out <-digits(post$summary[grepl("p.S3\\[\\d+,3\\]", rownames(post$summary)), "mean"] * 100)

t8 <- post$summary[grepl("theta\\[8,1\\]", rownames(post$summary)), ]
t9 <- post$summary[grepl("theta\\[9,1\\]", rownames(post$summary)), ]

sa8 <- post$summary[grepl("sigma.air\\[8\\]", rownames(post$summary)), ]
sa9 <- post$summary[grepl("sigma.air\\[9\\]", rownames(post$summary)), ]

lna3 <- post$summary[grepl("lnalpha\\[3\\]", rownames(post$summary)), ]

sw3 <- post$summary[grepl("sigma.white\\[3\\]", rownames(post$summary)), ]

phi3 <- post$summary[grepl("phi\\[3\\]", rownames(post$summary)), ]

SMSY3 <- post$summary[grepl("S.msy\\[3\\]", rownames(post$summary)), ]

SMSR3 <- post$summary[grepl("S.max\\[3\\]", rownames(post$summary)), ]

prob_p3 <- get_profileprobs(get_profile(post, "Talkeetna"), c(10000, 11000))
```
Talkeetna River Chinook salmon escapement estimates are proportional to 2 annual single aerial surveys (Figure 13). Five years (2013-2017) of mark recapture based inriver run estimates are available. Measures of abundance display a common trend through time although in 2013 the mark recapture estimate was much higher that would be expected based on aerial survey data alone. Runs increased through 1998, underwent a decline during 1999-1994, and rebounded till 1997 and gradually declined thereafter. Escapement estimates ranged between `r minrow(S, 3)$median` in `r minrow(S, 3)$year` and `r maxrow(S, 3)$median` in `r maxrow(S, 3)$year` while inriver run estimates ranged from `r minrow(IR, 3)$median` in `r minrow(IR, 3)$year` and `r maxrow(IR, 3)$median` in `r maxrow(IR, 3)$year`. Estimates of abundance are moderately precise throughout the time series.
  
Stock composition (Figure 8, Appendix C3) estimates are handled differently for surveyed and unsurveyed spawning areas within the model. For surveyed areas multinomial logistic regression is used to allow stock composition estimates to trend through time. Because empirical stock composition data only exists for late in the time series (2012-2017) estimated changes in stock composition early in the time series represent changes in the relative magnitude of the single aerial survey counts. In this model changes in survey relative abundance are assumed to reflect changes in stock composition, although trends in relative observability could result in similar data. This assumption is supported by consistent survey procedures utilized throughout the time series. Among the surveyed streams within the Talkeetna River stock group Clear Creek has increased in relative abundance between 1979 and 2017 while Prairie Creek has decreased in relative abundance. Prairie Creek remains the largest component of spawning abundance in recent years. The inverse dispersion for the Talkeetna River stock group is moderate (D = `r CI(D3)`, Table 4) indicating trends in the relative magnitude of survey counts and radio telemetry data are only moderately explained by the multinomial logistic regression model with a calendar year covariate. Interestingly, there is considerable divergence between estimated stock composition and our empirical stock composition estimates in some years, which represent situations where weighted relative survey counts and telemetry data disagree.
  
Because unsurveyed streams in the Talkeetna River stock group lack relative composition data early in the time series, no trend can be estimated. Unsurveyed streams comprise `r min(p3out)`-`r max(p3out)`% (Figure 8, Appendix C1) of the Talkeetna River stock group. Inverse dispersion is moderate (B = `r CI(B3)`, Table 4) indicating moderate variability in the proportion of the Talkeetna River stock group which spawns within the 2 surveyed streams. Moderate variability was documented with empirical telemetry data.
  
The model estimated proportion of the escapement observed during single aerial surveys of Clear Creek `r CI(t8)`(Table 1) does not include annual variation which is sure to exist. In this model annual variability is included in the log-normal error term from the relationship between survey counts and estimated escapement eq. $\@ref(eq:as)$. There was very good agreement between Clear Creek single aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Talkeetna River stock group.  The log-normal standard deviation for the Clear Creek aerial survey regression was `r CI(sa8)`, which is smaller than the median value for the distribution of $\sigma_{AS}$ (`r CI(B)`).
  
The model estimated proportion of the escapement observed during single aerial surveys of Prairie Creek `r CI(t9)`(Table 1) does not include annual variation which is sure to exist. There was very good agreement between Prairie Creek single aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Talkeetna River stock group.  The log-normal standard deviation for the Prairie Creek aerial survey regression was `r CI(sa9)`, which is smaller than the median value for the distribution of $\sigma_{AS}$.
  
Total run estimates (Figure 14 second panel, Appendix B3) are marginally more precise than escapement estimates because of low harvest levels that were relatively well estimated. Coefficients of variation for total run are generally less than 0.20. Coefficients of variation for recruitment (Figure 14 middle panel) were generally large (> 30%) particularly at the beginning and end of the data series, when one or more age classes were missing.  Harvest rates for Talkeetna River Chinook salmon were far below levels that would maximize yield but have been close to levels that would maximize recruitment most years since 1990 (Figure 14 fourth panel).
  
Estimates of population parameters from the state-space model take the measurement errors in escapement S and recruitment R (Figure 15 error bars) into account. The individual data pairs are weighted depending upon the certainty with which the individual values of S and R are known. Because measurement error is substantial for many brood years, and due to other sources of uncertainty, Ricker SR relationships that could have plausibly generated the observed data are diverse (Figure 15: light lines), often deviating substantially from the median Ricker relationship (Figure 15: heavy dashed line).
  
Median productivity (recruits per spawner, in the absence of density effects) of Talkeetna River Chinook salmon during 1979–2014 has been low ($\textrm{ln}(\alpha)$ = `r CI(lna3)`; Table 4). There is a great deal of uncertainty about productivity, as evident in the extent to which the plausible SR relationships differ with respect to their slope at the origin (Figure 15). Similarly, uncertainty about $\beta$ is reflected in variability in the escapements leading to maximum recruitment $S_{MSR}$, and uncertainty about equilibrium abundance $S_{EQ}$ is reflected by variability in the in the escapements where the curves intersect the replacement line. There is high variation around the Ricker estimated mean ($\sigma_W$ = `r CI(sw3)`).
  
The Ricker recruitment residuals in Figure 14 (bottom panel) are deviations in recruitment of Talkeetna River Chinook salmon from that predicted by the Ricker SR relationship, reflecting time-varying changes in productivity after controlling for density-dependent effects. Talkeetna River Chinook had mostly above average productivity through the 2002 brood year, and mostly below average productivity thereafter. Model residuals are weakly correlated ($\phi$ = `r CI(phi3)`).
  
Sustained yield is the number of fish in the expected recruitment over and above that needed to replace the spawners. Escapement goals in Alaska are developed to maximize sustained yield by choosing a range of escapements around $S_{MSY}$, the theoretical number of spawners that will result in the largest difference between recruitment and replacement. Graphically, this is the escapement which maximizes the length of a vertical line drawn from the Ricker curve downward to the replacement line. Given the diversity of plausible SR relationships (Figure 15), it is important to choose an escapement goal that is robust to this uncertainty rather than one tailored solely to the median SR relationship. To address this uncertainty we tallied the success or failure of a given number of spawners to achieve biological reference points across plausible SR relationships.
  
Talkeetna River Chinook salmon escapement leading to maximum sustained yield $S_{MSY}$ was estimated to be `r CI(SMSY3)`. The optimal yield profiles in Figure 16 (top panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSY. These probabilities, which are highest near SMSY can be used to quantify the yield performance of prospective escapement goals (Figure 16 shaded areas), taking into consideration all of the uncertainty about the true abundance and productivity of the stock. The overfishing profiles (Figure 16 middle panel) show the probability that sustained yield would be reduced to less than 70%, 80%, or 90% of MSY by fishing too hard and supplying too few spawners. For this stock, these probabilities are nearly the exact complements of the probabilities in the left-hand limbs of the optimal yield profiles.
  
Expected sustained yield (number of fish over and above that necessary to replace the number of spawners, averaged over brood years 1979–2015) is also maximized at $S_{MSY}$ (Figure 16). Realized yield in any single year varies widely, return per spawner varied between between `r rs(3)$min` and `r rs(3)$max` for Talkeetna River Chinook salmon with `r rs(3)$n` of 36 complete brood years failing to replace themselves.

Fishery managers may want to evaluate existing and proposed goal ranges with respect the other indicators of fishery performance. In some sport fisheries run sizes and high catch rates are an important priority. Run size is associated with large recruitment. Escapement leading to maximum recruitment $S_{MSR}$ was estimated to be `r CI(SMSR3)`. Analogous to the optimum yield profiles discussed above optimum recruitment profiles tally the success or failure of a given number of spawners to maximize recruitment across plausible SR relationships. The optimal recruitment profiles in Figure 16 (bottom panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSR. Optimum Recruitment probabilities, which are highest near $S_{MSR}$, reach maximums at larger spawning abundances than optimum yield probabilities and decrease more slowly as spawning abundance increases.
  
Clear Creek and Prairie Creek have existing goals based on single aerial survey data. Existing goals use 2 pieces of information (2 single aerial survey counts) to make 2 run size determinations without considering observability of each survey. This analysis leverages the same 2 pieces of information to make one run size determination while accounting for correlation in run sizes between the sub stocks and variability in survey observability. 
  
Proposed escapement goals were determined by. The proposed escapement goal has a `r prob_p3[[1, "OYP80"]]`% probability of achieving 80% of MSY at the lower bound and a `r prob_p3[[2, "OYP80"]]`% probability of achieving MSY at the upper bound. With respect to recruitment, the proposed escapement goal has a `r prob_p3[[1, "ORP80"]]`% probability of achieving 80% of MSR at the lower bound and a `r prob_p3[[2, "ORP80"]]`% probability of achieving 80% of MSR at the upper bound.

##Yentna
```{r echo=FALSE, include=FALSE}
D4 <- post$summary[grepl("Dsum.S4", rownames(post$summary)), ]
B4 <- post$summary[grepl("Bsum.So\\[3", rownames(post$summary)), ]

p4out <-digits(post$summary[grepl("p.S4\\[\\d+,5\\]", rownames(post$summary)), "mean"] * 100)

t10 <- post$summary[grepl("theta\\[10,1\\]", rownames(post$summary)), ]
t11 <- post$summary[grepl("theta\\[11,1\\]", rownames(post$summary)), ]
t12 <- post$summary[grepl("theta\\[12,1\\]", rownames(post$summary)), ]
t13 <- post$summary[grepl("theta\\[13,1\\]", rownames(post$summary)), ]

sa10 <- post$summary[grepl("sigma.air\\[10\\]", rownames(post$summary)), ]
sa11 <- post$summary[grepl("sigma.air\\[11\\]", rownames(post$summary)), ]
sa12 <- post$summary[grepl("sigma.air\\[12\\]", rownames(post$summary)), ]
sa13 <- post$summary[grepl("sigma.air\\[13\\]", rownames(post$summary)), ]

lna4 <- post$summary[grepl("lnalpha\\[4\\]", rownames(post$summary)), ]

sw4 <- post$summary[grepl("sigma.white\\[4\\]", rownames(post$summary)), ]

phi4 <- post$summary[grepl("phi\\[4\\]", rownames(post$summary)), ]

SMSY4 <- post$summary[grepl("S.msy\\[4\\]", rownames(post$summary)), ]

SMSR4 <- post$summary[grepl("S.max\\[4\\]", rownames(post$summary)), ]

prob_p4 <- get_profileprobs(get_profile(post, "Yentna"), c(10000, 11000))
```
Yentna River Chinook salmon escapement estimates are proportional to 4 annual single aerial surveys (Figure 18). Four years (2014-2017) of mark recapture based inriver run estimates are available. Measures of abundance display a common trend through time. Runs increased through 1984, underwent a decline during 1985-1994, and rebounded till 2004, declined again through 2012 and varied at historically low levels thereafter. Escapement estimates ranged between `r minrow(S, 4)$median` in `r minrow(S, 4)$year` and `r maxrow(S, 4)$median` in `r maxrow(S, 4)$year` while inriver run estimates ranged from `r minrow(IR, 4)$median` in `r minrow(IR, 4)$year` and `r maxrow(IR, 4)$median` in `r maxrow(IR, 4)$year`. Estimates of abundance are moderately precise throughout the time series.
  
Stock composition (Figure 8, Appendix C4) estimates are handled differently for surveyed and unsurveyed spawning areas within the model. For surveyed areas multinomial logistic regression is used to allow stock composition estimates to trend through time. Because empirical stock composition data only exists for late in the time series (2013-2017) estimated changes in stock composition early in the time series represent changes in the relative magnitude of the single aerial survey counts. In this model changes in survey relative abundance are assumed to reflect changes in stock composition, although trends in relative observability could result in similar data. This assumption is supported by consistent survey procedures utilized throughout the time series. Among the surveyed streams within the Yentna River stock group Peters Creek has increased in relative abundance between 1979 and 2017 while Cache Creek has decreased in relative abundance and Lake Creek and Talachulitna River have remained stable. Lake Creek is the largest component of spawning abundance in recent years followed by Talachulitna River, Peters Creek and Cache Creek. The inverse dispersion for the Yentna River stock group is moderately large (D = `r CI(D4)`, Table 3) indicating trends in the relative magnitude of survey counts and radio telemetry data are fairly well explained by the multinomial logistic regression model with a calendar year covariate. Estimated stock composition and our empirical stock composition estimates are similar.
  
Because unsurveyed streams in the Yentna River stock group lack relative composition data early in the time series, no trend can be estimated. Unsurveyed streams comprise `r min(p4out)`-`r max(p4out)`% (Figure 8, Appendix C3) of the Yentna River stock group. Inverse dispersion is very large (B = `r CI(B4)`, Table 3) indicating low variability in the proportion of the Yentna River stock group which spawns within the 4 surveyed streams. Moderate variability was documented with empirical telemetry data.
  
The model estimated proportion of the escapement observed during single aerial surveys of Cache Creek `r CI(t10)`(Table 1) does not include annual variation which is sure to exist. In this model annual variability is included in the log-normal error term from the relationship between survey counts and estimated escapement eq. $\@ref(eq:as)$. There was very poor agreement between Cache Creek single aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Yentna River stock group.  The log-normal standard deviation for the Cache Creek aerial survey regression was `r CI(sa10)`, which is larger than the median value for the distribution of $\sigma_{AS}$ (`r CI(B)`).
  
The model estimated proportion of the escapement observed during single aerial surveys of Lake Creek `r CI(t11)`(Table 1) does not include annual variation which is sure to exist. There was very good agreement between Lake Creek single aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Yentna River stock group.  The log-normal standard deviation for the Lake Creek aerial survey regression was `r CI(sa11)`, which is smaller than the median value for the distribution of $\sigma_{AS}$.
  
The model estimated proportion of the escapement observed during single aerial surveys of Peters Creek `r CI(t12)`(Table 1) does not include annual variation which is sure to exist. There was very poor agreement between Peters Creek single aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Yentna River stock group.  The log-normal standard deviation for the Peters Creek aerial survey regression was `r CI(sa12)`, which is larger than the median value for the distribution of $\sigma_{AS}$.
  
The model estimated proportion of the escapement observed during single aerial surveys of the Talachulitna River `r CI(t13)`(Table 1) does not include annual variation which is sure to exist. There was average agreement between Talachulitna River single aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Yentna River stock group.  The log-normal standard deviation for the Talachulitna River aerial survey regression was `r CI(sa13)`, which similar to the median value for the distribution of $\sigma_{AS}$.
  
Total run estimates (Figure 19 second panel, Appendix B4) are marginally more precise than escapement estimates because of low harvest levels that were relatively well estimated. Coefficients of variation for total run are generally less than 0.20. Coefficients of variation for recruitment (Figure 14 middle panel) were generally moderate (< 30%) except at the beginning and end of the data series, when one or more age classes were missing.  Harvest rates for Yentna River Chinook salmon were below levels that would maximize yield but have been close to levels that would maximize recruitment in 1993 and 1994 (Figure 19 fourth panel).
  
Estimates of population parameters from the state-space model take the measurement errors in escapement S and recruitment R (Figure 20 error bars) into account. The individual data pairs are weighted depending upon the certainty with which the individual values of S and R are known. Because measurement error is substantial for many brood years, and due to other sources of uncertainty, Ricker SR relationships that could have plausibly generated the observed data are diverse (Figure 20: light lines), often deviating substantially from the median Ricker relationship (Figure 20: heavy dashed line).
  
Median productivity (recruits per spawner, in the absence of density effects) of Yentna River Chinook salmon during 1979–2014 has been moderate  ($\textrm{ln}(\alpha)$ = `r CI(lna4)` Table 5). There is a great deal of uncertainty about productivity, as evident in the extent to which the plausible SR relationships differ with respect to their slope at the origin (Figure 20). Similarly, uncertainty about $\beta$ is reflected in variability in the escapements leading to maximum recruitment $S_{MSR}$, and uncertainty about equilibrium abundance $S_{EQ}$ is reflected by variability in the in the escapements where the curves intersect the replacement line. There is moderate variation around the Ricker estimated mean ($\sigma_W$ = `r CI(sw4)`).
  
The Ricker recruitment residuals in Figure 19 (bottom panel) are deviations in recruitment of Yentna River Chinook salmon from that predicted by the Ricker SR relationship, reflecting time-varying changes in productivity after controlling for density-dependent effects. Yentna River Chinook had near average productivity through the 1997 brood year, mostly above average productivity between 1998 and 2002 and mostly below average productivity thereafter. Model residuals are positively correlated supporting the concept of time-varying productivity ($\phi$ = `r CI(phi4)`).

Sustained yield is the number of fish in the expected recruitment over and above that needed to replace the spawners. Escapement goals in Alaska are developed to maximize sustained yield by choosing a range of escapements around $S_{MSY}$, the theoretical number of spawners that will result in the largest difference between recruitment and replacement. Graphically, this is the escapement which maximizes the length of a vertical line drawn from the Ricker curve downward to the replacement line. Given the diversity of plausible SR relationships (Figure 20), it is important to choose an escapement goal that is robust to this uncertainty rather than one tailored solely to the median SR relationship. To address this uncertainty we tallied the success or failure of a given number of spawners to achieve biological reference points across plausible SR relationships.
  
Yentna River Chinook salmon escapement leading to maximum sustained yield $S_{MSY}$ was estimated to be `r CI(SMSY4)`. The optimal yield profiles in Figure 21 (top panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSY. These probabilities, which are highest near $S_{MSY}$ can be used to quantify the yield performance of prospective escapement goals (Figure 21 shaded areas), taking into consideration all of the uncertainty about the true abundance and productivity of the stock. The overfishing profiles (Figure 21 middle panel) show the probability that sustained yield would be reduced to less than 70%, 80%, or 90% of MSY by fishing too hard and supplying too few spawners. For this stock, these probabilities are nearly the exact complements of the probabilities in the left-hand limbs of the optimal yield profiles.
  
Expected sustained yield (number of fish over and above that necessary to replace the number of spawners, averaged over brood years 1979–2015) is also maximized at $S_{MSY}$ (Figure 21). Realized yield in any single year varies widely, return per spawner varied between between `r rs(4)$min` and `r rs(4)$max` for Yentna River Chinook salmon with `r rs(4)$n` of 36 complete brood years failing to replace themselves.
  
Fishery managers may want to evaluate existing and proposed goal ranges with respect the other indicators of fishery performance. In some sport fisheries run sizes and high catch rates are an important priority. Run size is associated with large recruitment. Escapement leading to maximum recruitment $S_{MSR}$ was estimated to be `r CI(SMSR4)`. Analogous to the optimum yield profiles discussed above optimum recruitment profiles tally the success or failure of a given number of spawners to maximize recruitment across plausible SR relationships. The optimal recruitment profiles in Figure 21 (bottom panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSR. Optimum Recruitment probabilities, which are highest near $S_{MSR}$, reach maximums at larger spawning abundances than optimum yield probabilities and decrease more slowly as spawning abundance increases.
  
Lake Creek, Peters Creek and Talachulitna River have existing goals based on single aerial survey data. Existing goals use 3 pieces of information (3 single aerial survey counts) to make 3 run size determinations without considering observability of each survey. This analysis leverages 4 pieces of information to make one run size determination while accounting for correlation in run sizes between the sub stocks and variability in survey observability.
  
Proposed escapement goals were determined by. The proposed escapement goal has a `r prob_p4[[1, "OYP80"]]`% probability of achieving 80% of MSY at the lower bound and a `r prob_p4[[2, "OYP80"]]`% probability of achieving MSY at the upper bound. With respect to recruitment, the proposed escapement goal has a `r prob_p4[[1, "ORP80"]]`% probability of achieving 80% of MSR at the lower bound and a `r prob_p4[[2, "ORP80"]]`% probability of achieving 80% of MSR at the upper bound.
  
##Other Areas
The fifth stock group in the Susitna River drainage is a catch all including the mainstem Susitna River and the most upstream spawning tributaries. Single aerial surveys are conducted on three spawning areas within this stock group. Unfortunately, there is no relationship between mark-recapture estimates and aerial survey counts for this area and reliable estimates of abundance cannot be generated.

##Age Composition
```{r echo=FALSE, include=FALSE}
carcass <- age[grepl("Escapement", age$location), ]
wheel <- age[!grepl("Escapement|creel|weir", age$location), ]
creel <- age[grepl("creel", age$location), ]
weir <- age[grepl("weir", age$location), ]

p1 <- digits(range(post$summary[grepl("p\\[\\d+,1\\]", rownames(post$summary)), "mean"])*100)
p2 <- digits(range(post$summary[grepl("p\\[\\d+,2\\]", rownames(post$summary)), "mean"])*100)
p3 <- digits(range(post$summary[grepl("p\\[\\d+,3\\]", rownames(post$summary)), "mean"])*100)
p4 <- digits(range(post$summary[grepl("p\\[\\d+,4\\]", rownames(post$summary)), "mean"])*100)
```
Chinook salmon age data from the Susitna River drainage is sparse given the geographic extent of the drainage. Most sampling occurred in upstream spawning areas that may not be representative of other spawning populations throughout the drainage. In addition, consistent sampling methods are not available through the time series, and some samples are likely biased. Carcass survey data is available from `r dim(carcass)[1]` datasets in the Susitna and Yentna drainages between `r min(carcass$year)` and `r max(carcass$year)`. Fishwheel data is available from `r dim(wheel)[1]` datasets in Susitna River drainage between `r min(wheel$year)` and `r max(wheel$year)`. Creel survey data is available from `r dim(creel)[1]` datasets from upstream areas in the Susitna and Yentna drainages between `r min(creel$year)` and `r max(creel$year)`. Finally, weir data is available from the Deshka River annually since `r min(weir$year[grepl("Deshka weir", weir$location)])` and Willow Creek between `r min(weir$year[grepl("Willow weir", weir$location)])` and `r max(weir$year[grepl("Willow weir", weir$location)])`.
  
Between `r min(intersect(creel$year, c(carcass$year, wheel$year)))` and `r max(intersect(creel$year, c(carcass$year, wheel$year)))` creel and fishwheel/carcass survey data exist annually, although from different populations of fish. Fishwheel/carcass survey samples contain larger proportions of age-3 and age-4 fish in paired annual samples (Figure 23, middle panel). Between `r min(intersect(creel$year, weir$year))` and `r max(intersect(creel$year, weir$year))` creel and weir data exist annually, although from different populations of fish. Creel survey samples contain larger proportions of age-6 fish in paired annual samples. Our model assumes weir age samples are an unbiased estimate of drainage wide age composition. When weir based age samples are unavailable estimated age composition is adjusted for sample type consistent with the patterns described above.
  
Chinook salmon in the Susitna River Drainage are composed of age-3 (1.1), age-4(1.2), age-5(1.3) and age-6 (1.4) fish (Figure 23 middle panel, Table 6). Throughout the time series age-5 fish have been the predominate age class while the relative abundance of age-6 fish has steadily decreased and the relative abundance of age-3 fish has increased (dramatically in recent years).
  
Susitna River Chinook salmon matured (Figure 23 top panel, Table 7) at age-3 (`r p1[1]`-`r p1[2]`%), age-4 (`r p2[1]`-`r p2[2]`%), age-5 (`r p3[1]`-`r p3[2]`%) and age-6 (`r p4[1]`-`r p4[2]`%). Age-at-maturity has tended toward increasing contributions of age-3 and age-5 fish and decreasing contributions of age-4 and age-6 fish. 
