---
output: 
  word_document:
    reference_docx: ".\\doc_styles\\word_styles_FDS.docx"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.cap = TRUE, fig.align = 'center')
library(SusitnaEG)
get_ids()
#post <- readRDS("..\\..\\posts\\SuChinook_8e162f9.rds")
post <- readRDS("C:\\postsC\\SuChinook_8e162f9.rds")
```

Appendix B1.- RJAGS code for the Susitna River Chinook salmon run reconstruction and rscapement goal analysis.  
```{r code = readLines("..\\..\\models\\mod_SuChin.R"), echo = T, eval = F}
```

Table: Appendix C1.- Annual abundance estimates for the Deshka River Chinook salmon stock group obtained by fitting a state-space model to data from 1979 to 2017.
```{r}
tab_state <- table_state(post, "bystock")
knitr::kable(tab_state[[1]][-2], row.names = FALSE, align = "r", escape = FALSE)
```
  
*Note*: Point estimates are posterior medians, CVs are posterior standard deviations divided by posterior means.  Recruitment values are listed by brood year.
  
Table: Appendix C2.- Annual abundance estimates for the Eastside Susitna Chinook salmon stock group obtained by fitting a state-space model to data from 1979 to 2017.  
```{r}
knitr::kable(tab_state[[2]][-2], row.names = FALSE, align = "r", escape = FALSE)
```
  
*Note*: Point estimates are posterior medians, CVs are posterior standard deviations divided by posterior means.  Recruitment values are listed by brood year.
  
Table: Appendix C3.- Annual abundance estimates for the Talkeetna River Chinook salmon stock group obtained by fitting a state-space model to data from 1979 to 2017.  
```{r}
knitr::kable(tab_state[[3]][-2], row.names = FALSE, align = "r", escape = FALSE)
```
  
*Note*: Point estimates are posterior medians, CVs are posterior standard deviations divided by posterior means.  Recruitment values are listed by brood year.
  
Table: Appendix C4.- Annual abundance estimates for Yentna River Chinook salmon obtained by fitting a state-space model to data from 1979-2017.  
```{r}
knitr::kable(tab_state[[4]][-2], row.names = FALSE, align = "r", escape = FALSE)
```
  
*Note*: Point estimates are posterior medians, CVs are posterior standard deviations divided by posterior means.  Recruitment values are listed by brood year.
  
Table: Appendix D1.- Annual stock composition estimates for the Eastside Susitna Chinook salmon stock group obtained by fitting a state-space model to data from 1979 to 2017.  
```{r}
tab_stock <- table_stock(post)
knitr::kable(tab_stock[[1]], row.names = FALSE, align = "r", escape = FALSE)
```
  
*Note*: Point estimates are posterior means with posterior standard deviations in parentheses.
  
Table: Appendix D2.- Annual stock composition estimates for the Talkeetna River Chinook salmon stock group obtained by fitting a state-space model to data from 1979 to 2017.  
```{r}
knitr::kable(tab_stock[[2]], row.names = FALSE, align = "r", escape = FALSE)
```
  
*Note*: Point estimates are posterior means with posterior standard deviations in parentheses.
 
Table: Appendix D3.- Annual stock composition estimates for the Yentna River Chinook salmon stock group obtained by fitting a state-space model to data from 1979 to 2017. 
```{r}
knitr::kable(tab_stock[[3]], row.names = FALSE, align = "r", escape = FALSE)
```
  
*Note*: Point estimates are posterior means with posterior standard deviations in parentheses.
 