---
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.cap = TRUE, fig.align = 'center')
library(SusitnaEG)
get_ids()
post <- readRDS("..\\..\\posts\\SuChinook_a02eb71a.rds")
```


Table 1.- Aerial Survey observability and lognormal standard deviation with 95% confidence interval for each surveyed spawning area tributary in the Susitna River drainage.
```{r}
table_airerror(post)
``` 

Table 2.- State-space model parameter estimates for Deshka River Chinook salmon, calendar years 1979-2017. Posterior medians are point estimates while 95% credibility intervals are shown in parentheses. Parameter definitions are in the Methods section. 
```{r}
table_params(post, 1)
```

Table 3.- State-space model parameter estimates for East Susitna Chinook salmon, calendar years 1979-2017. Posterior medians are point estimates while 95% credibility intervals are shown in parentheses. Parameter definitions are in the Methods section. 
```{r}
table_params(post, 2)
```

Table 4.- State-space model parameter estimates for Talkeetna River Chinook salmon, calendar years 1979-2017. Posterior medians are point estimates while 95% credibility intervals are shown in parentheses. Parameter definitions are in the Methods section. 
```{r}
table_params(post, 3)
```

Table 5.- State-space model parameter estimates for Yentna River Chinook salmon, calendar years 1979-2017. Posterior medians are point estimates while 95% credibility intervals are shown in parentheses. Parameter definitions are in the Methods section. 
```{r}
table_params(post, 4)
```

Table 6.- Age composition estimates obtained by fitting a state-space model to data from Susitna River Chinook salmon, calendar years 1979-2017.
```{r}
table_age(post, "q")
```

Table 7.- Age-at-maturity estimates obtained by fitting a state-space model to data from Susitna River Chinook salmon, brood years 1973-2014.
```{r}
table_age(post, "p")
```
