---
title: "SusitnaEG analysis"
author: "Adam Reimer"
date: "September 4, 2018"
output: 
  bookdown::word_document2:
#    pandoc_args: ["-Fpandoc-crossref"]
    reference_docx: ".\\doc_styles\\word_styles_FDS.docx"
---

```{r setup, echo=FALSE, include=FALSE}
library(bookdown)
knitr::opts_chunk$set(echo = TRUE)
library(SusitnaEG)
post <- readRDS("..\\..\\posts\\SuChinook_134cf92.rds")
get_ids()
goals_list <- list(Deshka = c(9000, 18000),
                   Eastside = c(13000, 25000),
                   Talkeetna = c(9000, 17500),
                   Yentna = c(13000, 22000))
```
## State-Space Model
A state-space model (Appendix B1) was developed to generate annual abundance estimates for Susitna River Chinook salmon stocks and fit spawner-recruitment (S-R) relationships for use in developing escapement goal recommendations based on maximum sustained yield. State-space models contain 2 components: process equations and observation equations. Process equations describe population dynamics that are unobserved but of research interest. In this application we focus on spawning escapements, recruitment from those escapements, and parameters that describe the S-R relationship. Observation equations describe how observed data are generated conditional on population parameters estimated by the process equations. We lack a robust time series of observed abundance and instead model the relationship between abundance and aerial survey data to reconstruct historical abundances while incorporating the uncertainty in historical abundance estimates into the S-R parameter estimates.   
  
Many parameters are estimated in this state-space model. Parameters with similar function or interpretation often use the same symbol, distinguished by a subscript capital letter. Subscript lower-case letters denote parameter indices. For example, all harvest rates use the symbol $\mu$ where $\mu_{By}$ is the harvest rate below (downstream of) both Susitna RM 34 and Yentna RM 6 in year $y$, and $\mu_{Ays}$ is the harvest rate of stock $s$ above either Susitna RM 34 or Yentna RM 6 in year $y$. Year indices $y$ range from 1 to 39 representing 1979 to 2017, respectively. Age indices $a$ range from 3 to 6, representing total age of Chinook salmon, where $a=6$ represents fish with a total age of 6 or larger. Stock indices $s$ range from 1 to 4, representing the Deshka River, Eastside Susitna, Talkeetna River, and Yentna River stocks, respectively (Figure 2). Some data and parameters are nested within stocks. When this occurs the stock index is moved into the object name and one such object exists for each stock. For example, radio telemetry data vectors are called $\mathbf{r.s}$ for stock $s$ and each vector is a different length depending on the number of populations that compose the stock $s$.
  
### Process Component
Abundance of Susitna River Chinook salmon for each stock is generated by a S-R relationship that describes the number of fish expected to return (the “recruitment”) from a given number of spawning fish (the “escapement”). The total recruitment $R_{cs}$ produced from fish spawning in brood year $c$ by stock $s$ follows the Ricker (1975) formulation:
  
\begin{equation}
R_{cs}~=~S_{cs}\alpha_s exp(-\beta_s S_{cs}) (\#eq:ricker)
\end{equation}
  
where $S_{cs}$ is the number of spawners, $\alpha_s$ (number of recruits per spawner in the absence of density dependence) is a measure of productivity for each stock, and $\beta_s$ is a measure of density dependence for each stock.

Productivity varies among brood years, fluctuating around a central tendency. Time-varying productivity often manifests as serially correlated model residuals, so a lognormal error term with a lag of 1 year was included in the linearized form of the S-R relationship (Noakes et al. 1987).
  
\begin{equation}
ln(R_{cs})~=~ln(S_{cs})+ln(\alpha_s)-\beta_s S_{cs} +\phi_s \nu_{(c-1)s}+\epsilon_{Ws} (\#eq:rickerar)
\end{equation}
  
where $\phi_s$ is the lag-1 serial correlation coefficient, $\nu_{cs}$ are model residuals defined as
  
\begin{equation}
\nu_{cs}~=~ln(R_{cs})-ln(S_{cs})-ln(\alpha_s)+\beta_s S_{cs} (\#eq:residuals)
\end{equation}
  
and the $\epsilon_{Ws}$ are independently and normally distributed process errors with “white noise” variance $\sigma^2_{Ws}$. The productivity parameters for each stock are drawn from a common distribution, $\textrm{ln}(\alpha_s)~\sim~\textrm{Normal}(\mu_{ln\alpha}, \sigma^2_{ln\alpha})$.  
  
Age at maturity, which is needed to distribute recruitment across calendar years, is allowed to trend through time and fluctuate annually. Age-at-maturity vectors^[These proportions are maturity and survival schedules for a given brood year (cohort) across calendar years. In contrast, Equation \@ref(eq:qstar) describes age proportions of returning fish in a given calendar year across brood years.] $\mathbf{p_c} = (\begin{array}{am} p_{c3} & p_{c4} & p_{c5} & p_{c6} \end{array})$ from brood year $c$ returning at ages 3--6 were drawn from a $\textrm{Dirichlet}(\gamma_{c3}, \gamma_{c4},  \gamma_{c5}, \gamma_{c6})$ distribution. The sum of the Dirichlet parameters is the (inverse) dispersion^[A low value of $D$ is reflective of a large amount of variability in age-at-maturity proportions $\mathbf{p_c}$ among brood years, whereas a high value of $D$ indicates more consistency in $\mathbf{p_c}$ over time.] of the age-at-maturity vectors, reflecting consistency of $\mathbf{p_c}$ among brood years:
  
\begin{equation}
D_{age}~=~\sum_{a=3}^6 \gamma_{ca}~~\textrm{for all}~c (\#eq:Dage)
\end{equation}
  
The location parameters
  
\begin{equation}
\pi_{ca}~=~\frac{\gamma_{ca}}{D_{age}}~=~\frac{exp(ML1_a+ML2_ac)}{\sum_{a=3}^6 exp(ML1_a+ML2_ac)} (\#eq:pi)
\end{equation}
  
are proportions that sum to 1 for each brood year where the age-at-maturity central tendency can trend with brood year through the multinomial logistic regression coefficients $ML1_a$ and $ML2_a$.
  
The abundance $N_{yas}$ in stock $s$ of age $a$ Chinook salmon in calendar year $y$ is the product of the age at maturity scalar $p_{ca}$ and the total return (recruitment) $R_{cs}$ for stock $s$ from brood year $c=y−a$:
  
\begin{equation}
N_{yas}~=~p_{(y-a)a}R_{(y-a)s} (\#eq:Ntas)
\end{equation}
  
Total run $N_{ys}$ for stock $s$ during calendar year $y$ is the sum of abundance at age across all ages:
  
\begin{equation}
N_{ys}~=~\sum_{a=3}^6 N_{yas} (\#eq:Nts)
\end{equation}
  
Annual harvest of Susitna-origin Chinook salmon below (downstream of) both Susitna RM 34 and Yentna RM 6, $H_{By}$, was modeled as the product of the annual harvest rate in the downstream area $\mu_{By}$, and total run $N_y$:
  
\begin{equation}
H_{By}~=~\mu_{By}\sum_{s=1}^4 N_{ys} (\#eq:Hbelow)
\end{equation}
  
Inriver run $IR_{ys}$ of stock $s$ during calendar year $y$ at either Susitna RM 34 or Yentna RM 6 was modeled as the product of stock-specific total run $N_{ys}$ and the annual survival rate in the area downstream:
  
\begin{equation}
IR_{ys}~=~N_{ys}(1-\mu_{By}) (\#eq:IR)
\end{equation}
  
Annual harvest of stock $s$ above either Susitna RM 34 or Yentna RM 6, $H_{Ays}$, was the product of the annual harvest rate for each stock in the upstream area $\mu_{Ays}$ and the inriver run of stock $s$:
  
\begin{equation}
H_{Ays}~=~\mu_{Ays}IR_{ys} (\#eq:Habove)
\end{equation}
  
Annual harvest of Deshka River Chinook salmon ($s$ = 1) upstream of the Deshka River weir, $H_{DESHKAy}$, was a proportion $p_{DESHKAy}$ of the total inriver harvest of Deshka River Chinook salmon $H_{Ay1}$:
  
\begin{equation}
H_{DESHKAy}~=~p_{DESHKAy}H_{Ay1} (\#eq:Hdeshka)
\end{equation}
  
The $p_{DESHKAy}$ are drawn from a $\textrm{Beta}(b1_D, b2_D)$ distribution. The beta parameters are expressed in an alternate form where $B_D~=~b1_D+b2_D$ is the (inverse) dispersion and the location is drawn from a noninformative beta prior.
  
Spawning escapement $S_{ys}$ was inriver run abundance minus harvest above Susitna RM 34 or Yentna RM 6:
  
\begin{equation}
S_{ys}~=~IR_{ys}-H_{Ays} (\#eq:S)
\end{equation}
  
Finally, Chinook salmon passage at the Deshka River weir was the sum of the spawning escapement in the Deshka River, $S_{y1}$, and harvest upstream of the weir:   
\begin{equation}
IR_{DESy}~=~S_{y1}+H_{DESy} (\#eq:dweir)
\end{equation}
  
Multiple populations ($p=1,2,\dots,P_s$) contribute to the spawning escapement in the Eastside Susitna, Talkeetna, and Yentna stocks. The relative composition of spawning populations within each stock is of interest because some observed data is germane to the population scale. Composition of the $P_s-1$ populations within stock $s$ that are monitored^[Populations not monitored by aerial survey are grouped, hence $P_s-1$ populations are monitored.] by aerial survey are allowed to fluctuate annually around a trending central tendency. A set of equations analogous to Equations \@ref(eq:Dage) and \@ref(eq:pi) were used to define stock composition vectors $\mathbf{\rho.s^*}_y = (\begin{array}{} \rho.s^*_{y1} & \rho.s^*_{y2 } & \dots & \rho.s^*_{y(P_s-1)}\end{array})$ for the surveyed populations in each stock $s$. The composition vectors $\mathbf{\rho.s^*}_y$ are therefore allowed to fluctuate annually and trend through time, the (inverse) dispersion of the annual stock composition vectors being represented by $D.s_{COMP}$.
  
The annual proportion of fish from stock $s$ that spawned in populations not monitored by aerial survey, $\rho.s\prime_{y}$, are drawn from a $\textrm{Beta}(b1.s, b2.s)$ distribution. The beta parameters are expressed in an alternate form where $B.s_{SURVEY}~=~b1.s+b2.s$ is the (inverse) dispersion and the location is drawn from a non-informative beta prior.
  
Stock composition was calculated as follows:
        
\begin{equation}
\mathbf{\rho.s_y}~=~\left[\begin{array}{} \rho.s^*_{y1}(1-\rho.s\prime_{y}) & \rho.s^*_{y2}(1-\rho.s\prime_{y}) & \dots & \rho.s^*_{y(P_s-1)}(1-\rho.s\prime_{y}) &  \rho.s\prime_{y} \end{array}\right] (\#eq:pcomp)
\end{equation}
      
### Observation Component
Observed data (Appendices A1--A10) include mark--recapture estimates of inriver run, estimates of annual marine commercial and subsistence harvests below both Susitna RM 34 and Yentna RM 6, freshwater sport harvests above Susitna RM 34 or Yentna RM 6 and freshwater sport harvest above the Deshka weir, radiotelemetry data, aerial survey data for `r sum(sapply(as, function(x){dim(x)[2]}))` populations, weir counts for `r dim(weir)[2]` populations, age composition data from throughout the Susitna River drainage, and length composition data from the Deshka weir. Sampling distributions for the observed data are given below.
  
#### Inriver Run and Length Composition
Estimated annual inriver runs of Chinook salmon for stock $s$, $\widehat{IR}_{500ys}$, from mark--recapture data were
  
\begin{equation}
\widehat{IR}_{500ys}~=~IR_{500ys}exp(\epsilon_{IR500ys}) (\#eq:IRhat)
\end{equation}
  
where $IR_{500ys}$ is the inriver run of fish 500 mm mid eye to tail fork (METF) length or larger, $\epsilon_{IR500ys}~\sim~\textrm{Normal}(0, \sigma^2_{IR500ys})$, and $\sigma^2_{IR500ys}$ is calculated from the coefficient of variation (CV) of $\widehat{IR}_{500ys}$:
  
\begin{equation}
\sigma^2_{IR_{500ys}}~=~\textrm{ln}(\textrm{CV}(\widehat{IR}_{500ys})^2+1) (\#eq:cvIR)
\end{equation}
  
The number of age $a$ (where $a=3,4$) fish that were less than 500 mm METF in year $y$, $x_{lt500ya}$, was
  
\begin{equation}
x_{lt500ya}~\sim~\textrm{Binomial}(p_{lt500ya}, n_{ya}) (\#eq:xsmall)
\end{equation}
  
where $n_{ya}$ is the  total number of fish sampled for age and length in age class $a$ during year $y$ and $p_{lt500ya}$ is the proportion of fish less than 500 mm METF in age class $a$ (3 or 4) during year $y$.
  
Inriver runs of fish 500 mm METF or greater, $IR_{500ys}$, were
  
\begin{equation}
IR_{500ys}~=~IR_{ys}[1-(q_{y3}p_{lt500y3}+q_{y4}p_{lt500y4})] (\#eq:IRlarge)
\end{equation}
  
where $q_{ya}$ is the proportion of the run that is age $a$ in calendar year $y$.
  
#### Harvest
Estimated annual harvest of Susitna River Chinook salmon below both Susitna RM 34 and Yentna RM 6, $\widehat{H}_{By}$, was
  
\begin{equation}
\widehat{H}_{By}~=~H_{By}exp(\epsilon_{HBy}) (\#eq:HBhat)
\end{equation}
  
where the $\epsilon_{HBy}~\sim~\textrm{Normal}(0, \sigma^2_{HBy})$ and the variances followed Equation \@ref(eq:cvIR). Estimated annual harvest of Susitna River Chinook salmon above either Susitna RM 34 or Yentna RM 6, $\widehat{H}_{Ays}$ for stock $s$, was modeled according to Equation \@ref(eq:HBhat) after substituting ${H}_{Ays}$ and $\epsilon_{HAys}$ for ${H}_{By}$ and $\epsilon_{HBy}$, respectively, where the $\epsilon_{HAys}~\sim~\textrm{Normal}(0, \sigma^2_{HAys})$ and the variances followed Equation \@ref(eq:cvIR). Similarly, estimated annual harvest of Deshka River Chinook salmon upstream of the Deshka weir, $\widehat{H}_{DESy}$, was generated according to Equation \@ref(eq:HBhat) after substituting ${H}_{DESHKAy}$ and $\epsilon_{H_{DESHKA}y}$ for ${H}_{By}$ and $\epsilon_{HBy}$, respectively, where the $\epsilon_{H_{DESHKA}y}~\sim~\textrm{Normal}(0, \sigma^2_{H_{DESHKA}y})$ and the variances followed Equation \@ref(eq:cvIR).
  
#### Radiotelemetry
Radio telemetry data (counts of radiotagged fish) within each stock, where $\mathbf{r.s}_{y} = (\begin{array}{} r.s_{y1} & r.s_{y2} & \dots & r.s_{yP_s} \end{array})$, were partitioned into $P_s$ categories with $P_s-1$ categories representing populations that are counted during aerial surveys and 1 category ($P_s$) representing Chinook salmon belonging to stock $s$ but not belonging to the $P_s-1$ populations monitored by aerial survey. The number of radio tags from populations that were not counted during aerial surveys was
    
\begin{equation}
r.s_{yP_s}~\sim~\textrm{Binomial}\left(\rho.s\prime_y, \sum_{p=1}^{P_s} r.s_{yp}\right) (\#eq:nosurvey)
\end{equation}
  
The number of radio tags belonging to populations that were counted during aerial surveys, $r.s_{y[p=1:(P_s-1)]}$, was as follows:
  
\begin{equation}
r.s_{y[p=1:(P_s-1)]}~\sim~\textrm{Multinomial}\left(\rho.s^*_{y[p=1:(P_s-1)]}, \sum_p^{P_s-1} r.s_{yp}\right) (\#eq:survey)
\end{equation}
  
where $\rho.s^*_{yp}$ estimates the annual proportion of radiotagged fish from surveyed population $p$ within stock $s$.
  
#### Abundance Indices
Annual aerial survey counts of population $p$ within stock $s$, $a.s_{yp}$, are related to stock $s$ abundance $S_{ys}$ after accounting for survey observability $\theta_i$ and stock composition $\rho.s_{yp}$:
  
\begin{equation}
a.s_{yp}~=~\theta_{i(s,p)}\rho.s_{yp}S_{ys}exp(\epsilon_{ASi(s,p)}) (\#eq:as)
\end{equation}
    
where $\epsilon_{ASi}~\sim~\textrm{Normal}(0, \sigma^2_{ASi})$. A total of `r sum(sapply(as, function(x){dim(x)[2]}))` populations were monitored by aerial survey and $i(s,p)$ is a function that maps stock and population indices to an index $i$ = 1:`r sum(sapply(as, function(x){dim(x)[2]}))` allowing hierarchical treatment of survey observability and survey error. Thus, the proportion of the spawning escapement counted during aerial surveys $\theta_i$ was $\textrm{logit}(\theta_i)~\sim~\textrm{Normal}(\mu_\theta, \sigma^2_\theta)$.

Survey-specific residual standard deviations were $\sigma_{ASi}~\sim~\textrm{half_Cauchy}(0, C_{AS})$ where $C_{AS}$ is the median of the distribution of $\sigma_{ASi}$ (Lunn et al. 2013). Because modeled observability of spawning Chinook salmon $\theta_i$ is treated as constant through time, the annual variability in observability is confounded with annual variability in stock composition, $\rho.s_{yp}$. Also note that stock composition was only observed late in the time series (2012--2017) and modeled trends in stock composition in early years result from changes in the relative magnitude of aerial survey counts. Thus, the relative magnitude of survey counts is assumed to reflect stock composition^[While trending stock-specific observability could result in similar data we believe consistent survey procedures utilized throughout the time series make this possibility less likely.].  

Weirs counts were available for `r dim(weir)[2]` of the populations. Each weir count is related to the abundance of the stock where it was located after accounting for stock composition $\rho.s_{yp}$:
   
\begin{equation}
  w.s_{yp} = \begin{cases} IR_{DESHKAy}exp(\epsilon_{w}), & \mbox{if } s\mbox{ = 1} \\ 
  \rho.s_{yp}S_{ys}exp(\epsilon_{w}), & \mbox{if } s\ne\mbox{1} 
  \end{cases} (\#eq:weir) 
\end{equation}
   
where the $\epsilon_{w}~\sim~\textrm{Normal}(0, \sigma_{w}^2)$ and the variances followed Equation \@ref(eq:cvIR) with an assumed CV of 0.05 reflecting good precision associated with weir counts.
  
#### Age Composition
A total of `r dim(post$data$x.a)[1]` age composition datasets were collected from stock-specific locations between `r min(year_id)` and `r max(year_id)`. The Deshka River stock is represented throughout the time series, but most other stocks are represented only early in the time series (Figure 3). We deemed this resolution insufficient to model age composition independently for each stock and focused on modeling the age composition of the run to the entire Susitna River drainage. The model assumes fish were harvested in proportion to their abundance (by age and by stock), though this assumption is likely not critical because harvest rates are small. Age composition may differ between stocks, and multinomial logistic regression was used to include a correction for the stock that was sampled when estimating annual age composition for the entire drainage. Thus, age counts $x_{ja}$ were modeled as multinomially distributed
  
\begin{equation}
x_{j[a=3:6]}~=~\textrm{Multinomial}\left(q^*_{j[a=3:6]}, \sum_{a=3}^6 x_{ja}\right) (\#eq:xage)
\end{equation}
  
where $j$ = 1:`r dim(post$data$x.a)[1]`. The location parameters were
    
\begin{equation}
q^*_{ja}~=~\frac{exp\left[\textrm{ln}\left(\frac{N_{y(j)a}}{N_{y(j)(a=3)}}\right)+b_{s(j)a}\right]}{\sum_{a=3}^6 exp\left[\textrm{ln}\left(\frac{N_{y(j)a}}{N_{y(j)(a=3)}}\right)+b_{s(j)a}\right]} (\#eq:qstar)
\end{equation}
    
where $y(j)$ is a function that maps the row index $j$ to the year $y$ in which the data were collected. Hence, $N_{y(12)}$ is the abundance during the year in which the 12th age composition dataset was collected. Similarly, $s(j)$ is a function that maps the row index $j$ to the stock $s$ from which the data were collected. Equation \@ref(eq:qstar) represents a multinomial logistic regression where the intercept is a function of annual abundance of all 4 stocks in each age class and the categorical covariates $b_{sa}$ account for age composition differences between the stocks. The categorical covariates were parameterized with a sum to zero constraint. Because $\sum_s b_{sa}=0$, the quantity
  
\begin{equation}
q_{ya}~=~\frac{N_{ya}}{\sum_{a=3}^6 N_{y}} (\#eq:q)
\end{equation}
  
estimates age composition for the entire Susitna River Chinook salmon run.

## Model Fitting
Bayesian statistical methods employ the language of probability to quantify uncertainty about model parameters. Knowledge existing about the parameters outside the framework of this analysis is reflected in the “prior” probability distribution. The output of the Bayesian analysis is called the “posterior” probability distribution, which is a synthesis of the prior information and the information contained in the data. This methodology allows for inclusion of the effects of measurement error, serially-correlated productivity, and missing data into the analysis and provides a more realistic assessment of uncertainty than is possible with classical statistical methods. By properly specifying process variation, measurement error, and time-dependent linkage in the model, biases in the estimates can be reduced (Su and Peterman 2012). Model fitting involves finding the values of the population parameters of the model that could have plausibly resulted in the observed data. To do so, Markov Chain Monte Carlo (MCMC) methods were employed using the package RJAGS (Plummer 2013) within R (R Core Team 2016). See Fleischman et al. (2013) and Staton et al. (2016) for similar applications of the methods used in this report.
  
### Prior Distributions
Noninformative priors (chosen to have minimal effect on the posterior) were used for most parameters. Initial recruitments $R_{1973}-R_{1978}$ (those lacking linked spawner abundance) were modeled as drawn from a common lognormal distribution with median $\mu_{lnR}$ and variance $\sigma^2_{lnR}$. Truncated normal priors with mean zero, very large variances, and constrained to be positive were used for $\mu_{ln\alpha}$, $\beta$, and $\mu_{lnR}$. Initial model residuals $\nu_s$ were given a truncated normal prior with mean zero and variance $\sigma^2_{Ws}/(1-\phi^2_s)$ between --3 and +3. Annual harvest rates $\mu_{By},~\mu_{Ays}$ were given $\textrm{beta}(0.5,0.5)$ priors. Diffuse conjugate inverse gamma priors were used for $\sigma^2_{Ws}$ and $\sigma^2_{lnR}$. In some cases, the prior support was limited within a range that did not truncate the eventual posterior to aid in convergence. For example, Dirichlet dispersion parameters for age, stock, and harvest compositions use a $\textrm{Uniform}(0.07,1)$ prior on the $1/\sqrt{D}$ scale where the lower bound aids convergence by constraining the posterior densities for $D$ to realistic Dirichlet parameter sums. The prior on $C_{AS}$ was also $\textrm{Uniform}(0,1)$ but while $C_{AS}$ could exceed 1, the limited prior support did not truncate the posterior. A weakly informative conjugate inverse gamma prior [$\textrm{gamma}(2,1)$] was used for $\sigma^2_{ln\alpha}$ which also aided convergence while minimally affecting the posterior. 
  
### Sampling from the Posterior Distribution
MCMC samples were drawn from the joint posterior probability distribution of all unknowns in the model. The model was initiated with `r post$mcmc.info$n.chains` chains and `r format(post$mcmc.info$n.iter, big.mark = ",", scientific = 100)` samples were generated per chain. The first `r format(post$mcmc.info$n.burnin, big.mark = ",", scientific = 100)` samples from each chain were discarded and the remaining samples were thinned by a factor of `r post$mcmc.info$n.thin`, resulting in `r format(post$mcmc.info$n.samples, big.mark = ",", scientific = 100)` samples that were used to estimate the marginal posterior means, standard deviations, and percentiles. The diagnostic tool ShinySTAN (Stan Development Team 2016) was used to assess mixing and convergence, and no major problems were encountered. Interval estimates were constructed from the percentiles of the posterior distribution.

## Reference Points and Optimal Yield Profiles
Reference points were calculated from S-R parameter estimates for each individual MCMC sample. Sustained yield is the number of fish in the expected recruitment over and above that needed to replace the spawners. Spawning abundance providing MSY, $S_{MSY}$, which is the theoretical number of spawners that will result in the largest difference between recruitment and replacement, was approximated as follows:
  
\begin{equation}
S_{MSYs}~\cong~\frac{\textrm{ln}(\alpha\prime_s)}{\beta_s}[0.5-0.07\textrm{ln}(\alpha\prime_s)] (\#eq:SMSY)
\end{equation}
  
The quantity
  
\begin{equation}
\textrm{ln}(\alpha\prime_s)~=~\textrm{ln}(\alpha_s)+\frac{\sigma^2_{Ws}}{2(1-\phi_s^2)} (\#eq:alphaprime)
\end{equation}
  
in Equation \@ref(eq:SMSY) adjusts for the difference between the median and the mean of a right-skewed lognormal error distribution with autocorrelation.
  
Sustained yield at a specified escapement $Y(S)$ was obtained by subtracting spawning escapement from recruitment:
  
\begin{equation}
Y(S)_s~=~R_s-S~=~Sexp(\textrm{ln}(\alpha\prime_s)-\beta_s S)-S (\#eq:Ys)
\end{equation}
  
The harvest rate leading to maximum sustained yield, is approximated by (Hilborn 1985):
  
\begin{equation}
U_{MSYs}~\cong~\textrm{ln}(\alpha\prime_s)[0.5-0.07\textrm{ln}(\alpha\prime_s)] (\#eq:UMSY)
\end{equation}
  
Fishery managers may want to evaluate existing and proposed goal ranges with respect to other indicators of fishery performance. The escapement leading to maximum sustained recruitment (MSR) is as follows:
  
\begin{equation}
S_{MSRs}~=~\frac{1}{\beta_s} (\#eq:SMSR)
\end{equation}
  
Equilibrium spawning abundance, where recruitment exactly replaces spawners is
  
\begin{equation}
S_{EQs}~=~\frac{\textrm{ln}(\alpha\prime_s)}{\beta_s} (\#eq:SEQ)
\end{equation}
  
For each stock, the probability that a given spawning escapement $S$ would produce an average yield $Y(S)$ exceeding X% of MSY was obtained by calculating $Y(S)$ at incremental values of $S$ for each MCMC sample, then comparing $Y(S)$ with X% of the value of MSY for that sample. The proportion of samples in which $Y(S)$ exceeds X% of MSY is an estimate of the desired probability, and the plot of this proportion versus $S$ is termed an optimal yield profile (OYP; Fleischman et al. 2013).

The probability that yield would be reduced to less than X% of MSY by supplying too few spawners $S$ was obtained by calculating $Y(S)$ at incremental values of $S$ and tallying the number of MCMC samples for which $Y(S)$ was less than X% of MSY and $S$ was less than $S_{MSY}$. A plot of the fraction of samples in which this condition occurred versus $S$ is termed an overfishing profile (Bernard and Jones III 2010).

The probability that a given spawning escapement $S$ would produce average recruitment $R$ exceeding X% of MSR was obtained by calculating $R$ from Equation \@ref(eq:ricker) at incremental values of $S$ for each MCMC sample, then comparing $R$ with X% of the value of MSR for that sample. The proportion of samples in which $R$ exceeded X% of MSR is an estimate of the desired probability, and the plot of this proportion versus $S$ is termed an optimal recruitment profile (ORP; Fleischman et al. 2013).

OYPs, overfishing profiles, and ORPs were used to quantify the yield (or recruitment) performance of prospective escapement goals, taking into consideration the uncertainty about the true abundance, productivity, and capacity of the stock.

## Escapement Goals Standardized to $S_{MSY}$
To compare escapement goals from this study to goals for other Alaska stocks, we divided the lower and upper bounds of `r dim(chinBEGs)[1]` published goals for Alaska Chinook salmon (Munro 2019) by point estimates of $S_{MSY}$ associated with each goal range, thereby expressing all goal ranges in terms of multiples of $S_{MSY}$. These values were multiplied by estimates of $S_{MSY}$ presented in this report to provide a graphical comparison of the recommended goals with exisitng goals for Alaskan Chinook salmon.

## Escapement Goal Review Process
An interdivisional escapement goal review team was convened to review the available data, discuss analyses and results, and make escapement goal recommendations. The escapement goals recommended in this report are the product of several collaborative meetings of the review team and other ADF&G staff. The final recommendation was reached by consensus.

# Results
## Deshka River Stock
```{r echo=FALSE, include=FALSE}
digits <-
  function(p){
    ps <- ifelse(p < 0.01, format(p, TRUE, digits = 2, scientific = TRUE),
                 ifelse(p < 2, format(round(p, 2), TRUE, nsmall = 2),
                        ifelse(p < 100, format(round(p, 1), TRUE, nsmall = 1),
                               format(round(p, 0), TRUE, nsmall = 0, width = 5, scientific = FALSE, big.mark = ","))))
  return(ps)
}

S <- 
  post$summary[grepl("S\\[\\d+,\\d\\]", rownames(post$summary)),] %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column() %>%
  dplyr::rename(q50 = '50%') %>% 
  dplyr::mutate(stock = as.numeric(gsub("S\\[\\d+,(\\d)\\]", "\\1", rowname)),
                year = year_id[as.numeric(gsub("S\\[(\\d+),\\d\\]", "\\1", rowname))],
                cv = sd / mean) %>%
 dplyr::select(rowname, stock, year, q50, cv)
IR <- 
  post$summary[grepl("IR\\[\\d+,\\d\\]", rownames(post$summary)),] %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column() %>%
  dplyr::rename(q50 = '50%') %>%
  dplyr::mutate(stock = as.numeric(gsub("IR\\[\\d+,(\\d)\\]", "\\1", rowname)),
                year = year_id[as.numeric(gsub("IR\\[(\\d+),\\d\\]", "\\1", rowname))],
                cv = sd / mean) %>%
 dplyr::select(rowname, stock, year, q50, cv)
N <- 
  post$summary[grepl("N\\[\\d+,\\d\\]", rownames(post$summary)),] %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column() %>%
  dplyr::rename(q50 = '50%') %>%
  dplyr::mutate(stock = as.numeric(gsub("N\\[\\d+,(\\d)\\]", "\\1", rowname)),
                year = year_id[as.numeric(gsub("N\\[(\\d+),\\d\\]", "\\1", rowname))],
                cv = sd / mean) %>%
 dplyr::select(rowname, stock, year, q50, cv)
R <- 
  post$summary[grepl("R\\[\\d+,\\d\\]", rownames(post$summary)),] %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column() %>%
  dplyr::rename(q50 = '50%') %>%
  dplyr::mutate(stock = as.numeric(gsub("R\\[\\d+,(\\d)\\]", "\\1", rowname)),
                yr = as.numeric(gsub("R\\[(\\d+),\\d\\]", "\\1", rowname)),
                cv = sd / mean) %>%
  dplyr::filter(yr %in% 7:39) %>%
 dplyr::select(rowname, stock, yr, q50, cv)
minrow <- function(dat, n){
  dat %>% 
    dplyr::filter(stock == n) %>% 
    dplyr::slice(which.min(q50)) %>%
    dplyr::mutate(median = digits(q50))}
  
maxrow <- function(dat, n){
  dat %>% 
    dplyr::filter(stock == n) %>% 
    dplyr::slice(which.max(q50)) %>%
    dplyr::mutate(median = digits(q50))}
maxrow(N, 1)

NIR1cv94 <- digits(range(c(IR[IR$year %in% year_id[1:which(year_id == "1994")] & IR$stock == 1, ]$cv, 
                          N[N$year %in% year_id[1:which(year_id == "1994")] & N$stock == 1, ]$cv)))
NIRS1cv17 <- digits(range(c(IR[IR$year %in% year_id[which(year_id == "1995"):length(year_id)] & IR$stock == 1, ]$cv, 
                           N[IR$year %in% year_id[which(year_id == "1995"):length(year_id)] & IR$stock == 1, ]$cv, 
                           S[IR$year %in% year_id[which(year_id == "1995"):length(year_id)] & IR$stock == 1, ]$cv)))
S1cv94 <- digits(range(S[S$year %in% year_id[1:which(year_id == "1994")] & S$stock == 1, ]$cv))
R1cv94 <- digits(range(R[R$yr %in% 7:22 & R$stock == 1, ]$cv))
R1cv17 <- digits(range(R[R$yr %in% 23:39 & R$stock == 1, ]$cv))

t1 <- post$summary[grepl("theta\\[1,1\\]", rownames(post$summary)), ]
CI <- function(df) paste0(digits(df['50%']), "; 95% CI ", digits(df['2.5%']), "--", digits(df['97.5%']))
CIt <- function(df) paste0(digits(df['50%']), " (95% CI ", digits(df['2.5%']), "--", digits(df['97.5%'])) #Note missing closing parens

et1 <- as[[1]]/weir[,1] 
et1_n <- sum(!is.na(et1))
et1_r <-digits(range(et1, na.rm = TRUE))

sa1 <- post$summary[grepl("sigma.air\\[1\\]", rownames(post$summary)), ]

C_as <- post$summary[grepl("C_as$", rownames(post$summary)), ]

lna1 <- post$summary[grepl("lnalpha\\[1\\]", rownames(post$summary)), ]

sw1 <- post$summary[grepl("sigma.white\\[1\\]", rownames(post$summary)), ]

phi1 <- post$summary[grepl("phi\\[1\\]", rownames(post$summary)), ]

SMSY1 <- post$summary[grepl("S.msy\\[1\\]", rownames(post$summary)), ]

SMSR1 <- post$summary[grepl("S.max\\[1\\]", rownames(post$summary)), ]

rs <- function(sn){
  rs <- post$summary[grepl(paste0("R\\[\\d+,", sn, "\\]"), rownames(post$summary)), "50%"][7:42]/
    post$summary[grepl(paste0("S\\[\\d+,", sn, "\\]"), rownames(post$summary)), "50%"][1:36]
  list(min = digits(range(rs)[1]),
       max = digits(range(rs)[2]),
       n = sum(rs < 1)
  )
}

prob_e <- get_profileprobs(get_profile(post, "Deshka"), c(13000, 27000))
prob_p <- get_profileprobs(get_profile(post, "Deshka"), c(goals_list[[1]][1], goals_list[[1]][2]))
```
Measures of Chinook salmon abundance for the Deshka River stock displayed a common trend through time when more than one measure was available (Figure 4). Estimated escapement closely tracked weir counts, which are assumed to be very precise, starting in 1995. Prior to 1995, only aerial survey data are available to index abundance. Runs were large prior to 1991, underwent a decline during 1991--1994, rebounded during 1995--2004, declined again starting in 2005, and remained at a lower level during 2008--2017. Escapement estimates ranged between `r minrow(S, 1)$median` in `r minrow(S, 1)$year` and `r maxrow(S, 1)$median` in `r maxrow(S, 1)$year`, and inriver run estimates ranged from `r minrow(IR, 1)$median` in `r minrow(IR, 1)$year` to `r maxrow(IR, 1)$median` in `r maxrow(IR, 1)$year` (Appendix C1).
  
Total and inriver run estimates (Appendix C1) are more precise than escapement estimates prior to 1995 because harvest is well estimated compared to the abundance estimates based on single annual aerial surveys. Coefficients of variation for total and inriver run ranged from `r NIR1cv94[1]` to `r NIR1cv94[2]` prior to 1995 whereas coefficients of variation for escapement ranged from `r S1cv94[1]` to `r S1cv94[2]`. After 1995, all estimates have coefficients of variation ranging from `r NIRS1cv17[1]` to `r NIRS1cv17[2]` because weir estimates are very precise. Coefficients of variation for recruitment from complete brood years were highly variable both before (`r R1cv94[1]`--`r R1cv94[2]`) and after (`r R1cv17[1]`--`r R1cv17[2]`) the weir was installed and associated with considerable variation in the S-R relationship ($\sigma_W$ = `r CI(sw1)`; Table 1). 
  
The model-estimated proportion of the escapement observed during single aerial surveys of the Deshka River, $\theta_i$, was `r CIt(t1)`; Table 2). Empirical estimates of observability (survey count/weir count) exist for `r et1_n` years and range from `r et1_r[1]` to `r et1_r[2]`. There was average agreement between Deshka River aerial survey counts (expanded by inverse observability) and Deshka River weir counts.  The lognormal standard deviation for the Deshka River aerial survey regression, $\sigma_{ASi}$, was `r CIt(sa1)`; Table 2), which is similar to the median value for the distribution of $\sigma_{AS}$ (`r CI(C_as)`).
  
Estimated Ricker parameters from the state-space model take uncertainty in estimated escapement S and recruitment R (Figure 5 error bars) into account. The individual data pairs are weighted depending upon the certainty with which the individual values of S and R are known. Because escapement and recruitment are poorly known for many brood years, and due to other sources of uncertainty, Ricker S-R relationships that could have plausibly generated the observed data are diverse (Figure 5: light lines), often deviating substantially from the mean Ricker relationship (Figure 5: heavy dashed line).
  
Median productivity (log recruits per spawner in the absence of density effects) of the Deshka River Chinook salmon stock during 1979–2017 was moderate ($\textrm{ln}[\alpha]$ = `r CI(lna1)`; Table 1). There is a great deal of uncertainty about productivity, as evident in the extent to which the plausible S-R relationships differ with respect to their slope at the origin (Figure 5). Similarly, uncertainty about $\beta$ is reflected in variability in the escapements leading to maximum recruitment $S_{MSR}$, and uncertainty about equilibrium abundance $S_{EQ}$ is reflected by variability in the escapements where the curves intersect the replacement line. Variability in spawning escapements associated with maximum sustained yield $S_{MSY}$ is harder to visualize. Graphically, sustained yield is greatest at the escapement that maximizes the length of a vertical line drawn from the Ricker curve downward to the replacement line. Given the diversity of plausible S-R relationships (Figure 5), it is important to choose an escapement goal that is robust to this uncertainty rather than one tailored solely to the median S-R relationship. To address this uncertainty, we tallied the success or failure of a given number of spawners in achieving biological reference points across plausible S-R relationships in the optimal yield, optimal recruitment, and overfishing profiles (Figure 6). 
  
The model-estimated escapement leading to maximum sustained yield $S_{MSY}$ for the Deshka River Chinook salmon stock was `r CIt(SMSY1)`; Table 1). The optimal yield profiles (Figure 6, top panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSY. These probabilities, which are greatest near $S_{MSY}$, can be used to quantify the yield performance of prospective escapement goals (Figure 6 pink-shaded areas), taking into consideration all uncertainty about the true abundance and productivity of the stock. The overfishing profiles (Figure 6 middle panel) show the probability that sustained yield would be reduced to less than 70%, 80%, or 90% of MSY by fishing too hard and supplying too few spawners. For this stock, these probabilities are nearly the exact complements of the probabilities in the left-hand limbs of the optimal yield profiles.
  
Expected sustained yield (number of fish over and above that necessary to replace the number of spawners, averaged over brood years 1973–2014) is maximized at $S_{MSY}$ (Figure 7). Actual yield in any single year has varied widely (Figure 5), in part because the S-R relationship is noisy and in part because many escapements have been near $S_{EQ}$. Annual median return per spawner has ranged between `r rs(1)$min` and `r rs(1)$max` for Deshka River Chinook salmon with `r rs(1)$n` of 36 complete brood years failing to replace themselves (Figure 5, Appendix C1).
  
The model-estimated escapement leading to maximum recruitment $S_{MSR}$ was `r CIt(SMSR1)`; Table 1). Analogous to the optimum yield profiles discussed above, optimum recruitment profiles tally the success or failure of a given number of spawners to maximize recruitment across plausible S-R relationships. The optimal recruitment profiles in Figure 6 (bottom panel) show the probability of a given number of spawners achieving 70%, 80%, and 90% of MSR. Optimum recruitment probabilities, which are highest near $S_{MSR}$, reach maximums at larger spawning abundances than optimum yield probabilities and decrease more slowly as spawning abundance increases.
  
## Eastside Susitna Stock
```{r echo=FALSE, include=FALSE}
NIR2cv <- digits(range(c(IR[IR$stock == 2, ]$cv, 
                        N[N$stock == 2, ]$cv)))
S2cv <- digits(range(S[S$stock == 2, ]$cv))
R2cv <- digits(range(R[R$stock == 2, ]$cv))

D2 <- post$summary[grepl("Dsum.S2", rownames(post$summary)), ]
B2 <- post$summary[grepl("Bsum.So\\[1", rownames(post$summary)), ]

p2out <-digits(post$summary[grepl("p.S2\\[\\d+,7\\]", rownames(post$summary)), "mean"] * 100)

t2 <- post$summary[grepl("theta\\[2,1\\]", rownames(post$summary)), ]
t3 <- post$summary[grepl("theta\\[3,1\\]", rownames(post$summary)), ]
t4 <- post$summary[grepl("theta\\[4,1\\]", rownames(post$summary)), ]
t5 <- post$summary[grepl("theta\\[5,1\\]", rownames(post$summary)), ]
t6 <- post$summary[grepl("theta\\[6,1\\]", rownames(post$summary)), ]
t7 <- post$summary[grepl("theta\\[7,1\\]", rownames(post$summary)), ]

et2 <- as[[2]][,4]/weir[,2] 
et2_n <- sum(!is.na(et2))
et2_r <- digits(et2[!is.na(et2)])

et3 <- as[[2]][,6]/weir[,3] 
et3_n <- sum(!is.na(et3))
et3_r <- digits(et3[!is.na(et3)])

sa2 <- post$summary[grepl("sigma.air\\[2\\]", rownames(post$summary)), ]
sa3 <- post$summary[grepl("sigma.air\\[3\\]", rownames(post$summary)), ]
sa4 <- post$summary[grepl("sigma.air\\[4\\]", rownames(post$summary)), ]
sa5 <- post$summary[grepl("sigma.air\\[5\\]", rownames(post$summary)), ]
sa6 <- post$summary[grepl("sigma.air\\[6\\]", rownames(post$summary)), ]
sa7 <- post$summary[grepl("sigma.air\\[7\\]", rownames(post$summary)), ]

lna2 <- post$summary[grepl("lnalpha\\[2\\]", rownames(post$summary)), ]

sw2 <- post$summary[grepl("sigma.white\\[2\\]", rownames(post$summary)), ]

phi2 <- post$summary[grepl("phi\\[2\\]", rownames(post$summary)), ]

SMSY2 <- post$summary[grepl("S.msy\\[2\\]", rownames(post$summary)), ]

SMSR2 <- post$summary[grepl("S.max\\[2\\]", rownames(post$summary)), ]

prob_p2 <- get_profileprobs(get_profile(post, "East Susitna"), c(goals_list[[2]][1], goals_list[[2]][2]))
```
Measures of Chinook salmon abundance for the Eastside Susitna stock displayed a common trend through time (Figure 8). Runs were small prior to 1983, increased during 1983--1997, underwent a decline during 1998--2012, rebounded slightly after 2012, but were low again in 2017. Escapement estimates ranged between `r minrow(S, 2)$median` in `r minrow(S, 2)$year` and `r maxrow(S, 2)$median` in `r maxrow(S, 2)$year`, and inriver run estimates ranged from `r minrow(IR, 2)$median` in `r minrow(IR, 2)$year` to `r maxrow(IR, 2)$median` in `r maxrow(IR, 2)$year` (Appendix C2).
  
Total and inriver run estimates (Appendix C2) have similar precision as escapement estimates. Coefficients of variation for total and inriver run ranged from `r NIR2cv[1]` to `r NIR2cv[2]`, and coefficients of variation for escapement ranged from `r S2cv[1]` to `r S2cv[2]`. Coefficients of variation for recruitment from complete brood years were moderate (`r R2cv[1]`--`r R2cv[2]`) and reflect moderate variation in the S-R relationship ($\sigma_W$ = `r CI(sw2)`).
  
Among the surveyed streams within the Eastside Susitna stock, Chinook salmon in Little Willow and Willow creeks increased in relative abundance between 1979 and 2017 whereas those in Goose, Kashwitna, Montana, and Sheep creeks decreased in relative abundance (Figure 9, Appendix D1). Most recently, Willow Creek was the largest component of the Eastside Susitna stock spawning abundance followed by Little Willow Creek, Montana Creek, Sheep Creek,  Kashwitna River, and Goose Creek. The inverse dispersion for the Eastside Susitna stock is large ($D_{comp}$ = `r CI(D2)`; Table 1), indicating trends in the relative magnitude of survey counts and radiotelemetry data are well explained by the multinomial logistic regression model with a calendar-year covariate. There are minor differences between estimated stock composition and empirical stock composition estimates in some years, which represent situations where weighted relative survey counts and telemetry data disagree.
  
Because Chinook salmon in unsurveyed streams in the Eastside Susitna stock lack relative composition information early in the time series, no trend in the relative abundance of unsurveyed streams can be estimated. "Other" fish from unsurveyed streams composed `r min(p2out)`--`r max(p2out)`% (Figure 9, Appendix D1) of the Eastside Susitna stock. Inverse dispersion is small ($B_{survey}$ = `r CI(B2)`; Table 1), indicating high variability in the proportion of the Eastside Susitna stock that spawns within the 6 surveyed streams. High variability was documented with telemetry data.
  
The model-estimated proportion of the escapement observed during an aerial survey (Table 2) of the Eastside Susitna stock ranged from `r CIt(t3)`) for Kashwitna River to `r CIt(t5)`) for Montana Creek. There was good agreement between the Goose Creek, Little Willow Creek, Montana Creek, and Willow Creek aerial survey counts (expanded by inverse observability and stock composition) and other indices of abundance in the Eastside Susitna stock, all of which had lognormal standard deviations that were smaller than the median value for the distribution of $\sigma_{AS}$ (`r CI(C_as)`). The lognormal standard deviation for the Kashwitna River and Sheep Creek aerial survey regressions were larger than the median value for the distribution of $\sigma_{AS}$, indicating these surveys were more variable abundance indicators.
  
Uncertainty in estimated escapement S and recruitment R (Figure 10^[The interpretation of Figures 10-12 is explained more fully in the Deshka River stock section] error bars) is incorporated into variability in the underlying stock-recruit relationship. The Eastside Susitna stock has produced a yield for most broods, although not for a prolonged period in the early part of this century. Annual median return per spawner has ranged between `r rs(2)$min` and `r rs(2)$max` for the Eastside Susitna Chinook salmon stock with `r rs(2)$n` of 36 complete brood years failing to replace themselves (Figure 10, Appendix C2). 

Median productivity (log recruits per spawner in the absence of density effects) of the Eastside Susitna Chinook salmon stock during 1979–2017 was moderate ($\textrm{ln}[\alpha]$ = `r CI(lna2)`; Table 1). The model-estimated escapement leading to maximum sustained yield $S_{MSY}$ for the Eastside Susitna Chinook salmon stock was `r CIt(SMSY2)`; Table 2). Both quantities have wide credibility intervals, as do the other reference points for the stock. Profiles (Figure 11) are used to evaluate the performance of various escapements relative to reference points while considering the underlying uncertainly. The probability that a given number of spawners achieves a high percentage of MSY is maximized near $S_{MSY}$. Expected sustained yield (number of fish over and above that necessary to replace the number of spawners, averaged over brood years 1973–2014) is also maximized at $S_{MSY}$ (Figure 12). Optimum recruitment probabilities (Figure 11), which are highest near $S_{MSR}$, reach maximums at larger spawning abundances than optimum yield probabilities and are very wide relative to yield profiles, limiting their management utility.
  
## Talkeetna River Stock
```{r echo=FALSE, include=FALSE}
NIR3cv <- digits(range(c(IR[IR$stock == 3, ]$cv, 
                        N[N$stock == 3, ]$cv)))
S3cv <- digits(range(S[S$stock == 3, ]$cv))
R3cv <- digits(range(R[R$stock == 3, ]$cv))

D3 <- post$summary[grepl("Dsum.S3", rownames(post$summary)), ]
B3 <- post$summary[grepl("Bsum.So\\[2", rownames(post$summary)), ]

p3out <-digits(post$summary[grepl("p.S3\\[\\d+,3\\]", rownames(post$summary)), "mean"] * 100)

t8 <- post$summary[grepl("theta\\[8,1\\]", rownames(post$summary)), ]
t9 <- post$summary[grepl("theta\\[9,1\\]", rownames(post$summary)), ]

sa8 <- post$summary[grepl("sigma.air\\[8\\]", rownames(post$summary)), ]
sa9 <- post$summary[grepl("sigma.air\\[9\\]", rownames(post$summary)), ]

lna3 <- post$summary[grepl("lnalpha\\[3\\]", rownames(post$summary)), ]

sw3 <- post$summary[grepl("sigma.white\\[3\\]", rownames(post$summary)), ]

phi3 <- post$summary[grepl("phi\\[3\\]", rownames(post$summary)), ]

SMSY3 <- post$summary[grepl("S.msy\\[3\\]", rownames(post$summary)), ]

SMSR3 <- post$summary[grepl("S.max\\[3\\]", rownames(post$summary)), ]

prob_p3 <- get_profileprobs(get_profile(post, "Talkeetna"), c(goals_list[[3]][1], goals_list[[3]][2]))
```
Measures of Chinook salmon abundance for the Talkeetna River stock are few but displayed a common trend through time (Figure 13). Runs increased through 1988, underwent a decline during 1989--1994, rebounded until 1997, and gradually declined thereafter. Escapement estimates ranged between `r minrow(S, 3)$median` in `r minrow(S, 3)$year` and `r maxrow(S, 3)$median` in `r maxrow(S, 3)$year`, and inriver run estimates ranged from `r minrow(IR, 3)$median` in `r minrow(IR, 3)$year` to `r maxrow(IR, 3)$median` in `r maxrow(IR, 3)$year` (Appendix C3).
  
Total and inriver run estimates (Appendix C3) have similar precision as escapement estimates. Coefficients of variation for total and inriver run ranged from `r NIR3cv[1]` to `r NIR3cv[2]`, and coefficients of variation for escapement ranged from `r S3cv[1]` to `r S3cv[2]`. Coefficients of variation for recruitment from complete brood years were highly variable (`r R3cv[1]`--`r R3cv[2]`) and associated with considerable variation in the S-R relationship ($\sigma_W$ = `r CI(sw3)`).
  
Between the 2 surveyed streams within the Talkeetna River stock, Clear Creek Chinook salmon increased in relative abundance between 1979 and 2017 whereas fish in Prairie Creek decreased in relative abundance (Figure 9, Appendix D2). Clear and Prairie Creeks are similar-sized components of the spawning abundance for the Talkeetna River stock in recent years. The inverse dispersion for the Talkeetna River stock is small ($D_{comp}$ = `r CI(D3)`; Table 1), indicating trends in the relative magnitude of survey counts and radiotelemetry data vary significantly from the multinomial logistic regression model with a calendar-year covariate. There is considerable divergence between estimated stock composition and empirical stock composition estimates in some years, which represent situations where weighted relative survey counts and telemetry data disagree.
  
Because fish in unsurveyed streams in the Talkeetna River stock lack relative composition data early in the time series, no trend in the relative abundance of unsurveyed streams can be estimated. "Other" fish from unsurveyed streams composed `r min(p3out)`--`r max(p3out)`% (Figure 9, Appendix D2) of the Talkeetna River stock. Inverse dispersion is small ($B_{survey}$ = `r CI(B3)`; Table 1) indicating high variability in the proportion of the Talkeetna River stock spawning within the 2 surveyed streams. High variability was also documented with telemetry data.

The model-estimated proportion of the escapement observed during an aerial survey (Table 2) of the Talkeetna stock ranged from `r CIt(t8)`) for Clear Creek to `r CIt(t9)`) for Prairie Creek (Table 2). There was very good agreement between both aerial survey counts (expanded by inverse observability and stock composition) and mark-recapture estimated abundance for the Talkeetna River stock.  The lognormal standard deviation for the aerial survey regressions was `r CIt(sa8)`) for Clear Creek and `r CIt(sa9)`) for Prairie Creek, both of which are smaller than the median value for the distribution of $\sigma_{AS}$ (`r CI(C_as)`).
  
Uncertainty in estimated escapement S and recruitment R (Figure 14^[The interpretation of Figures 14-16 is explained more fully in the Deshka River stock section] error bars) is incorporated into variability in the underlying stock-recruit relationship. The Talkeetna stock has frequently failed to produce a yield; this may be partially due to the escapements being near $S_{eq}$ and partially due to the low productivity of the stock. Annual median return per spawner has ranged between `r rs(3)$min` and `r rs(3)$max` for Talkeetna River Chinook salmon, with `r rs(3)$n` of 36 complete brood years failing to replace themselves (Figure 14, Appendix C3). 

Median productivity (log recruits per spawner in the absence of density effects) of the Talkeetna River Chinook salmon stock during 1979–2017 was low ($\textrm{ln}[\alpha]$ = `r CI(lna3)`; Table 1). Model-estimated escapement leading to maximum sustained yield $S_{MSY}$ for the Talkeetna River Chinook salmon stock was `r CIt(SMSY3)`; Table 1). Both quantities have wide credibility intervals, as do the other reference points for the stock. Profiles (Figure 15) are used to evaluate the performance of various escapements relative to reference points while considering the underlying uncertainly. The probability that a given number of spawners achieves a high percentage of MSY is maximized near $S_{MSY}$. Expected sustained yield (number of fish over and above that necessary to replace the number of spawners, averaged over brood years 1973–2014) is also maximized at $S_{MSY}$ (Figure 16). Optimum recruitment probabilities (Figure 15), which are highest near $S_{MSR}$, reach maximums at larger spawning abundances than optimum yield probabilities and are very wide relative to yield profiles, limiting their management utility.

## Yentna River Stock
```{r echo=FALSE, include=FALSE}
NIR4cv <- digits(range(c(IR[IR$stock == 4, ]$cv, 
                        N[N$stock == 4, ]$cv)))
S4cv <- digits(range(S[S$stock == 4, ]$cv))
R4cv <- digits(range(R[R$stock == 4, ]$cv))

D4 <- post$summary[grepl("Dsum.S4", rownames(post$summary)), ]
B4 <- post$summary[grepl("Bsum.So\\[3", rownames(post$summary)), ]

p4out <-digits(post$summary[grepl("p.S4\\[\\d+,5\\]", rownames(post$summary)), "mean"] * 100)

t10 <- post$summary[grepl("theta\\[10,1\\]", rownames(post$summary)), ]
t11 <- post$summary[grepl("theta\\[11,1\\]", rownames(post$summary)), ]
t12 <- post$summary[grepl("theta\\[12,1\\]", rownames(post$summary)), ]
t13 <- post$summary[grepl("theta\\[13,1\\]", rownames(post$summary)), ]

sa10 <- post$summary[grepl("sigma.air\\[10\\]", rownames(post$summary)), ]
sa11 <- post$summary[grepl("sigma.air\\[11\\]", rownames(post$summary)), ]
sa12 <- post$summary[grepl("sigma.air\\[12\\]", rownames(post$summary)), ]
sa13 <- post$summary[grepl("sigma.air\\[13\\]", rownames(post$summary)), ]

lna4 <- post$summary[grepl("lnalpha\\[4\\]", rownames(post$summary)), ]

sw4 <- post$summary[grepl("sigma.white\\[4\\]", rownames(post$summary)), ]

phi4 <- post$summary[grepl("phi\\[4\\]", rownames(post$summary)), ]

SMSY4 <- post$summary[grepl("S.msy\\[4\\]", rownames(post$summary)), ]

SMSR4 <- post$summary[grepl("S.max\\[4\\]", rownames(post$summary)), ]

prob_p4 <- get_profileprobs(get_profile(post, "Yentna"), c(goals_list[[4]][1], goals_list[[4]][2]))
```
Some of the measures of abundance for the Yentna River Chinook salmon stock displayed a common trend through time (Figure 17). Runs increased through 1984, underwent a decline during 1985--1994, and rebounded until 2004, declined through 2009, increased through 2015, and declined to historically low levels in 2017. Escapement estimates ranged between `r minrow(S, 4)$median` in `r minrow(S, 4)$year` and `r maxrow(S, 4)$median` in `r maxrow(S, 4)$year`, and inriver run estimates ranged from `r minrow(IR, 4)$median` in `r minrow(IR, 4)$year` to `r maxrow(IR, 4)$median` in `r maxrow(IR, 4)$year` (Appendix C4).
  
Total and inriver run estimates (Appendix C4) have similar precision as escapement estimates. Coefficients of variation for total and inriver run ranged from `r NIR4cv[1]` to `r NIR4cv[2]`, and coefficients of variation for escapement ranged from `r S4cv[1]` to `r S4cv[2]`. Coefficients of variation for recruitment from complete brood years were moderate (`r R4cv[1]`--`r R4cv[2]`), reflecting moderate variation in the S-R relationship ($\sigma_W$ = `r CI(sw4)`).
  
Among the surveyed streams within the Yentna River stock, Chinook salmon in Peters Creek increased in relative abundance between 1979 and 2017 whereas those in Cache Creek decreased in relative abundance, and the relative abundances of the Chinook salmon in Lake Creek and Talachulitna River have remained similar across years (Figure 9, Appendix D3). Lake Creek Chinook salmon are the largest component of the Yentna River stock spawning abundance in recent years followed by Talachulitna River, Peters Creek, and Cache Creek. The inverse dispersion for the Yentna River stock is moderate ($D_{comp}$ = `r CI(D4)`; Table 2), indicating trends in the relative magnitude of survey counts and radio-telemetry data are fairly well explained by the multinomial logistic regression model with a calendar year covariate. Estimated stock composition and empirical stock composition estimates are similar.
  
Because fish in unsurveyed streams in the Yentna River stock lack relative composition data early in the time series, no trend in the relative abundance of unsurveyed streams can be estimated. "Other" fish in unsurveyed streams compose `r min(p4out)`--`r max(p4out)`% (Figure 9, Appendix D3) of the Yentna River stock. Inverse dispersion is moderate ($B_{survey}$ = `r CI(B4)`; Table 1), indicating moderate variability in the proportion of the Yentna River stock  spawning within the 4 surveyed streams. Moderate variability was documented with telemetry data.

The model-estimated proportion of the escapement observed during an aerial survey (Table 2) in the Yentna River stock ranged from `r CIt(t11)`) for Lake Creek to `r CIt(t13)`) for Talachulitna River. There was good agreement between the Lake Creek and Talachulitna River aerial survey counts (expanded by inverse observability and stock composition) and mark--recapture estimated abundance in the Yentna River stock, both of which had lognormal standard deviations that were less than or equal to the median value for the distribution of $\sigma_{AS}$ (`r CI(C_as)`). The lognormal standard deviation for the Cache Creek and Peters Creek aerial survey regressions were larger than the median value for the distribution of $\sigma_{AS}$ indicating these surveys were poorly correlated with mark--recapture abundance. These regressions are based on only 4 years of mark--recapture data.
  
Uncertainty in estimated escapement S and recruitment R (Figure 18^[The interpretation of Figures 18-20 is explained more fully in the Deshka River stock section] error bars) is incorporated into variability in the underlying stock-recruit relationship. Many brood years from the Yentna River stock have produced a yield, with most exceptions coming from escapement at or above $S_{EQ}$. Annual median return per spawner ranged between `r rs(4)$min` and `r rs(4)$max` for the Yentna River Chinook salmon stock with `r rs(4)$n` of 36 complete brood years failing to replace themselves (Figure 18, Appendix C4). 

Median productivity (log recruits per spawner in the absence of density effects) of the Yentna River Chinook salmon stock during 1979–2017 was moderate  ($\textrm{ln}[\alpha]$ = `r CI(lna4)`; Table 1). Model-estimated escapement leading to maximum sustained yield $S_{MSY}$ for the Yentna River Chinook salmon stock was estimated to be `r CIt(SMSY4)`; Table 1). Both quantities have wide credibility intervals, as do the other reference points for the stock. Profiles (Figure 19) are used to evaluate the performance of various escapements relative to reference points while considering the underlying uncertainly. The probability that a given number of spawners achieves a high percentage of MSY is maximized near $S_{MSY}$. Expected sustained yield (number of fish over and above that necessary to replace the number of spawners, averaged over brood years 1973–2014) is also maximized at $S_{MSY}$ (Figure 20). Optimum recruitment probabilities (Figure 19), which are highest near $S_{MSR}$, reach maximums at larger spawning abundances than optimum yield probabilities and are very wide relative to yield profiles, limiting their management utility.
  
## Age Composition
```{r echo=FALSE, include=FALSE}
ageD <- age[grepl("Deshka", age$stock), ]
ageES <- age[grepl("East Susitna", age$stock), ]
ageT <- age[grepl("Talkeetna", age$stock), ]
ageY <- age[grepl("Yentna", age$stock), ]

p1 <- digits(range(post$summary[grepl("p\\[\\d+,1\\]", rownames(post$summary)), "mean"])*100)
p2 <- digits(range(post$summary[grepl("p\\[\\d+,2\\]", rownames(post$summary)), "mean"])*100)
p3 <- digits(range(post$summary[grepl("p\\[\\d+,3\\]", rownames(post$summary)), "mean"])*100)
p4 <- digits(range(post$summary[grepl("p\\[\\d+,4\\]", rownames(post$summary)), "mean"])*100)
```
Between `r min(intersect(ageD$year, intersect(ageES$year, ageY$year)))` and `r max(intersect(ageD$year, intersect(ageES$year, ageY$year)))`, annual age composition datasets exist from sport harvested Chinook salmon in the Deshka River, Eastside Susitna, and Yentna River stocks. In general, the Eastside Susitna Chinook salmon stock contained larger proportions of older fish (Figure 21, middle panel). Between `r min(intersect(ageD$year, intersect(ageES$year, ageT$year)))` and `r max(intersect(ageD$year, intersect(ageES$year, ageT$year)))`, annual age composition datasets exist for the sport harvest of Chinook salmon in the Eastside Susitna, Deshka River and Talkeetna River stocks. The Deshka River Chinook salmon stock contained smaller proportions of older fish in paired annual samples. 
  
Chinook salmon in the Susitna River drainage are composed of age-3 (1.1), age-4 (1.2), age-5 (1.3), and age-6 (1.4) fish (Figure 21 middle panel, Table 3). Throughout the time series age-5 fish have been the dominant age class whereas the relative abundance of age-6 fish has steadily decreased and the relative abundance of age-3 fish has increased (dramatically in recent years).
  
Age-at-maturity of Susitna River drainage Chinook salmon varied across years (Figure 21 top panel, Table 4) from `r p1[1]` to `r p1[2]`% for age-3, from `r p2[1]` to `r p2[2]`% for age-4, from `r p3[1]` to `r p3[2]`% for age-5, and from `r p4[1]` to `r p4[2]`% for age-6. Age-at-maturity has trended strongly toward increasing contributions of age-3, age-4, and age-5 fish and decreasing contributions of age-6 fish.
  
# Discussion
The only discussion presented in this document pertains to performance at the current and recommended goal ranges.
  
### Deshka River
Deshka River Chinook salmon have an existing goal range of 13,000--27,000 Chinook salmon. Escapements at the low end of the existing range have `r prob_e[[1, "OYP80"]]`% probability of producing a yield greater than 80% of MSY whereas escapements at the upper end of the existing range have `r prob_e[[2, "OYP80"]]`% probability of producing yields greater than 80% of MSY. 
  
The proposed escapement goal of 9,000--18,000 fish has `r prob_p[[1, "OYP80"]]`% probability of achieving 80+% of MSY at the lower bound and `r prob_p[[2, "OYP80"]]`% probability of achieving 80+% MSY at the upper bound.

### East Susitna
The proposed escapement goal of 13,000–25,000 fish has `r prob_p2[[1, "OYP80"]]`% probability of achieving 80+% of MSY at the lower bound and `r prob_p2[[2, "OYP80"]]`% probability of achieving 80+% of MSY at the upper bound.
  
### Talkeetna River
The proposed escapement goal 9,000–17,500 fish has `r prob_p3[[1, "OYP80"]]`% probability of achieving 80+% of MSY at the lower bound and `r prob_p3[[2, "OYP80"]]`% probability of achieving 80+% of MSY at the upper bound. With respect to recruitment, the proposed escapement goal has `r prob_p3[[1, "ORP80"]]`% probability of achieving 80+% of MSR at the lower bound and `r prob_p3[[2, "ORP80"]]`% probability of achieving 80+% of MSR at the upper bound.
  
### Yentna River
The proposed escapement goal of 13,000–22,000 fish has `r prob_p4[[1, "OYP80"]]`% probability of achieving 80+% of MSY at the lower bound and `r prob_p4[[2, "OYP80"]]`% probability of achieving 80+% of MSY at the upper bound. With respect to recruitment, the proposed escapement goal has `r prob_p4[[1, "ORP80"]]`% probability of achieving 80+% of MSR at the lower bound and `r prob_p4[[2, "ORP80"]]`% probability of achieving 80+% of MSR at the upper bound.