---
output: 
  word_document:
    reference_docx: ".\\doc_styles\\word_styles_FDS.docx"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.cap = TRUE, fig.align = 'center')
library(SusitnaEG)
get_ids()
post <- readRDS("..\\..\\posts\\SuChinook_134cf92.rds")
```


Table: Table 1.- Aerial survey observability and lognormal standard deviation with 95% confidence interval for each population in the Susitna River drainage, calendar years 1979--2017.
```{r}
table_airerror(post)
``` 

Table: Table 2.- State-space model parameter estimates for Susitna River Chinook salmon by stock, calendar years 1979--2017. 
```{r}
table_params(post)
```
  
*Note*: Posterior medians are point estimates and 95% credibility intervals are shown in parentheses. Parameter definitions are in the Methods section.
  
Table: Table 3.- Age composition estimates obtained by fitting a state-space model to data from Susitna River drainage Chinook salmon, calendar years 1979--2017.
```{r}
table_age(post, "q")
```

Table: Table 4.- Age-at-maturity estimates obtained by fitting a state-space model to data from Susitna River drainage Chinook salmon, brood years 1973--2014.
```{r}
table_age(post, "p")
```
