---
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.cap = TRUE, fig.align = 'center')
library(SusitnaEG)
get_ids()
post <- readRDS("..\\..\\posts\\SuChinook_a02eb71a.rds")
```

Appendix C1.- Annual abundance estimates for Deshka River Chinook salmon obtained by fitting a state-space model to data from 1979-2017. Point estimates are posterior medians, CVs are posterior standard deviations divided by posterior means.  Recruitment values are listed by brood year.  
```{r}
tab_state <- table_state(post, "bystock")
knitr::kable(tab_state[[1]][-2], row.names = FALSE, align = "r", escape = FALSE)
```

Appendix C2.- Annual abundance estimates for East Susitna Chinook salmon obtained by fitting a state-space model to data from 1979-2017. Point estimates are posterior medians, CVs are posterior standard deviations divided by posterior means.  Recruitment values are listed by brood year.  
```{r}
knitr::kable(tab_state[[2]][-2], row.names = FALSE, align = "r", escape = FALSE)
```

Appendix C3.- Annual abundance estimates for Talkeetna River Chinook salmon obtained by fitting a state-space model to data from 1979-2017. Point estimates are posterior medians, CVs are posterior standard deviations divided by posterior means.  Recruitment values are listed by brood year.  
```{r}
knitr::kable(tab_state[[3]][-2], row.names = FALSE, align = "r", escape = FALSE)
```

Appendix C4.- Annual abundance estimates for Yentna River Chinook salmon obtained by fitting a state-space model to data from 1979-2017. Point estimates are posterior medians, CVs are posterior standard deviations divided by posterior means.  Recruitment values are listed by brood year.  
```{r}
knitr::kable(tab_state[[4]][-2], row.names = FALSE, align = "r", escape = FALSE)
```

Appendix D1.- Annual stock composition estimates for East Susitna Chinook salmon obtained by fitting a state-space model to data from 1979-2017. Point estimates are posterior means with posterior standard deviations in parentheses.  
```{r}
tab_stock <- table_stock(post)
knitr::kable(tab_stock[[1]], row.names = FALSE, align = "r", escape = FALSE)
```

Appendix D2.- Annual stock composition estimates for Talkeetna River Chinook salmon obtained by fitting a state-space model to data from 1979-2017. Point estimates are posterior means with posterior standard deviations in parentheses.  
```{r}
knitr::kable(tab_stock[[2]], row.names = FALSE, align = "r", escape = FALSE)
```

Appendix D3.- Annual stock composition estimates for Yentna River Chinook salmon obtained by fitting a state-space model to data from 1979-2017. Point estimates are posterior means with posterior standard deviations in parentheses.  
```{r}
knitr::kable(tab_stock[[3]], row.names = FALSE, align = "r", escape = FALSE)
```