---
title: "Susitna EG Preliminary 2018-2019 estimates"
author: "Adam Reimer"
date: "12/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(SusitnaEG)
get_ids()
post <- readRDS("..\\posts\\SuChinook_adddata_c211807.rds")
table <- table_state(post, "bystock")
plot <- lapply(stock_id, plot_fit, post_dat = post)
```

## Preliminary estimates
  
Adding 2018-2019 age, harvest, survey and weir data to the model was easy as those data sets were collected with unchanged sampling designs. In 2018, the mark-recapture sampling design changed, and the model required slight modification to include the data in the new format. For 2018, estimated abundance (N = 30,605: SE = 4,376) from the MR is for the Chinook salmon gt 500mm MEFT spawning within the mainstem Susitna. I used 74% of this estimate ($MR_{y[S=1:3]}$ =  22,648, CV = 0.14) as input data where 74% represent the average proportion of mainstem Susitna MR estimate abundance contained within the Deshka, Eastside Susitna and Talkeetna stocks in 2013-2017. In this format we can include the 2018 MR estimate in the model with the following sampling distribution:

\begin{equation}
MR_{y[S=1:3]}~\sim~\textrm{lognormal}(\textrm{log}(\sum_{s=1}^3 IR_{500ys}), 0.14)
\end{equation}
  
The 2019 estimates can be included directly. Note that the CV's are considerable wider in 2019 than in prior years. 
  
## Deshka
  
Deshka weir data dominates the estimates for the Deshka River stock.
  
```{r, fig.height = 10, fig.width = 10, fig.cap = "Figure 1.- Model estimated escapement (top) and inriver run abundance (bottom) of the Deshka River Chinook salmon stock (black lines show the median and shaded areas show 95% credibility intervals) as reconstructed from aerial survey counts, weir counts, and mark-recapture estimates."}
plot[[1]]
```
  
Table 1.- Annual abundance estimates for the Deshka River Chinook salmon stock obtained by fitting a state-space model to data from 1979 to 2019.
```{r}
knitr::kable(table[[1]][-2], row.names = FALSE, align = "r", escape = FALSE)
```
  
## Eastside Susitna
  
Estimates for the Eastside Susitna stock are considerably less precise than the Deshka River estimates and less precise than prior years Eastside Susitna estimates for which we had MR data. I ran the model 3 times to try and get some intuition about how each data source affects our estimate of abundance. For this stock group the 2018 abundance estimate was ~200 fish larger when run without MR data while the 2019 estimate was ~1,300 fish smaller when run without MR data. I also noticed that in 2018 Willow Creek was surveyed while Deception Creek was not. This is unfortunate because the model requires both surveys, Deception/Willow is the largest population in the Eastside Susitna stock and the 2018 Willow count was the smallest on record. Out of curiosity I expanded the Willow count (by 1.36, the historic ratio of (Deception + Willow)/Willow). This estimate was ~900 less than the estimate tabulated below.  
  
```{r, fig.height = 10, fig.width = 10, fig.cap = "Figure 2.- Model estimated escapement (top) and inriver run abundance (bottom) of the Eastside SUsitna  Chinook salmon stock (black lines show the median and shaded areas show 95% credibility intervals) as reconstructed from aerial survey counts, weir counts, and mark-recapture estimates."}
plot[[2]]
```
  
Table 2.- Annual abundance estimates for the Eastside Susitna Chinook salmon stock obtained by fitting a state-space model to data from 1979 to 2019.
```{r}
knitr::kable(table[[2]][-2], row.names = FALSE, align = "r", escape = FALSE)
```
  
## Talkeetna
  
Estimates for the Talkeetna River stock are also less precise than the Deshka. For this stock the 2018 abundance estimate was ~800 fish larger when run without MR data while the 2019 estimate was ~1,200 fish larger when run without MR data.   
  
```{r, fig.height = 10, fig.width = 10, fig.cap = "Figure 3.- Model estimated escapement (top) and inriver run abundance (bottom) of the Talkeetna River  Chinook salmon stock (black lines show the median and shaded areas show 95% credibility intervals) as reconstructed from aerial survey counts, weir counts, and mark-recapture estimates."}
plot[[3]]
```
  
Table 3.- Annual abundance estimates for the Talkeetna River Chinook salmon stock obtained by fitting a state-space model to data from 1979 to 2019.
```{r}
knitr::kable(table[[3]][-2], row.names = FALSE, align = "r", escape = FALSE)
```
  
## Yentna
  
```{r, fig.height = 10, fig.width = 10, fig.cap = "Figure 4.- Model estimated escapement (top) and inriver run abundance (bottom) of the Yentna River Chinook salmon stock (black lines show the median and shaded areas show 95% credibility intervals) as reconstructed from aerial survey counts, weir counts, and mark-recapture estimates."}
plot[[4]]
```
  
Table 4.- Annual abundance estimates for the Yentna River Chinook salmon stock obtained by fitting a state-space model to data from 1979 to 2019.
```{r}
knitr::kable(table[[4]][-2], row.names = FALSE, align = "r", escape = FALSE)
```