---
title: "Untitled"
author: "Adam Reimer"
date: "February 15, 2019"
output: 
  word_document:
    reference_docx: ".\\word_styles_FDS.docx"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
To use:
  
* The file word_styles_FDS.docx contains commonly used text styles in FDS format.
  
* If a new FDS style is needed add it this markdown file and then create a word doc.
  
* Edit the new style within the word doc to match the appropriate FDS format and save as word_styles_FDS.docx.
  
* Test style by running RMarkdown with reference_docx: ".\\word_styles_FDS.docx"
  
See (https://rmarkdown.rstudio.com/articles_docx.html: Incremental style editing) for more detail.

# Heading 1
First Paragraph^[footnote text]
  
Body text
  
## Heading2
First Paragraph
  
### Heading 3
First Paragraph
  
#### Heading 4
First Paragraph
  
```{r, echo = FALSE, fig.cap = "Figure 2.- Image Caption."}
plot(pressure)
```
  
Body text
  
```{r, echo = FALSE}
knitr::kable(matrix(1:3, 3, 3), col.names = c("Made", "up", "table"))
```
  
Table: Table 1.- Table Caption

Appendix A1.- Code.  
```{r  code = paste0(readLines("..\\..\\..\\models\\mod_SuChin.R", n = 10), "\r\n"), echo = T, eval = F}
```