---
title: "Generic Horsetail Plot"
author: "Adam Reimer"
date: "2024-02-02"
output: html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

```{r, include=FALSE}
library(magrittr)
library(ggplot2)
source("..\\functions\\get.R")
source("..\\functions\\internal.R")
source("..\\functions\\plot.R")
source("..\\functions\\table.R")
data_names <- list.files(path="..\\data")
lapply(data_names, function(x) load(paste0("..\\data\\", x), .GlobalEnv))
getwd()
get_ids(year_range = 1979:2022)
post_new <- readRDS("..\\posts\\SuChinook_11302022.rds") 

Deshka <- 
  plot_horse(post_new, stock_name = "Deshka") +
  ggtitle (NULL) +
  theme_bw(base_size = 20)
Deshka$layers[5:45] <- NULL
Deshka$layers[1:3] <- NULL
Deshka +
  geom_point(aes(x = S, y = R))

Yentna <- 
  plot_horse(post_new, stock_name = "Yentna") +
  ggtitle (NULL) +
  theme_bw(base_size = 20)
Yentna_point <- Yentna
Yentna_point$layers[5:45] <- NULL
Yentna_point$layers[1:3] <- NULL

Yentna_horse <- Yentna
Yentna_horse$layers[1:3] <- NULL
```


Deshka plot with points instead of year labels and error bars and horsetail removed.

```{r, fig.height=8, fig.width=8}
Deshka +
  geom_point(aes(x = S, y = R))
```

Yentna plot with points instead of year labels and error bars and horsetail removed. I did this in case you want to have the same points that were responsible for the "horsetail only" plot your requested earlier.

```{r, fig.height=8, fig.width=8}
Yentna_point +
  geom_point(aes(x = S, y = R))
```

Yentna plot horsetail only. We choose Yetna becasue it had the least variability.

```{r, fig.height=8, fig.width=8}
Yentna_horse
```
