---
output: 
  word_document:
    reference_docx: "..\\markdown\\Report 2019\\doc_styles\\word_styles_FDS.docx"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.cap = TRUE, fig.align = 'center')
library(SusitnaEG)
get_ids()
post <- readRDS("..\\posts\\SuChinook_134cf92.rds")
goals_list <- list(Deshka = c(9000, 18000),
                   Eastside = c(13000, 25000),
                   Talkeetna = c(9000, 17500),
                   Yentna = c(13000, 22000))
```


```{r, fig.width = 8, fig.height = 5, fig.cap = "Optimal yield (OYP) profile for the Deshka River Chinook salmon stock. Profiles show the probability that a specified spawning abundance will result in specified fractions (70%, 80%, and 90% line) of maximum sustained yield."}
profiles <- lapply(stock_id[-5], get_profile, post_dat = post)
profile <- mapply(plot_profile, 
                  profile_dat = profiles, 
                  goal_range = goals_list, 
                  MoreArgs = list(limit = 30000), 
                  profiles = "OYP",
                  SIMPLIFY = FALSE)
profile[[1]]
```
  
*Note*: Pink shaded areas bracket the proposed goal range; grey and black marks along the *x*-axis show comparable lower and upper bounds, respectively, scaled by $S_{MSY}$ ratios for other Alaskan Chinook salmon stocks (see Methods).

```{r, fig.width = 8, fig.height = 5, fig.cap = "Optimal yield (OYP) profile for the Eastside Susitna Chinook salmon stock. Profiles show the probability that a specified spawning abundance will result in specified fractions (70%, 80%, and 90% line) of maximum sustained yield."}
profile[[2]]
```
  
*Note*: Pink shaded areas bracket the proposed goal range; grey and black marks along the *x*-axis show comparable lower and upper bounds, respectively, scaled by $S_{MSY}$ ratios for other Alaskan Chinook salmon stocks (see Methods).

```{r, fig.width = 8, fig.height = 5, fig.cap = "Optimal yield (OYP) profile for the Talkeetna River Chinook salmon stock. Profiles show the probability that a specified spawning abundance will result in specified fractions (70%, 80%, and 90% line) of maximum sustained yield."}
profile[[3]]
```
  
*Note*: Pink shaded areas bracket the proposed goal range; grey and black marks along the *x*-axis show comparable lower and upper bounds, respectively, scaled by $S_{MSY}$ ratios for other Alaskan Chinook salmon stocks (see Methods).

```{r, fig.width = 8, fig.height = 5, fig.cap = "Optimal yield (OYP) profile for the Yentna River Chinook salmon stock. Profiles show the probability that a specified spawning abundance will result in specified fractions (70%, 80%, and 90% line) of maximum sustained yield."}
profile[[4]]
```
  
*Note*: Pink shaded areas bracket the proposed goal range; grey and black marks along the *x*-axis show comparable lower and upper bounds, respectively, scaled by $S_{MSY}$ ratios for other Alaskan Chinook salmon stocks (see Methods).